### 2021-02-14 outputs/paper/data_simulation.Rmd

---
title: "Simulating data for the Ontario restaurant closures experiment"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "SUBTITLE"
abstract: "This document explains how data for the Ontario restaurant closures experiment was simulated, including the research that was used for parameterization and the methods used to randomize data."
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(bookdown)    # for cross referencing figures and graphs; referencing
library(scales)      # for fixing date axes
library(lubridate)   # for manipulating timeseries data
library(kableExtra)  # for nicer tables

```

# Survey questions that require simulated data

# Sources of parameterization

# Methods of data simulation

\newpage

# References

### 2021-02-14 outputs/paper/paper.Rmd

---
title: "TITLE"
author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  bookdown::pdf_document2:
    toc: no
subtitle: "SUBTITLE"
abstract: "ABSTRACT"
thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
bibliography: references.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(bookdown)    # for cross referencing figures and graphs; referencing
library(scales)      # for fixing date axes
library(lubridate)   # for manipulating timeseries data
library(kableExtra)  # for nicer tables

```

# Introduction

# Data

# Discussion

## Overview

## Findings

### FINDING ONE

### FINDING TWO

### FINDING THREE

## Limitations

## Future Directions

\newpage

# References

### 2021-02-14 outputs/paper/paper.Rmd
tidy up files

@@
 library(bookdown)    # for cross referencing figures and graphs; referencing
-library(scales)      # for fixing date axes
-library(lubridate)   # for manipulating timeseries data
 library(kableExtra)  # for nicer tables

### 2021-02-15 scripts/04_clean_restaurant_list_csvs.R
Hamilton dupe fix

@@ -16,11 +16,11 @@ library(tidyverse)
 # Read in data
 
 brant_r <- read_csv(here("inputs/data/brant_restaurants.csv")) %>% 
-  add_column(type = "restaurant") 
+  add_column(type = "") 
 brant_to <- read_csv(here("inputs/data/brant_takeout.csv")) %>% 
-  add_column(type = "takeout") # TODO - split type into three (dine in, dine in and t-o, t-o only)
+  add_column(type = "") 
 
-brant_data <- rbind(brant_r, brant_to) %>% 
+brant_data <- unique(rbind(brant_r, brant_to)) %>% 
   clean_names() %>%
   rename(name = facility_name,
          address = site_address) %>% 
@@ -35,11 +35,11 @@ write_csv(brant_data, here("outputs/data/brant_data.csv"))
 
 clean_data <- function(unit, csv_r, csv_to, save_dir){
   unit_r <- read_csv(here(csv_r)) %>% 
-    add_column(type = "restaurant") 
+    add_column(type = "") 
   unit_to <- read_csv(here(csv_to)) %>% 
-    add_column(type = "takeout") # TODO - split type into three (dine in, dine in and t-o, t-o only)
+    add_column(type = "") 
   
- unit_data <- rbind(unit_r, unit_to) %>% 
+ unit_data <- unique(rbind(unit_r, unit_to)) %>% 
     clean_names() %>%
     rename(name = facility_name,
            address = site_address) %>% 
@@ -56,11 +56,6 @@ chatham_kent_data <- clean_data("chatham",
                                 "inputs/data/chatham_kent_takeout.csv",
                                 "outputs/data/chatham_kent_data.csv")
 
-hamilton_data <- clean_data("hamilton",
-                            "inputs/data/hamilton_restaurants.csv",
-                            "inputs/data/hamilton_takeout.csv",
-                            "outputs/data/hamilton_data.csv")
-
 peel_data <- clean_data("peel",
                             "inputs/data/peel_restaurants.csv",
                             "inputs/data/peel_takeout.csv",
@@ -76,10 +71,23 @@ sudbury_data <- clean_data("sudbury",
                                 "inputs/data/sudbury_takeout.csv",
                                 "outputs/data/sudbury_data.csv")
 
+# Clean data further for Hamilton
+
+hamilton_data <- clean_data("hamilton",
+                            "inputs/data/hamilton_restaurants.csv",
+                            "inputs/data/hamilton_takeout.csv",
[…]

### 2021-02-15 scripts/04_clean_restaurant_list_csvs.R
Actual Hamilton dupe fix

@@ -91,3 +91,4 @@ all_units_data <- unique(rbind(brant_data, chatham_kent_data, hamilton_data, pee
 
 write_csv(all_units_data, here("outputs/data/all_units_data.csv"))
 
+

### 2021-02-15 scripts/04_clean_restaurant_list_csvs.R
Hamilton data clean up

@@ -78,8 +78,8 @@ hamilton_data <- clean_data("hamilton",
                             "inputs/data/hamilton_takeout.csv",
                             "outputs/data/hamilton_data.csv") %>% 
                             filter(!grepl("grocery|convenience|variety|store|market|private club|bakery|
-                            foodmart|food mart|bulk barn|canadian tire|church|gas|dollar|esso|fortinos|
-                            giant tiger|school|college|shop|petro|pioneer|pharma|legion|drug|express", name, ignore.case=TRUE))
+                            |foodmart|food mart|bulk barn|canadian tire|church|gas|dollar|esso|fortinos|
+                            |giant tiger|school|college|shop|petro|pioneer|pharma|legion|drug|express", name, ignore.case=TRUE))
 
 write_csv(hamilton_data, here("outputs/data/hamilton_data.csv"))
 

### 2021-02-15 scripts/07_service_type_parameterization.R
Service type percentage from Yelp data

@@ -1,0 +1,37 @@
+#### Preamble ####
+# Purpose: Use Yelp data to parameterize type of service (dine in/ dine in & takeout/takeout) for generating data
+# Author: Lorena Almaraz De La Garza
+# Date: 2021-02-15
+# Contact: l.almaraz@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: Needs CSV with Yelp restaurant data, available here: https://github.com/amycfarrow/ontariorestaurantclosuresexperiment/blob/main/inputs/data/yelp_restaurants_ontario.csv
+# TODO: 
+
+# Setup
+# install packages if needed
+library(ggplot2)
+library(here)
+library(tidyverse)
+
+# Read in data
+
+yelp_data <- read_csv(here("inputs/data/yelp_restaurants_ontario.csv"))
+
+# Check proportion of RestaurantsTakeOut
+
+takeout <- yelp_data %>% 
+  select(RestaurantsTakeOut)
+summary(takeout) # FALSE:834    TRUE :12972   NA's :3266    NONE: 7
+count(takeout) # COUNT: 17072
+
+takeout_percentage <- takeout %>%
+  group_by(RestaurantsTakeOut) %>% 
+  summarize(count = n()) %>%
+  mutate(percentage = count/sum(count))
+
+# Graph
+
+ggplot(takeout_percentage, aes(RestaurantsTakeOut, percentage, fill = RestaurantsTakeOut)) + 
+  geom_bar(stat='identity') + 
+  geom_text(aes(label=scales::percent(percentage)))+
+  scale_y_continuous(labels = scales::percent)

### 2021-02-16 outputs/paper/data_simulation.Rmd

@@
 library(kableExtra)  # for nicer tables
+library(here) # for working in projects
+
+```
+
+```{r}
+all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv"))
+
+all_units_data <- all_units_data %>%
+  mutate(group = case_when(unit == "brant" ~ "treatment",
+                           unit == "peel" ~ "treatment",
+                           unit == "sudbury" ~ "treatment",
+                           unit == "hamilton" ~ "control",
+                           unit == "southwestern" ~ "control",
+                           unit == "chatham" ~ "control"
+                           ))
+
+num_treat <- first(count(all_units_data %>%
+                   filter(group == "treatment")))
+
+num_control <- first(count(all_units_data %>%
+                   filter(group == "control")))
+
+num_total <- first(count(all_units_data))
+
+survey_1 <- all_units_data
+
+survey_2 <- all_units_data
 
@@
 
-# Sources of parameterization
+# Type of service provided
+LORENA
+## Survey 1
+```{r}
 
-# Methods of data simulation
+```
+
+## Survey 2
+```{r}
+
+```
+
+# Number of employees
+LALA
+## Survey 1
+```{r}
+
+```
+
+## Survey 2
+```{r}
+
+```
+
+# Revenue
+
+## Survey 1
+```{r}
+
+```
+
+## Survey 2
+```{r}
+
+```
+
+# Applications for government assistance
+LORENA
+## Survey 1
+```{r}
+
+```
+
+## Survey 2
+```{r}
+
+```
+
+# Demographic traits of owners
+AMY AND LALA
+## Survey 1
+```{r}
+
+```
+
+## Survey 2
+```{r}
+
+```
 

### 2021-02-16 scripts/05_import_yelp_restaurant_data.R
Edited Yelp data. Worked on demographic data.

@@ -46,6 +46,7 @@ yelp_business_on <- yelp_business_df[yelp_business_df$state == 'ON',] %>%
          RestaurantsPriceRange2,
          RestaurantsTakeOut,
          RestaurantsDelivery,
+         RestaurantsTableService,
          OutdoorSeating,
          categories,
          business_id

### 2021-02-16 scripts/08_ontario_restaurant_count_with_employee_count.R

@@ -1,0 +1,45 @@
+#### Preamble ####
+# Purpose: Get number of Ontario restaurants by number of restaurant employees from previous semi-annual reports
+# Author: Lala K. Sondjaja
+# Date: Sys.date()
+# Contact: k.sondjaja@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None
+
+### Install packages ###
+#devtools::install_github("warint/statcanR")
+#install.packages("tidyverse")
+
+### Load packages ###
+library(statcanR)
+library(tidyverse)
+
+### Get datasets from Statistics Canada ###
+### From 'Canadian Business Counts, with employees' from various dates ###
+
+#"Mobile food services [722330]"
+
+industry <- c("Special food services [7223]", "Drinking places (alcoholic beverages) [7224]", "Full-service restaurants and limited-service eating places [7225]")
+
+ontario <- statcan_data("33-10-0222-01", "eng") %>% filter(GEO=='Ontario')
+
+businesses_dec_2019 <- janitor::clean_names(statcan_data("33-10-0222-01", "eng") %>% filter(GEO=='Ontario', `North American Industry Classification System (NAICS)`%in% industry))
+businesses_june_2020 <- janitor::clean_names(statcan_data("33-10-0267-01", "eng") %>% filter(GEO=='Ontario', `North American Industry Classification System (NAICS)`%in% industry))
+businesses_dec_2020 <- janitor::clean_names(statcan_data("33-10-0304-01", "eng") %>% filter(GEO=='Ontario', `North American Industry Classification System (NAICS)`%in% industry))
+
+restaurants_by_employees <- function(x){
+  one_to_four <- sum(x$value[x$employment_size == "1 to 4 employees"])
+  five_to_nine <- sum(x$value[x$employment_size == "5 to 9 employees"])
+  ten_to_nineteen <- sum(x$value[x$employment_size == "10 to 19 employees"])
+  twenty_to_fortynine <- sum(x$value[x$employment_size == "20 to 49 employees"])
+  fifty_to_ninetynine <- sum(x$value[x$employment_size == "50 to 99 employees"])
+  hundred_to_199 <- sum(x$value[x$employment_size == "100 to 199 employees"])
+  twohundred_to_499 <- sum(x$value[x$employment_size == "200 to 499 employees"])
+  over_500 <- sum(x$value[x$employment_size == "500 plus employees"])
+  
[…]

### 2021-02-16 outputs/paper/data_simulation.Rmd

--- 2021-02-14 outputs/paper/data_simulation.Rmd
@@
 library(kableExtra)  # for nicer tables
+library(here) # for working in projects
+
+```
+
+```{r}
+# read in the data
+all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv"))
+
+# assign treatment and control based on health unit random selection
+all_units_data <- all_units_data %>%
+  mutate(group = case_when(unit == "brant" ~ "treatment",
+                           unit == "peel" ~ "treatment",
+                           unit == "sudbury" ~ "treatment",
+                           unit == "hamilton" ~ "control",
+                           unit == "southwestern" ~ "control",
+                           unit == "chatham" ~ "control"
+                           ))
+
+all_treat <- all_units_data %>%
+  filter(group == "treatment")
+
+all_control <- all_units_data %>%
+  filter(group == "control")
+
+# count the numbers for treat, control, and total
+num_treat <- first(count(all_treat))
+
+num_control <- first(count(all_control))
+
+num_total <- first(count(all_units_data))
+
+# randomly select 10% of total to be surveyed for #1, and recount.
+set.seed(24)
+survey_1 <- bind_rows(
+  all_treat %>%
+    mutate(surveyed = sample(x = c("yes", "no"),
+                             size = num_treat,
+                             prob = c(0.1, 0.9),
+                             replace = TRUE
+                             )) %>%
+    filter(surveyed == "yes"),
+  all_control %>%
+    mutate(surveyed = sample(x = c("yes", "no"),
+                             size = num_control,
+                             prob = c(0.1, 0.9),
+                             replace = TRUE
+                             )) %>%
+    filter(surveyed == "yes")
+)
+
+num_treat_1 <- first(count(survey_1 %>%
+                   filter(group == "treatment")))
+
+num_control_1 <- first(count(survey_1 %>%
+                   filter(group == "control")))
+
+num_total_1 <- first(count(survey_1))
+
+# randomly select 10% of total to be surveyed for #2, and recount.
+set.seed(25)
+survey_2 <- bind_rows(
+  all_treat %>%
+  mutate(surveyed = sample(x = c("yes", "no"),
+                           size = num_treat,
+                           prob = c(0.1, 0.9),
+                           replace = TRUE
+                           )) %>%
+  filter(surveyed == "yes"),
+  all_control %>%
+  mutate(surveyed = sample(x = c("yes", "no"),
+                           size = num_control,
+                           prob = c(0.1, 0.9),
+                           replace = TRUE
+                           )) %>%
+  filter(surveyed == "yes")
+)
+
+num_treat_2 <- first(count(survey_2 %>%
+                   filter(group == "treatment")))
+
+num_control_2 <- first(count(survey_2 %>%
+                   filter(group == "control")))
+
+num_total_2 <- first(count(survey_2))
 
@@
 
-# Sources of parameterization
+# Type of service provided
+LORENA
+## Survey 1
+```{r}
 
-# Methods of data simulation
+```
+
+## Survey 2
+```{r}
+
+```
+
+# Number of employees
+LALA
+## Survey 1
+```{r}
+
+```
+
+## Survey 2
+```{r}
+
+```
+
+# Revenue
+AMY
+
+## Survey 1
+```{r}
+
+```
+
+## Survey 2
+```{r}
+
+```
+
+# Applications for government assistance
+LORENA
+## Survey 1
+```{r}
+
+```
+
+## Survey 2
+```{r}
+
+```
+
+# Demographic traits of owners
+AMY AND LALA
+
+## Survey 1
+```{r}
+
+```
+
+## Survey 2
+
+Based on:https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3310028101
+there seems to be no significant difference in business losses for disabled owners.
+
+```{r}
+
+```
 

### 2021-02-16 outputs/paper/data_simulation.Rmd
rewriting sampling frame and simulation frame to ensure anonymity

--- 2021-02-14 outputs/paper/data_simulation.Rmd
@@
 library(kableExtra)  # for nicer tables
+library(here) # for working in projects
 
+```
+
+```{r}
+# read in the data
+# NOTE: scripts 01_scrape_health_depts and 02_sampling_frame must have been run already
+
+table_for_surveys <- read_csv(here::here("outputs/table_for_surveys.csv"))
+
+survey_1 <- table_for_surveys %>%
+  select(ID, group) %>%
+  arrange(ID)
+
+# count the numbers for treat, control, and total
+num_treat <- first(count(data %>%
+                           filter(group == "treatment")))
+
+num_control <- first(count(data %>% 
+                             filter(group == "control")))
+
+num_total <- first(count(data))
+
+survey_2 <- survey_1
+
+survey_1
 ```
@@
 
-# Sources of parameterization
+# Type of service provided
+LORENA
+## Survey 1
+```{r}
+survey_1 <- survey_1 %>%
+```
 
-# Methods of data simulation
+## Survey 2
+```{r}
+survey_2 <- survey_2 %>%
+```
+
+# Demographic traits of owners
+AMY AND LALA
+
+## Survey 1
+```{r}
+survey_1 <- survey_1 %>%
+```
+
+## Survey 2
+
+Based on:https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3310028101
+there seems to be no significant difference in business losses for disabled owners.
+
+```{r}
+survey_2 <- survey_2 %>%
+
+```
+
+# Shutdowns
+
+https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3310027601
+43.2% shut down temporarily
+
+https://nypost.com/2020/06/30/more-than-half-of-us-restaurants-closed-due-to-covid-19-study/
+3% closed permanently - but that was over far more than two weeks.
+
+# Survey 2
+```{r}
+set.seed(24)
+survey_2 <- bind_rows(
+  survey_2 %>%
+    filter(group == "treatment") %>%
+    mutate(shutdown = sample(c("none", "temporary", "permanent"), 
+                                                            size = num_treat, 
+                                                            prob = c(0.558, 0.432, 0.01),
+                                                            replace = TRUE))
+  ,
+  survey_2 %>%
+    filter(group == "control") %>%
+    mutate(shutdown = sample(c("none", "temporary", "permanent"), 
+                                                          size = num_control, 
+                                                          prob = c(.99, 0.005, 0.005),
+                                                          replace = TRUE))
+) %>%
+  arrange(ID)
+
+```
+
+# Revenue
+From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022201&pickMembers%5B0%5D=2.1&pickMembers%5B1%5D=3.423
+25,836 employers
+
+From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022301&pickMembers%5B0%5D=2.423
+6,968 non-employers
+
+So 32,804 businesses in 2019
+
+https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=2110017101&pickMembers%5B0%5D=1.7&pickMembers%5B1%5D=2.2&cubeTimeFrame.startYear=2015&cubeTimeFrame.endYear=2019&referencePeriods=20150101%2C20190101
+full-service restaurants have 13,456,600,000 in revenue in 2019.
+https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=2110017101&pickMembers%5B0%5D=1.7&pickMembers%5B1%5D=2.3&cubeTimeFrame.startYear=2015&cubeTimeFrame.endYear=2019&referencePeriods=20150101%2C20190101
+limited-service eating places have 14,082,700,000 in revenue in 2019.
+
+so averaging 839,510 in annual revenue.
+
+69,959 average per month.
+
+From http://www.mbel.io/2019/08/23/kaggle-restaurant-revenue-prediction/
+we can see the distribution looks like an F distribution, or a log normal distribution.
+rf(n, df1, df2, ncp) = rf(num_rest, 10, 5) should have a mean of 5/3
+so we would multiply by 41,975 to get the mean where we want.
+
+## Survey 1
+```{r}
+set.seed(24)
+survey_1 <- survey_1 %>%
+  mutate(revenue = 41975 * rf(num_total,10,5))
+```
+
+need to account for total and partial shutdowns: assume that total shutdowns cut revenue 75%, and partial cut revenue 50%
+
+from https://www.eater.com/2020/3/24/21184301/restaurant-industry-data-impact-covid-19-coronavirus
+revenues went from +5 to -35 when the shutdowns started. loss of -38. 
+but takeout only places need -0
+dine-in only places -100*14/31 = -45
+and combo places need -38*14/31 = -17
+
+####################### TODO: account for minority owned businesses
+
+## Survey 2
+```{r}
+survey_2 <- survey_2 %>%
+  mutate(revenue = 41975 * rf(num_total,10,5))
+
+survey_2 <-
+  bind_rows(
+    survey_2 %>%
+      filter(shutdown == "none") %>%
+      mutate(revenue = revenue)
+    ,
+    survey_2 %>%
+      filter(shutdown == "temporary") %>%
+      mutate(revenue = 0.50 * revenue)
+    ,
+    survey_2 %>%
+      filter(shutdown == "permanent") %>%
+      mutate(revenue = 0.25 * revenue)
+  ) %>%
+  arrange(ID)
+
+####################33 THIS WONT WORK UNTIL LORENA"S PART IS ADDED ON TYPE
+survey_2 <-
+  bind_rows(
+    survey_2 %>%
+      filter(type == "dinein" & group == "treatment") %>%
+      mutate(revenue = 0.55 * revenue)
+    ,
+    survey_2 %>%
+      filter(type == "both" & group == "treatment") %>%
+      mutate(revenue = 0.83 * revenue)
+    ,
+    survey_2 %>%
+      filter(type == "takeout" & group == "treatment") %>%
+      mutate(revenue = revenue)
+    ,
+    survey_2 %>%
+      filter(group == "control")
+  ) %>%
+  arrange(ID)
+
+survey_2 <-
+  bind_rows(
+    survey_2 %>%
+      filter(minority == "yes" & group == "treatment") %>%
+      mutate(revenue = 0.9 * revenue)
+    ,
+    survey_2 %>%
+      filter(minority == "no" & group == "treatment")
+    ,
+    survey_2 %>%
+      filter(group == "control")
+  )
+
+```
+
+# Number of employees
+LALA
+## Survey 1
+```{r}
+survey_1 <- survey_1 %>%
+```
+
+## Survey 2
+```{r}
+survey_2 <- survey_2 %>%
+```
+
+# Applications for government assistance
+LORENA
+## Survey 1
+```{r}
+survey_1 <- survey_1 %>%
+```
+
+## Survey 2
+```{r}
+survey_2 <- survey_2 %>%
+```
 

### 2021-02-16 scripts/02_sampling_frame.R

@@ -5,7 +5,7 @@
 # Contact: amy.farrow@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-# - Need to have run 01_scrape_health_depts.R
+# - Need to have run 01_scrape_health_depts
 
 
 #### Workspace setup ####
@@ -84,3 +84,49 @@ treatment_control_groups <-
 
 ### Save sampling ###
 write_csv(treatment_control_groups, here::here("outputs/treatment_control_groups.csv"))
+
+## assign groups on table of all treatment and control restaurants
+all_units_data <- all_units_data %>%
+  mutate(group = case_when(unit == "brant" ~ "treatment",
+                           unit == "peel" ~ "treatment",
+                           unit == "sudbury" ~ "treatment",
+                           unit == "hamilton" ~ "control",
+                           unit == "southwestern" ~ "control",
+                           unit == "chatham" ~ "control"
+  )) %>%
+  select(-type)
+
+
+# construct table to conduct the survey from.
+
+all_treat <- all_units_data %>%
+  filter(group == "treatment")
+
+all_control <- all_units_data %>%
+  filter(group == "control")
+
+
+set.seed(24)
+table_for_surveys <- bind_rows(
+  all_treat %>%
+    mutate(surveyed = sample(x = c("yes", "no"),
+                             size = first(count(all_treat)),
+                             prob = c(0.15, 0.85),
+                             replace = TRUE
+    )) %>%
+    filter(surveyed == "yes"),
+  all_control %>%
+    mutate(surveyed = sample(x = c("yes", "no"),
+                             size = first(count(all_control)),
+                             prob = c(0.15, 0.85),
+                             replace = TRUE
+    )) %>%
+    filter(surveyed == "yes")
+) 
+
+set.seed(24)
+table_for_surveys <- table_for_surveys %>%
+  mutate(ID = pull(tibble(sample(seq(1, first(count(table_for_surveys)), by = 1), size = first(count(table_for_surveys)), replace = FALSE)))) %>%
+  select(-surveyed)
+
+write_csv(table_for_surveys, here::here("outputs/table_for_surveys.csv"))

### 2021-02-17 scripts/04_clean_restaurant_list_csvs.R
Data cleanup for increased sample

@@ -51,15 +51,35 @@ clean_data <- function(unit, csv_r, csv_to, save_dir){
 
 # Use function for remaining health units
 
-chatham_kent_data <- clean_data("chatham",
-                                "inputs/data/chatham_kent_restaurants.csv",
-                                "inputs/data/chatham_kent_takeout.csv",
-                                "outputs/data/chatham_kent_data.csv")
+#chatham_kent_data <- clean_data("chatham",
+#                                "inputs/data/chatham_kent_restaurants.csv",
+#                                "inputs/data/chatham_kent_takeout.csv",
+#                                "outputs/data/chatham_kent_data.csv")
 
-peel_data <- clean_data("peel",
-                            "inputs/data/peel_restaurants.csv",
-                            "inputs/data/peel_takeout.csv",
-                            "outputs/data/peel_data.csv")
+#peel_data <- clean_data("peel",
+#                            "inputs/data/peel_restaurants.csv",
+#                            "inputs/data/peel_takeout.csv",
+#                            "outputs/data/peel_data.csv")
+
+algoma_data <- clean_data("algoma",
+                          "inputs/data/algoma_restaurants.csv",
+                          "inputs/data/algoma_takeout.csv",
+                          "outputs/data/algoma_data.csv")
+
+durham_data <- clean_data("durham",
+                           "inputs/data/durham_restaurants.csv",
+                           "inputs/data/durham_takeout.csv",
+                           "outputs/data/durham_data.csv")
+
+northwestern_data <- clean_data("northwestern",
+                          "inputs/data/northwestern_restaurants.csv",
+                          "inputs/data/northwestern_takeout.csv",
+                          "outputs/data/northwestern_data.csv")
+
+simcoe_data <- clean_data("simcoe",
+                                "inputs/data/simcoe_restaurants.csv",
+                                "inputs/data/simcoe_takeout.csv",
+                                "outputs/data/simcoe_data.csv")
 
 southwestern_data <- clean_data("southwestern",
                         "inputs/data/southwestern_restaurants.csv",
@@ -71,7 +91,22 @@ sudbury_data <- clean_data("sudbury",
                                 "inputs/data/sudbury_takeout.csv",
                                 "outputs/data/sudbury_data.csv")
 
-# Clean data further for Hamilton
+timiskaming_data <- clean_data("timiskaming",
[…]

### 2021-02-17 scripts/04_clean_restaurant_list_csvs.R
Data cleanup update

@@ -119,7 +119,7 @@ hamilton_data <- clean_data("hamilton",
 write_csv(hamilton_data, here("outputs/data/hamilton_data.csv"))
 
 
-haliburton_data <- clean_data("hamilton",
+haliburton_data <- clean_data("haliburton",
                             "inputs/data/haliburton_restaurants.csv",
                             "inputs/data/haliburton_restaurants.csv",
                             "outputs/data/haliburton_data.csv") %>% 

### 2021-02-17 outputs/paper/data_simulation.Rmd
add set seed

@@
 ---
-title: "Simulating data for the Ontario restaurant closures experiment"
+title: "Data for the Ontario Restaurant Closures Experiment"
 author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
@@
     toc: no
-subtitle: "SUBTITLE"
+subtitle: "Simulation Methods and Parameterization Research"
 abstract: "This document explains how data for the Ontario restaurant closures experiment was simulated, including the research that was used for parameterization and the methods used to randomize data."
@@
 # count the numbers for treat, control, and total
-num_treat <- first(count(data %>%
+num_treat <- first(count(survey_1 %>%
                            filter(group == "treatment")))
 
-num_control <- first(count(data %>% 
+num_control <- first(count(survey_1 %>% 
                              filter(group == "control")))
 
-num_total <- first(count(data))
+num_total <- first(count(survey_1))
 
@@
 
+https://www.ic.gc.ca/eic/site/061.nsf/eng/h_03115.html
+0.5% are owned by persons with disabilities
+
 ## Survey 1
 ```{r}
+set.seed(19893)
 survey_1 <- survey_1 %>%
+  mutate(disability = sample(c("yes", "no"),
+                             size = num_total,
+                             prob = c(0.005, .995),
+                             replace = TRUE))
+
+survey_1 <- survey_1 %>%
+
 ```
@@
 ```{r}
+set.seed(19893)
 survey_2 <- survey_2 %>%
+  mutate(disability = sample(c("yes", "no"),
+                             size = num_total,
+                             prob = c(0.005, .995),
+                             replace = TRUE))
 
+survey_2 <- survey_2 %>%
 ```
@@
 # Shutdowns
+
+# Survey 2
 
@@
 
-# Survey 2
 ```{r}
-set.seed(24)
+set.seed(19893)
 survey_2 <- bind_rows(
@@
 # Revenue
+
+## Survey 1
+
 From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022201&pickMembers%5B0%5D=2.1&pickMembers%5B1%5D=3.423
@@
 
-## Survey 1
 ```{r}
-set.seed(24)
+set.seed(19893)
 survey_1 <- survey_1 %>%
@@
 ```
+
+## Survey 2
 
@@
 
-####################### TODO: account for minority owned businesses
+https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3310028101
+all business had a median decrease of about 15%
+minority owned businesses had a median decrease of about 25%.
+Decrease of about 12%.
 
-## Survey 2
 ```{r}
+set.seed(19894)
 survey_2 <- survey_2 %>%
@@
       filter(minority == "yes" & group == "treatment") %>%
-      mutate(revenue = 0.9 * revenue)
+      mutate(revenue = 0.88 * revenue)
     ,

### 2021-02-17 outputs/paper/paper.Rmd
rewriting sampling frame and simulation frame to ensure anonymity

@@
 
+# NOTE: scripts 01_scrape_health_depts and 02_sampling_frame, 
+# and markdown file data_simulation must have been run already
+
 ```
@@
 # Data
+
+```{r}
+treatment_control_groups
+```
+
+```{r}
+all_units_data
+```
+
+```{r}
+table_for_surveys
+```
+
+```{r}
+
+```
 
@@
 ### FINDING ONE
+ Closures had a negative impact
 
 ### FINDING TWO
+Closures had a stronger negative impact on dine-in only restaurants
 
 ### FINDING THREE
+CLosures had a stronger negative impact on POC-owned
 

### 2021-02-17 outputs/paper/data_simulation.Rmd
stitching together simulation work and tidying file names

@@
 # read in the data
-# NOTE: scripts 01_scrape_health_depts and 02_sampling_frame must have been run already
+# NOTE: scripts 01_scrape_health_depts, 04_clean_restaurant_list_csvs, and 02_sampling_frame must have been run already
 
@@
 survey_1 <- table_for_surveys %>%
-  select(ID, group) %>%
+  select(ID, group, verify) %>%
   arrange(ID)
@@
 # Type of service provided
-LORENA
+```{r}
+# Read in data
+yelp_data <- read_csv(here("inputs/data/yelp_restaurants_ontario.csv")) %>% 
+  na.omit() # Remove all NAs
+total_restaurants <- count(yelp_data)
+
+# Check proportion of RestaurantsTakeOut
+takeout <- yelp_data %>% 
+  select(RestaurantsTakeOut)
+summary(takeout)
+```
+```{r}
+takeout_percentage <- takeout %>%
+  group_by(RestaurantsTakeOut) %>% 
+  summarize(count = n()) %>%
+  mutate(percentage = count/sum(count))
+
+takeout_percentage
+```
+```{r}
+# Check proportion of RestaurantsTableService
+tableserv <- yelp_data %>% 
+  select(RestaurantsTableService)
+summary(tableserv)
+```
+```{r}
+tableserv_percentage <- tableserv %>%
+  group_by(RestaurantsTableService) %>% 
+  summarize(count = n()) %>%
+  mutate(percentage = count/sum(count))
+
+tableserv_percentage
+```
+
+```{r}
+# Calculate invalid responses (neither dine-in nor takeout)
+invalid <- yelp_data %>% 
+  filter(RestaurantsTableService == FALSE & RestaurantsTakeOut == FALSE) %>% 
+  count()
+
+valid_restaurants <- total_restaurants-invalid
+
+# Calculate service type percentages
+takeout_only <- yelp_data %>% 
+  filter(RestaurantsTableService == FALSE & RestaurantsTakeOut == TRUE) %>% 
+  count()/valid_restaurants
+
+dinein_only <- yelp_data %>% 
+  filter(RestaurantsTableService == TRUE & RestaurantsTakeOut == FALSE) %>% 
+  count()/valid_restaurants
+
+both <- yelp_data %>% 
+  filter(RestaurantsTableService == TRUE & RestaurantsTakeOut == TRUE) %>% 
+  count()/valid_restaurants
+
+service_percentage<- data.frame(
+  service = c("takeout", "dinein", "both"),
+  percentage = c(takeout_only$n, dinein_only$n, both$n), options(digits = 2)
+)
+
+ service_percentage
+```
+According to Ontario restaurant data from Yelp (cite, KSondjaja source), approximately 6% of restaurants
+offer dine in service, 32.5% offer takeout, and 61.5% offer both.
+
 ## Survey 1
 ```{r}
+set.seed(19)
 survey_1 <- survey_1 %>%
+  mutate(service_type = sample(x = c("dinein",
+                                     "both",
+                                     "takeout"),
+      size = num_total,
+      replace = TRUE, 
+      prob = c(0.06, 0.615, 0.325)
+      ))
 ```
@@
 ```{r}
+set.seed(19)
 survey_2 <- survey_2 %>%
+  mutate(service_type = sample(x = c("dinein",
+                                     "both",
+                                     "takeout"),
+      size = num_total,
+      replace = TRUE, 
+      prob = c(0.06, 0.615, 0.325)
+      ))
 ```
@@
 # Demographic traits of owners
-AMY AND LALA
 
@@
 ```{r}
-set.seed(19894)
+set.seed(19893)
 survey_2 <- survey_2 %>%
-  mutate(revenue = 41975 * rf(num_total,10,5))
+  mutate(revenue = 41975 * rf(num_total,10,5)) %>%
+  mutate(factor = abs(rnorm(num_total, 1, .05))) %>%
+  mutate(revenue = factor * revenue) %>%
+  select(-factor)
 
@@
 
-####################33 THIS WONT WORK UNTIL LORENA"S PART IS ADDED ON TYPE
 survey_2 <-
@@
     survey_2 %>%
-      filter(type == "dinein" & group == "treatment") %>%
+      filter(service_type == "dinein" & group == "treatment") %>%
       mutate(revenue = 0.55 * revenue)
@@
     survey_2 %>%
-      filter(type == "both" & group == "treatment") %>%
+      filter(service_type == "both" & group == "treatment") %>%
       mutate(revenue = 0.83 * revenue)
@@
     survey_2 %>%
-      filter(type == "takeout" & group == "treatment") %>%
+      filter(service_type == "takeout" & group == "treatment") %>%
       mutate(revenue = revenue)

### 2021-02-17 outputs/paper/paper.Rmd
stitching together simulation work and tidying file names

@@
 
-# NOTE: scripts 01_scrape_health_depts and 02_sampling_frame, 
+# NOTE: scripts 01_scrape_health_depts, 04_clean_restaurant_list_csvs, and 02_sampling_frame, 
 # and markdown file data_simulation must have been run already
@@
 ```{r}
+treatment_control_groups <- read_csv(here::here("outputs/treatment_control_groups.csv"))
 treatment_control_groups
@@
 ```{r}
+all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv"))
 all_units_data
@@
 ```{r}
+table_for_surveys <- read_csv(here::here("outputs/table_for_surveys.csv"))
 table_for_surveys

### 2021-02-17 scripts/02_stratified_cluster_sampling.R

@@ -5,7 +5,7 @@
 # Contact: amy.farrow@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-# - Need to have run 01_scrape_health_depts
+# - Need to have run 01 script
 
 
 #### Workspace setup ####
@@ -87,57 +87,3 @@ treatment_control_groups <-
 
 ### Save sampling ###
 write_csv(treatment_control_groups, here::here("outputs/treatment_control_groups.csv"))
-
-all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv"))
-## assign groups on table of all treatment and control restaurants
-all_units_data <- all_units_data %>%
-  mutate(group = case_when(unit == "hamilton" ~ "treatment",
-                           unit == "simcoe" ~ "treatment",
-                           unit == "haliburton" ~ "treatment",
-                           unit == "windsor" ~ "treatment",
-                           unit == "algoma" ~ "treatment",
-                           unit == "timiskaming" ~ "treatment",
-                           unit == "durham" ~ "control",
-                           unit == "waterloo" ~ "control",
-                           unit == "southwestern" ~ "control",
-                           unit == "sudbury" ~ "control",
-                           unit == "brant" ~ "control",
-                           unit == "northwestern" ~ "control"
-  )) %>%
-  select(-type)
-
-
-# construct table to conduct the survey from.
-
-all_treat <- all_units_data %>%
-  filter(group == "treatment")
-
-all_control <- all_units_data %>%
-  filter(group == "control")
-
-
-set.seed(19893)
-table_for_surveys <- bind_rows(
-  all_treat %>%
-    mutate(surveyed = sample(x = c("yes", "no"),
-                             size = first(count(all_treat)),
-                             prob = c(0.15, 0.85),
-                             replace = TRUE
-    )) %>%
-    filter(surveyed == "yes"),
-  all_control %>%
-    mutate(surveyed = sample(x = c("yes", "no"),
-                             size = first(count(all_control)),
-                             prob = c(0.15, 0.85),
-                             replace = TRUE
-    )) %>%
-    filter(surveyed == "yes")
-) 
-
-set.seed(19893)
-table_for_surveys <- table_for_surveys %>%
-  mutate(verify = substr(address, -3, -1)) %>%
[…]

### 2021-02-17 scripts/03_clean_restaurant_list_csvs.R

@@ -114,7 +114,8 @@ hamilton_data <- clean_data("hamilton",
                             "outputs/data/hamilton_data.csv") %>% 
                             filter(!grepl("grocery|convenience|variety|store|market|private club|bakery|
                             |foodmart|food mart|bulk barn|canadian tire|church|gas|dollar|esso|fortinos|
-                            |giant tiger|school|college|shop|petro|pioneer|pharma|legion|drug|express", name, ignore.case=TRUE))
+                            |giant tiger|school|college|shop|petro|pioneer|pharma|legion|drug|express|
+                            wee watch|club|centre|camp|valu|sobeys|shell|army|park|community|meals", name, ignore.case=TRUE))
 
 write_csv(hamilton_data, here("outputs/data/hamilton_data.csv"))
 
@@ -125,7 +126,8 @@ haliburton_data <- clean_data("haliburton",
                             "outputs/data/haliburton_data.csv") %>% 
                             filter(!grepl("grocery|convenience|variety|store|market|private club|bakery|
                             |foodmart|food mart|bulk barn|canadian tire|church|gas|dollar|esso|fortinos|
-                            |giant tiger|school|college|shop|petro|pioneer|pharma|legion|drug|express", name, ignore.case=TRUE))
+                            |giant tiger|school|college|shop|petro|pioneer|pharma|legion|drug|express|
+                            wee watch|club|centre|camp|valu|sobeys|shell|army|park|community|meals", name, ignore.case=TRUE))
 
 write_csv(haliburton_data, here("outputs/data/haliburton_data.csv"))
 

### 2021-02-17 scripts/03_scrape_peel_restaurants.R

@@ -1,24 +1,0 @@
-#### Preamble ####
-# Purpose: Get a tibble of all health units in Ontario
-# Author: Amy Farrow
-# Date: 2021-02-10
-# Contact: amy.farrow@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
-
-
-
-######## TODO: (optional) write this script rather than copying the csvs the tables and saving.
-
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(RCurl)
-library(here)
-library(XML)
-
-
-### Get raw data ###
-peel_restaurants_raw <- getURL("http://rmop.hedgerowsoftware.com/Portal/Food/Table?SortMode=FacilityName&page=1&PageSize=100000",
-                               cookiefile = )

### 2021-02-17 outputs/paper/paper.Rmd
adding explanations, census data

@@
 
-```{r}
+#TODO: citations for R and all packages used.
+
+This experiment used two-stage stratified cluster sampling with survey data collection.
+
+The population was all restaurants in Ontario.
+
+A list of Ontario local health authorities (LHAs) that carry out food inspections was used to identify units that inspect restaurants.
+Using census data from 2016, these LHAs were sorted by population covered by the LHA, and the list was stratified into equally sized strata of small (less than 150,000 population), medium (150,000 to 400,000 population), and large (more than 400,000 population) LHAs.
+This list of stratified LHAs was the frame at the cluster level.
+
+From each strata, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control. This was the sample at the cluster level.
+
+The clusters were used because pandemic shutdowns operated based on LHA, and the goal was to recreate the effect as closely as possible.
+
+The stratification was used because there were very differently sized LHAs, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of unequivalent treatment and control groups.
+
+```{r treatmentcontrolgroups}
 treatment_control_groups <- read_csv(here::here("outputs/treatment_control_groups.csv"))
@@
 ```
+
+Once the treatment and control LHAs were selected, each corresponding Food Inspection unit was contacting, and a list of all registered restaurants in each LHA was obtained.
+Each restaurant was listed by name and address.
+Once collected into one dataframe, this was the frame at the unit level.
 
@@
 
+A simple random sample of 15% of the treatment list and 15% of the control list was randomly selected to be surveyed. This was the sample at the unit level.
+
+This selection was used to create a panel, so the same restaurants would be surveyed for the first survey and the second survey.
+Attempting to sample only 15% of the restaurants allowed time and money to be spent on follow-up and multiple methods of data collecting, reducing the non-response bias.
+
 ```{r}
@@
 ```
+The randomly sampled restaurants were all assigned ID numbers in a random order.
+
+The table for surveys was used to generate 2,006 mailers to be sent to each restaurant on the list.
+Each mailer was a small envelope containing a sheet that explained the survey, provided a link to the survey, and provided a QR code that went to the same place as the link.
+There was also a copy of the survey contained in a mailer envelope and a contact number, allowing restaurant owners to complete the survey by phone or mail if they did not feel able to complete it online.
+This procedure was repeated for Survey 1 and Survey 2.
+If there was no response within two weeks, the restaurant was contacted by phone, and again if there was no response five days later.
+
+Each link and paper survey was personalized to the restaurant's ID number.
+The link lead to the survey, which asked for confirmation of the last three letters of the restaurant's postal code.
+This was to ensure that no mailing mistakes were made, and to prevent duplicate data collection.
+Once verified, the survey-taker was given the main survey.
+
+The data from the survey was tied to the ID number and last three digits of the postal code, but not the restaurant name or address.
+This was to ensure data privacy.
+The identifying information was kept in a separate dataframe (Table for Surveys) than the survey answers (Survey 1 Data, Survey 2 Data).
 
 ```{r}
+survey_1_data <- read_csv(here::here("outputs/survey__data.csv"))
+survey_1_data
+```
 
+Survey 1 was conducted June 3rd to 27th 2021, and it asked about May 2021.
+
+Survey 1 Data was used to confirm that the two-stage stratified cluster sampling had created treatment and control groups that were roughly equivalent.
+
+Survey 1 collected the following data:
+
+* Demographic information
+- Disability status
+- Indigenous status
+- Visible minority (non-Indigenous) status
+* Type of service provided (dine-in, take-out, or both)
+* Revenue in May 2021
+* Employees
+- Number of full-time employees (30 hours/week or more)
+- Number of part-time employees (less than 30 hours/week)
+* Applications for government assistance
+- Which funds were applied for
+- Estimated money received
+
+Distributions for revenue and tables for key demographics were compared.
+
+```{r}
+survey_2_data <- read_csv(here::here("outputs/survey_2_data.csv"))
+survey_2_data
 ```
+
+After Survey 1 data was collected, on June 28th, shutdowns were announced for the six treatment LHAs.
+The shutdowns ran from July 1s to July 14th, inclusive.
+This length of time was considered to be the minimum effective length for a shutdown to stop circulation of the virus.
+During the shutdown, all restaurants in the treatment LHAs were officially banned from offering dine-in and patio services.
+Take-out and delivery were permitted.
+This type of partial shutdown was selected because it has been the most common type of shutdown since the pandemic began.
+
+Survey 2 was conducted August 3rd to 27th 2021, and it asked about July 2021.
+
+Survey 2 collected the following data:
+
+* Demographic information
+- Disability status
+- Indigenous status
+- Visible minority (non-Indigenous) status
+* Type of service provided (dine-in, take-out, or both)
+* Closures (none, temporary, or permanent)
+* Revenue in May 2021
+* Employees
+- Number of full-time employees (30 hours/week or more)
+- Number of part-time employees (less than 30 hours/week)
+* Applications for government assistance
+- Which funds were applied for
+- Estimated money received
 

### 2021-02-17 outputs/paper/data_simulation.Rmd
editing census 2016 import for population parameterization; adding text to start paper; updating references for simulation file

@@
 
-```{r}
+```{r surveyframe}
 # read in the data
@@
 # Type of service provided
+
 ```{r}
@@
 
-https://www.ic.gc.ca/eic/site/061.nsf/eng/h_03115.html
-0.5% are owned by persons with disabilities
+0.5% of small to medium enterprises in Canada are owned by persons with disabilities [@ownershipdemos].
 
@@
                              replace = TRUE))
-
-survey_1 <- survey_1 %>%
-
 ```
@@
 ## Survey 2
-
-Based on:https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3310028101
-there seems to be no significant difference in business losses for disabled owners.
-
 ```{r}
@@
                              replace = TRUE))
+```
 
+Download link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058 ###
+GEO_CODE indicates public health regions, taken from Census 2016 links:
+https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0
+```{r}
+### Load census dataset by Health Regions ###
+census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
+census_2016 <- janitor::clean_names(census_2016)
+
+### Select demographic data to include, relating to employment, income, immigration status, minority groups, commute, etc. ###
+# Many categories
+# demographic_info <- c(1, 6, 8:33, 60:67, 100:104, 661:663, 694:707, 724:726, 1135:1136, 1139, 1140:1150, 1157, 1158, 1170, 1188, 1198, 1216, 1287, 1289:1292, 1324:1337, 1683:1697, 1884:1929)
+
+# Narrowed down categories
+demographic_info <- c(1, 8, 1324, 1290, 1917)
+
+### Function to get data from specific regions and rows ###
+
+get_region_data <- function(y){
+  census_2016 %>%
+    filter(geo_code_por == y,
+           member_id_profile_of_health_regions_2247 %in% demographic_info) %>%
+    select(dim_profile_of_health_regions_2247, member_id_profile_of_health_regions_2247, dim_sex_3_member_id_1_total_sex, dim_sex_3_member_id_2_male, dim_sex_3_member_id_3_female)
+}
+
+### Get data from the randomly selected Health Regions ###
+
+ontario <- get_region_data(35)
+
+haliburton <- get_region_data(3535)
+hamilton <- get_region_data(3537)
+algoma <- get_region_data(3526)
+simcoe_muskoka <- get_region_data(3560)
+timiskaming <- get_region_data(3563)
+windsor_essex <- get_region_data(3568)
+
+northwest <- get_region_data(3549)
+# southwestern <- get_region_data(3502)
+# Southwestern is a newer health unit. it was created by almagamating oxford and elgin-st. thomas units:
+oxford <- get_region_data(3552)
+elgin <- get_region_data(3531)
+waterloo <- get_region_data(3565)
+durham <- get_region_data(3530)
+sudbury <- get_region_data(3561)
+brant <- get_region_data(3527)
+
+### Put together demographic info in one table ###
+
+populationss <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
+
+get_pop_info <- function(x){
+  c(as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Population, 2016"]),
+    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Aboriginal identity"]),
+    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Total visible minority population"]),
+    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "72 Accommodation and food services"]),
+    as.numeric(x$dim_sex_3_member_id_3_female[x$dim_profile_of_health_regions_2247 == "Total - Age groups and average age of the population - 100% data"]))
+}
+
+ontario_pop <- get_pop_info(ontario)
+
+haliburton_pop <- get_pop_info(haliburton)
+algoma_pop <- get_pop_info(algoma)
+hamilton_pop <- get_pop_info(hamilton)
+windsor_essex_pop <- get_pop_info(windsor_essex)
+simcoe_muskoka_pop <- get_pop_info(simcoe_muskoka)
+timiskaming_pop <- get_pop_info(timiskaming)
+
+brant_pop <- get_pop_info(brant)
+sudbury_pop <- get_pop_info(sudbury)
+#southwestern_pop <- get_pop_info(southwestern)
+oxford_pop <- get_pop_info(oxford)
+elgin_pop <- get_pop_info(elgin)
+northwest_pop <- get_pop_info(northwest)
+waterloo_pop <- get_pop_info(waterloo)
+durham_pop <- get_pop_info(durham)
+
+populations <- bind_cols(populationss, ontario_pop, haliburton_pop, algoma_pop, hamilton_pop, windsor_essex_pop, simcoe_muskoka_pop, timiskaming_pop, brant_pop, sudbury_pop, oxford_pop, elgin_pop, northwest_pop, waterloo_pop, durham_pop)
+
+colnames(populations) <- c("Info", "Ontario", "Haliburton", "Algoma", "Hamilton", "Windsor_Essex", "Simcoe_Muskoka", "Timiskaming",
+                           "Brant", "Sudbury", "Oxford", "Elgin", "Northwest", "Waterloo", "Durham")
+
+populations <- populations %>%
+  mutate(Southwestern = Oxford + Elgin) %>%
+  mutate(total_treat = Haliburton + Algoma + Hamilton + Windsor_Essex + Simcoe_Muskoka + Timiskaming,
+         total_control = Brant + Sudbury + Northwest + Waterloo + Durham + Southwestern) %>%
+  select(-Oxford, -Elgin)
+
+populations
+```
+
+```{r}
+populations_split <- matrix(ncol=4, nrow=5)
+populations_split[,1] <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
+populations_split[,2] <- ontario_pop
+
+total_pop_treatment <- sum(populations[1,c(3:8)])
+indigenous_treatment <- sum(populations[2,c(3:8)])
+minority_treatment <- sum(populations[3,c(3:8)])
+food_services_treatment <- sum(populations[4,c(3:8)])
+women_treatment <- sum(populations[5,c(3:8)])
+
+treatment <- c(total_pop_treatment, indigenous_treatment, minority_treatment, food_services_treatment, women_treatment)
+populations_split[,3] <- treatment
+
+total_pop_control <- sum(populations[1,c(9:14)])
+indigenous_control <- sum(populations[2,c(9:14)])
+minority_control <- sum(populations[3,c(9:14)])
+food_services_control <- sum(populations[4,c(9:14)])
+women_control <- sum(populations[5,c(9:14)])
+
+control <- c(total_pop_control, indigenous_control, minority_control, food_services_control, women_control)
+populations_split[,4] <- control
+
+populations_split <- as.data.frame(populations_split)
+colnames(populations_split) <- c("Info", "Ontario", "Treatment", "Control")
+
+populations_split
+```
+
+```{r}
+### Get percentage proportions of demographic groups of interest ###
+
+populations_split_percentage <- matrix(ncol=4, nrow=5)
+
+for(i in 2:length(populations_split)){
+  for(j in 1:5){
+    populations_split_percentage[j,i] <- round(as.numeric(populations_split[j,i])/as.numeric(populations_split[1,i]), digits=3)
+  }
+}
+
+#populations_percentage[1, 2:4] <- c(1, 1, 1)
+populations_split_percentage[,1] <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
+
+populations_split_percentage <- as.data.frame(populations_split_percentage)
+colnames(populations_split_percentage) <- c("Info", "Ontario", "Treatment", "Control")
+
+populations_split_percentage
+```
+https://www150.statcan.gc.ca/n1/pub/89-656-x/89-656-x2015001-eng.htm
+Indigenous groups are 4% of the population.
+
+https://www.statcan.gc.ca/eng/dai/btd/othervisuals/other010
+visible minorities are 25% of the population
+
+https://www.ic.gc.ca/eic/site/061.nsf/eng/h_03115.html
+1.4% of business owners are indigenous, and 12.2% are visible minorities.
+
+Therefore, Indigenous people are 0.35 times as likely to own a business, and visible minorities are 0.49 as likely to own a business.
+
+## Survey 1
+```{r}
+set.seed(19893)
+survey_1 <- survey_1 %>%
+  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD MINORITY DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+```
+
+## Survey 2
+
+```{r}
+set.seed(19893)
 survey_2 <- survey_2 %>%
+  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD MINORITY DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 ```
@@
 
-https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3310027601
-43.2% shut down temporarily
+43.2% of restaurants shut down temporarily due to the pandemic [@covid19impactonbusiness].
 
-https://nypost.com/2020/06/30/more-than-half-of-us-restaurants-closed-due-to-covid-19-study/
-3% closed permanently - but that was over far more than two weeks.
+3% closed of restaurants in the US closed permanently between March and June [@restaurantclosures]. This period was about six times as long as our two week closure.
 
@@
 
-From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022201&pickMembers%5B0%5D=2.1&pickMembers%5B1%5D=3.423
-25,836 employers
+In 2019, there were 25,836 restaurants and eating-places that were employers [@businesseswithemployees] and 6,968 restaurants that were not employers [@businesseswithoutemployees] in Canada, for a total of 32,804 restaurants.
 
-From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022301&pickMembers%5B0%5D=2.423
-6,968 non-employers
+In the same year, full-service restaurants had \$13,456,600,000 in revenue, and limited-service eating places had \$14,082,700,000 in revenue [@foodservicessummary].
 
-So 32,804 businesses in 2019
+From this, we can calculate an estimated \$69,959 average revenue per month.
 
-https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=2110017101&pickMembers%5B0%5D=1.7&pickMembers%5B1%5D=2.2&cubeTimeFrame.startYear=2015&cubeTimeFrame.endYear=2019&referencePeriods=20150101%2C20190101
-full-service restaurants have 13,456,600,000 in revenue in 2019.
-https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=2110017101&pickMembers%5B0%5D=1.7&pickMembers%5B1%5D=2.3&cubeTimeFrame.startYear=2015&cubeTimeFrame.endYear=2019&referencePeriods=20150101%2C20190101
-limited-service eating places have 14,082,700,000 in revenue in 2019.
-
-so averaging 839,510 in annual revenue.
-
-69,959 average per month.
-
-From http://www.mbel.io/2019/08/23/kaggle-restaurant-revenue-prediction/
-we can see the distribution looks like an F distribution, or a log normal distribution.
-rf(n, df1, df2, ncp) = rf(num_rest, 10, 5) should have a mean of 5/3
-so we would multiply by 41,975 to get the mean where we want.
+From an analysis of Kaggle restaurant data [@kagglerestaurantdata], we can see that restaurant revenue looks like an F distribution.
+The distribution rf(n, df1, df2, ncp) = rf(num_rest, 10, 5) gives an approximate shape.
+Using the f-distribution formula, we know the distribution has a mean of 5/3, so we would multiply by 41,975 to get the mean to 69,959.
 
@@
 
-need to account for total and partial shutdowns: assume that total shutdowns cut revenue 75%, and partial cut revenue 50%
+First, the revenues from the first survey will have a randomized factor (normal distribution with a mean of 1 and a standard distribution of 0.1) to add some random variance between months.
 
-from https://www.eater.com/2020/3/24/21184301/restaurant-industry-data-impact-covid-19-coronavirus
-revenues went from +5 to -35 when the shutdowns started. loss of -38. 
-but takeout only places need -0
-dine-in only places -100*14/31 = -45
-and combo places need -38*14/31 = -17
+Second, places that are closed permanently will be assumed to experience -75% average revenue, and temporary shutdowns will be assumed to experience -50% revenue.
 
-https://www150.statcan.gc.ca/t1/tbl1/en/cv.action?pid=3310028101
-all business had a median decrease of about 15%
-minority owned businesses had a median decrease of about 25%.
-Decrease of about 12%.
+Revenues went to -35% during the first lockdown wave in March [@bythenumbers].
+We will assume that these numbers are accurate for a dine-in/takeout restaurant that is experiencing a takeout-only closure.
+They are closed 14 out of 31 days, so we will assume average losses of -17%.
+
+We will assume that takeout-only restaurants will not have losses on average, and dine-in only places will have -100% revenue on average for the days they are closed.
+With closures 14 out of 31 days in the month, dine-in only will have average losses of -45%.
+
+All businesses had a median decrease of -15%, but visible minority-owned businesses had a median decrease of -25% [@aug20192020].
+Therefore, an additional -12% will be applied to visible minority-owned restaurants.
+
+There seems to be no significant difference in business losses for disabled owners [@aug20192020].
 
@@
   mutate(revenue = 41975 * rf(num_total,10,5)) %>%
-  mutate(factor = abs(rnorm(num_total, 1, .05))) %>%
+  mutate(factor = abs(rnorm(num_total, 1, .1))) %>%
   mutate(revenue = factor * revenue) %>%
@@
 
+<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<CHECK IF THIS WORKS ONCE MINORITY DATA IS ADDED AMY>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 survey_2 <-
@@
 survey_1 <- survey_1 %>%
+  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD EMPLOYMENT DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 ```
@@
 survey_2 <- survey_2 %>%
+  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD EMPLOYMENT DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 ```
@@
 survey_1 <- survey_1 %>%
+  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD ASSISTANCE DATA SIMULATION HERE LORENA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 ```
@@
 survey_2 <- survey_2 %>%
+  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD ASSISTANCE DATA SIMULATION HERE LORENA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+```
+
+# Non-response
+
+A professional mail survey with follow up found a non-response rate of 61% [@nonresponse].
+We will also assume that some people will mail in answers and fill in the form incompletely.
+
+```{r}
+num_cols_1 = number of columns in the tibble <<<<<<<<<<<<<<<<<<<<<<<SET AMY>>>>>>>>>>>>>>>>>>>>
+
+set.seed(19893)
+survey_1 <- survey_1 %>%
+  mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
+  filter(nonresponse != "no")
+
+set.seed(19893)
+survey_1 <- survey_1 %>%
+  mutate(which_partial = sample(c(4:num_cols_1), size = first(count(survey_1)), replace = TRUE))
+
+for (i in c(1:as.numeric(count(survey_1)))){
+  if (survey_1[i, "nonresponse"] == "partial") {
+    survey_1[i, as.numeric(survey_1[i,"which_partial"])] <- NA
+  }
+}
+
+survey_1 <- survey_1 %>%
+  select(-nonresponse, -which_partial)
+
+```
+
+```{r}
+num_cols_2 = number of columns in the tibble <<<<<<<<<<<<<<<<<<<<<<<SET AMY>>>>>>>>>>>>>>>>>>>>
+
+set.seed(19894)
+survey_2 <- survey_2 %>%
+  mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
+  filter(nonresponse != "no")
+
+set.seed(19894)
+survey_2 <- survey_2 %>%
+  mutate(which_partial = sample(c(4:num_cols_1), size = first(count(survey_2)), replace = TRUE))
+
+for (i in c(1:as.numeric(count(survey_2)))){
+  if (survey_2[i, "nonresponse"] == "partial") {
+    survey_2[i, as.numeric(survey_2[i,"which_partial"])] <- NA
+  }
+}
+
+survey_2 <- survey_2 %>%
+  select(-nonresponse, -which_partial)
 ```

### 2021-02-17 scripts/06_import_2016_census_data.R

@@ -21,7 +21,7 @@ library(janitor)
 ### GEO_CODE indicates public health regions, taken from Census 2016 links:
 ### https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0
 
-census_2016 <- read.csv(here("inputs", "data", "98-401-X2016058_English_CSV_data.csv"))
+census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
 census_2016 <- janitor::clean_names(census_2016)
 
 names(census_2016)
@@ -46,7 +46,7 @@ get_region_data <- function(y){
 
 ### Get data from the randomly selected Health Regions ###
 
-canada <- get_region_data(1)
+ontario <- get_region_data(35)
 
 haliburton <- get_region_data(3535)
 hamilton <- get_region_data(3537)
@@ -55,8 +55,11 @@ simcoe_muskoka <- get_region_data(3560)
 timiskaming <- get_region_data(3563)
 windsor_essex <- get_region_data(3568)
 
-northwest <- get_region_data(3514)
-southwestern <- get_region_data(3502)
+northwest <- get_region_data(3549)
+# southwestern <- get_region_data(3502)
+# Southwestern is a newer health unit. it was created by almagamating oxford and elgin-st. thomas units:
+oxford <- get_region_data(3552)
+elgin <- get_region_data(3531)
 waterloo <- get_region_data(3565)
 durham <- get_region_data(3530)
 sudbury <- get_region_data(3561)
@@ -65,7 +68,7 @@ brant <- get_region_data(3527)
 
 ### Put together demographic info in one table ###
 
-populations <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
+populationss <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
 
 get_pop_info <- function(x){
   c(as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Population, 2016"]),
@@ -75,7 +78,7 @@ get_pop_info <- function(x){
[…]

### 2021-02-18 outputs/paper/data_simulation.Rmd
merging .bibs, adding reminders to paper, and removing government funding

@@
     survey_2 %>%
-      filter(minority == "yes" & group == "treatment") %>%
+      filter((minority == "yes" | indigenous == "yes") & group == "treatment") %>%
       mutate(revenue = 0.88 * revenue)
@@
   <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD EMPLOYMENT DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-```
-
-# Applications for government assistance
-LORENA
-## Survey 1
-```{r}
-survey_1 <- survey_1 %>%
-  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD ASSISTANCE DATA SIMULATION HERE LORENA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
-```
-
-## Survey 2
-```{r}
-survey_2 <- survey_2 %>%
-  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD ASSISTANCE DATA SIMULATION HERE LORENA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 ```

### 2021-02-18 outputs/paper/paper.Rmd

@@
 
+This survey cost <<<<<<<<LORENA>>>>>>>>>>>>>.
+
 The data from the survey was tied to the ID number and last three digits of the postal code, but not the restaurant name or address.
@@
 - Visible minority (non-Indigenous) status
+- Gender identity
 * Type of service provided (dine-in, take-out, or both)
@@
 - Number of part-time employees (less than 30 hours/week)
-* Applications for government assistance
-- Which funds were applied for
-- Estimated money received
 
@@
 - Number of part-time employees (less than 30 hours/week)
-* Applications for government assistance
-- Which funds were applied for
-- Estimated money received
+
+Survey 1 data as baseline
+
+Counterfactuals
+
+Survey 2 data to contrast treatment and control.
 
@@
 ### FINDING ONE
- Closures had a negative impact
+Closures had a negative impact on revenues and employment counts
+
+Suggestion: funding for businesses and temporary unemployment
 
@@
 
+Suggestions: technical support for restaurants to increase takeout business
+
 ### FINDING THREE
-CLosures had a stronger negative impact on POC-owned
+Closures had a stronger negative impact on indigenous or visible minority-owned businesses.
+
+Suggestions: grants for minority business owners
 
@@
 
+External validity, internal validity, cluster sampling. Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them.
+
+Legally registered businesses only.
+
+Survey non-response.
+
+Self-reported information.
+
 ## Future Directions
+
+For statistical analysis, this would require propensity score weighting.
+
+\newpage
+
+# Appendix {-}
 

### 2021-02-18 outputs/paper/data_simulation.Rmd
data simulation done, all in-text references in data_simulation, first test knits run on both paper and data_simulation

@@
 ```
-According to Ontario restaurant data from Yelp (cite, KSondjaja source), approximately 6% of restaurants
+According to Ontario restaurant data from Yelp [@yelp_dataset], approximately 6% of restaurants
 offer dine in service, 32.5% offer takeout, and 61.5% offer both.
@@
       ))
+
+survey_1
 ```
@@
       ))
+
+survey_2
 ```
@@
                              replace = TRUE))
+
+survey_1
 ```
@@
                              replace = TRUE))
+
+survey_2
 ```
 
-Download link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058 ###
-GEO_CODE indicates public health regions, taken from Census 2016 links:
-https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0
 ```{r}
 ### Load census dataset by Health Regions ###
+### Download link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058 ###
 census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
 census_2016 <- janitor::clean_names(census_2016)
-
-### Select demographic data to include, relating to employment, income, immigration status, minority groups, commute, etc. ###
-# Many categories
-# demographic_info <- c(1, 6, 8:33, 60:67, 100:104, 661:663, 694:707, 724:726, 1135:1136, 1139, 1140:1150, 1157, 1158, 1170, 1188, 1198, 1216, 1287, 1289:1292, 1324:1337, 1683:1697, 1884:1929)
 
@@
 ### Get data from the randomly selected Health Regions ###
+# GEO_CODE indicates public health regions, taken from Census 2016 links:
+#https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0
 
@@
 ```
-https://www150.statcan.gc.ca/n1/pub/89-656-x/89-656-x2015001-eng.htm
-Indigenous groups are 4% of the population.
 
-https://www.statcan.gc.ca/eng/dai/btd/othervisuals/other010
-visible minorities are 25% of the population
+We established expected percentages for the treatment and control regions based on census data [@census_2016].
 
-https://www.ic.gc.ca/eic/site/061.nsf/eng/h_03115.html
-1.4% of business owners are indigenous, and 12.2% are visible minorities.
+15.6% of business owners are women in Canada [@ownershipdemos].
 
-Therefore, Indigenous people are 0.35 times as likely to own a business, and visible minorities are 0.49 as likely to own a business.
+Visible minorities are 25% of the population [@visibleminority].
+
+12.2% of business owners are visible minorities [@ownershipdemos].
+
+Therefore, visible minorities are 0.49 as likely to own a business.
+Therefore, we can estimate that 0.058 of restaurant owners are a visible minority in the treatment group, and 0.081 in the control group.
+
+Indigenous people have 3.7% service business ownership as opposed to 15.3% in the reference population [@businessesper]. They are 0.24 times as likely to own a service business in Ontario.
+Therefore, we can estimate that 0.009 of business owners in the treatment group are Indigenous, and 0.011 in the control group.
 
@@
 survey_1 <- survey_1 %>%
-  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD MINORITY DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+  mutate(woman = sample(c("yes","no","nonanswer"), size = num_total, prob = c(0.154, 0.836, 0.01), replace = TRUE))
+
+set.seed(19893)
+survey_1 <- bind_rows(
+  survey_1 %>%
+    filter(group == "treatment") %>%
+    mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_treat, prob = c(0.009, 0.981, 0.01), replace = TRUE))
+  ,
+  survey_1 %>%
+    filter(group == "control") %>%
+   mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_control, prob = c(0.011, 0.979, 0.01), replace = TRUE))
+)
+
+set.seed(19893)
+survey_1 <- bind_rows(
+  survey_1 %>%
+    filter(group == "treatment", indigenous != "yes") %>%
+    mutate(visible = sample(c("yes", "no", "nonanswer"), 
+                               size = first(count(survey_1 %>% filter(group == "treatment", indigenous != "yes"))), 
+                               prob = c(0.057, 0.933, 0.01), replace = TRUE))
+  ,
+  survey_1 %>%
+    filter(group == "control", indigenous != "yes") %>%
+   mutate(visible = sample(c("yes", "no", "nonanswer"), 
+                              size = first(count(survey_1 %>% filter(group == "control", indigenous != "yes"))), 
+                              prob = c(0.08, 0.91, 0.01), replace = TRUE))
+  ,
+  survey_1 %>%
+    filter(indigenous == "yes") %>%
+    mutate(visible = "no")
+)
+
+survey_1
 ```
@@
 survey_2 <- survey_2 %>%
-  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD MINORITY DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+  mutate(woman = sample(c("yes","no","nonanswer"), size = num_total, prob = c(0.154, 0.836, 0.01), replace = TRUE))
+
+set.seed(19893)
+survey_2 <- bind_rows(
+  survey_2 %>%
+    filter(group == "treatment") %>%
+    mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_treat, prob = c(0.009, 0.981, 0.01), replace = TRUE))
+  ,
+  survey_2 %>%
+    filter(group == "control") %>%
+   mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_control, prob = c(0.011, 0.979, 0.01), replace = TRUE))
+)
+
+set.seed(19893)
+survey_2 <- bind_rows(
+  survey_2 %>%
+    filter(group == "treatment", indigenous != "yes") %>%
+    mutate(visible = sample(c("yes", "no", "nonanswer"), 
+                               size = first(count(survey_2 %>% filter(group == "treatment", indigenous != "yes"))), 
+                               prob = c(0.057, 0.933, 0.01), replace = TRUE))
+  ,
+  survey_2 %>%
+    filter(group == "control", indigenous != "yes") %>%
+   mutate(visible = sample(c("yes", "no", "nonanswer"), 
+                              size = first(count(survey_2 %>% filter(group == "control", indigenous != "yes"))), 
+                              prob = c(0.08, 0.91, 0.01), replace = TRUE))
+  ,
+  survey_1 %>%
+    filter(indigenous == "yes") %>%
+    mutate(visible = "no")
+)
+
+survey_2
 ```
@@
 
+survey_2
 ```
@@
 The distribution rf(n, df1, df2, ncp) = rf(num_rest, 10, 5) gives an approximate shape.
-Using the f-distribution formula, we know the distribution has a mean of 5/3, so we would multiply by 41,975 to get the mean to 69,959.
+Using the f-distribution formula, we know the distribution has a mean of 10/9, so we would multiply by 62,963 to get the mean to 69,959.
 
 ```{r}
-set.seed(19893)
+set.seed(19894)
 survey_1 <- survey_1 %>%
-  mutate(revenue = 41975 * rf(num_total,10,5))
+  mutate(revenue = 62963 * rf(num_total,20,20))
+
+survey_1
 ```
@@
 
-There seems to be no significant difference in business losses for disabled owners [@aug20192020].
+There seems to be no significant difference in business losses for disabled owners or female business owners [@aug20192020].
 
 ```{r}
-set.seed(19893)
+set.seed(19894)
 survey_2 <- survey_2 %>%
-  mutate(revenue = 41975 * rf(num_total,10,5)) %>%
+  mutate(revenue = 62963 * rf(num_total,20,20)) %>%
   mutate(factor = abs(rnorm(num_total, 1, .1))) %>%
@@
 
-<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<CHECK IF THIS WORKS ONCE MINORITY DATA IS ADDED AMY>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
 survey_2 <-
@@
     survey_2 %>%
-      filter((minority == "yes" | indigenous == "yes") & group == "treatment") %>%
+      filter((visible == "yes" | indigenous == "yes") & group == "treatment") %>%
       mutate(revenue = 0.88 * revenue)
@@
     survey_2 %>%
-      filter(minority == "no" & group == "treatment")
+      filter(visible == "no" & group == "treatment")
     ,
@@
 # Number of employees
-LALA
+
+$82,000 in yearly sales (gross revenue) per full-time equivalent employee [@restfact]
+
+Therefore 6,833 monthly revenue per full-time equivalent employee.
+
+In January 2021, there were 2187300 full time sales and service employees in Canada and 1164000 part time sales and service employees [@hourswages].
+Therefore there are 1.9 full time employees per part time employee.
+Part time employees in service and sales averaged 16.6 hours per week. We will assume that 2 PTE = 1 FTE, or 1 PTE = 0.5 FTE.
+Therefore, for every 1.9 + 1 employees, there are 1.9 + 1*0.5 FTE. For every 2.9 employees, there are 2.4 FTE.
+
+2.4 FTE -> 1.9 FT + 1 PT.
+0.79 = 1.9 / 2.4 = 1.9 / (1.9 + 0.5)
+0.42 = 1 / 2.4 = 0.42 = 1 / (1.9 + 0.5)
+
 ## Survey 1
 ```{r}
+set.seed(19893)
 survey_1 <- survey_1 %>%
-  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD EMPLOYMENT DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+  mutate(fte = revenue / 6833) %>%
+  mutate(ft = round(fte * 0.79)) %>%
+  mutate(pt = round(fte * 0.42)) %>%
+  select(-fte)
+
+survey_1 <- bind_rows(
+  survey_1 %>% filter(ft < 1) %>%
+    mutate(ft = 1),
+  survey_1 %>% filter(ft >= 1)
+)
+
+survey_1
 ```
@@
 ## Survey 2
+
+For the second survey, we will assume that treatment restaurants shifted towards part time random amounts-- that is, the number of full time employees per part time employee dropped from 1.9.
+X is some number less than or equal to 1.9.
+x / (x + 0.5)
+1 / (x + 0.5)
+
 ```{r}
+set.seed(19893)
 survey_2 <- survey_2 %>%
-  <<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<<ADD EMPLOYMENT DATA SIMULATION HERE LALA>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+  mutate(fte = revenue / 6833) %>%
+  mutate(ptincrease = 1.9 * (1 - abs(rnorm(num_total, 0, sd = 0.1)))) %>%
+  mutate(ft = round(fte * (ptincrease / (ptincrease + 0.5)))) %>%
+  mutate(pt = round(fte * (1 / (ptincrease + 0.5)))) %>%
+  select(-fte, - ptincrease)
+
+survey_2 <- bind_rows(
+  survey_2 %>% filter(ft < 1) %>%
+    mutate(ft = 1),
+  survey_2 %>% filter(ft >= 1)
+)
+
+survey_2
 ```
@@
 ```{r}
-num_cols_1 = number of columns in the tibble <<<<<<<<<<<<<<<<<<<<<<<SET AMY>>>>>>>>>>>>>>>>>>>>
+num_cols_1 = 11
 
@@
 
+survey_1
 ```
@@
 ```{r}
-num_cols_2 = number of columns in the tibble <<<<<<<<<<<<<<<<<<<<<<<SET AMY>>>>>>>>>>>>>>>>>>>>
+num_cols_2 = 12
 
@@
   select(-nonresponse, -which_partial)
+
+survey_2
+```
+
+```{r}
+write_csv(survey_1, here("outputs/data/survey_1.csv"))
+write_csv(survey_2, here("outputs/data/survey_2.csv"))
 ```

### 2021-02-18 scripts/03_clean_restaurant_list_csvs.R

@@ -135,6 +135,12 @@ write_csv(haliburton_data, here("outputs/data/haliburton_data.csv"))
 
 all_units_data <- unique(rbind(algoma_data, brant_data, durham_data, hamilton_data, haliburton_data, northwestern_data, simcoe_data, southwestern_data, sudbury_data, timiskaming_data, windsor_data, waterloo_data))
 
+
+all_units_data <- all_units_data %>%
+  mutate(address = str_replace(address, "(?: Canada)$", "")) %>%
+  mutate(address = str_replace(address, "(?: ON)$", "")) %>%
+  mutate(address = str_replace(address, "(?: Ontario)$", ""))
+  
 # Save
 
 write_csv(all_units_data, here("outputs/data/all_units_data.csv"))

### 2021-02-18 outputs/paper/paper.Rmd

@@
 library(kableExtra)  # for nicer tables
+library(here) # for working in an RProject
 
@@
 
-```{r}
-survey_1_data <- read_csv(here::here("outputs/survey__data.csv"))
-survey_1_data
-```
-
 Survey 1 was conducted June 3rd to 27th 2021, and it asked about May 2021.
@@
 Distributions for revenue and tables for key demographics were compared.
-
-```{r}
-survey_2_data <- read_csv(here::here("outputs/survey_2_data.csv"))
-survey_2_data
-```
 
@@
 
+```{r}
+survey_1 <- read_csv(here("outputs/data/survey_1.csv"))
+survey_2 <- read_csv(here("outputs/data/survey_2.csv"))
+```
+
+## Survey 1 results
+```{r}
+treat1 <- subset(survey_1, group == "treatment")
+control1 <- subset(survey_1, group == "control")
+t.test(treat1$revenue, control1$revenue)
+```
+
+```{r}
+survey_1 %>%
+  group_by(group) %>%
+  summarise(mean_revenue = mean(revenue, na.rm = TRUE),
+            median_revenue = median(revenue, na.rm = TRUE),
+            n = n())
+```
+
+```{r}
+survey_1 %>%
+  ggplot(aes(x = revenue)) +
+  geom_histogram() +
+  facet_wrap(~group)
+```
 Survey 1 data as baseline
 
-Counterfactuals
+Counterfactuals established.
+
+## Survey 2 results
 
 Survey 2 data to contrast treatment and control.
+
+```{r}
+survey_2 %>%
+  group_by(group) %>%
+  summarise(mean_revenue = mean(revenue, na.rm = TRUE),
+            median_revenue = median(revenue, na.rm = TRUE),
+            n = n())
+```
+
+```{r}
+treat2 <- subset(survey_2, group == "treatment")
+control2 <- subset(survey_2, group == "control")
+t.test(treat2$revenue, control2$revenue)
+```
+
+```{r}
+survey_2 %>%
+  ggplot(aes(x = revenue)) +
+  geom_histogram() +
+  facet_wrap(~group)
+```
 
@@
 
-Suggestions: technical support for restaurants to increase takeout business
+Suggestion: technical support for restaurants to increase takeout business
 
@@
 
-Suggestions: grants for minority business owners
+Suggestion: grants for minority business owners
 
@@
 
-External validity, internal validity, cluster sampling. Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them.
+External validity, internal validity, cluster sampling.
+Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them.
+It was ethically unsound to run the experiment on the entire province, so sampling was necessary.
 

### 2021-02-19 outputs/paper/data_simulation.Rmd

@@
 
-```{r surveyframe}
+```{r, warning = FALSE}
 # read in the data
@@
 
-# Survey questions that require simulated data
-
 # Type of service provided
 
-```{r}
+```{r, warning = FALSE}
 # Read in data
@@
 ```
-```{r}
+```{r, warning = FALSE}
 takeout_percentage <- takeout %>%
@@
 ```
-```{r}
+```{r, warning = FALSE}
 # Check proportion of RestaurantsTableService
@@
 ```
-```{r}
+```{r, warning = FALSE}
 tableserv_percentage <- tableserv %>%
@@
 
-```{r}
+```{r, warning = FALSE}
 # Calculate invalid responses (neither dine-in nor takeout)
@@
 ## Survey 1
-```{r}
+```{r, warning = FALSE}
 set.seed(19)
@@
 ## Survey 2
-```{r}
+```{r, warning = FALSE}
 set.seed(19)
@@
 ## Survey 1
-```{r}
+```{r, warning = FALSE}
 set.seed(19893)
@@
 ## Survey 2
-```{r}
+```{r, warning = FALSE}
 set.seed(19893)
@@
 
-```{r}
+```{r, warning = FALSE}
 ### Load census dataset by Health Regions ###
@@
 
-```{r}
+```{r, warning = FALSE}
 populations_split <- matrix(ncol=4, nrow=5)
@@
 
-```{r}
+```{r, warning = FALSE}
 ### Get percentage proportions of demographic groups of interest ###
@@
 
-```{r}
+```{r, warning = FALSE}
 set.seed(19893)
@@
 
-```{r}
+```{r, warning = FALSE}
 set.seed(19894)
@@
 
-```{r}
+```{r, warning = FALSE}
 num_cols_1 = 11
@@
 
-```{r}
+```{r, warning = FALSE}
 num_cols_2 = 12
@@
 
-```{r}
+```{r, warning = FALSE}
 write_csv(survey_1, here("outputs/data/survey_1.csv"))

### 2021-02-19 outputs/paper/paper.Rmd

--- 2021-02-18 outputs/paper/paper.Rmd
@@
 
-From each strata, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control. This was the sample at the cluster level.
+From each strata, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control.
+This was the sample at the cluster level.
+This sample is shown in Table \@ref(table:treatmentcontrolgroups).
 
@@
 
-The stratification was used because there were very differently sized LHAs, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of unequivalent treatment and control groups.
+The stratification was used because there were very differently sized LHAs, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of nonequivalent treatment and control groups.
 
-```{r treatmentcontrolgroups}
+```{r treatmentcontrolgroups, echo = FALSE, message = FALSE, warning = FALSE}
 treatment_control_groups <- read_csv(here::here("outputs/treatment_control_groups.csv"))
-treatment_control_groups
+treatment_control_groups %>%
+  knitr::kable() %>%
+  kableExtra::kable_styling()
 ```
@@
 Once collected into one dataframe, this was the frame at the unit level.
+A sample of this frame is shown in Table \@ref(table:sampleallunitsdata).
 
-```{r}
+```{r sampleallunitsdata, echo = FALSE, message = FALSE, warning = FALSE}
 all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv"))
-all_units_data
+all_units_data %>%
+  slice(1:10) %>%
+  knitr::kable() %>%
+  kableExtra::kable_styling()
 ```
@@
 
-```{r}
+```{r, include = FALSE}
 table_for_surveys <- read_csv(here::here("outputs/table_for_surveys.csv"))
-table_for_surveys
 ```
@@
 
-```{r}
-survey_1_data <- read_csv(here::here("outputs/survey__data.csv"))
-survey_1_data
-```
-
-Survey 1 was conducted June 3rd to 27th 2021, and it asked about May 2021.
+Survey 1 was conducted June 3rd to 27th 2021, and it asked about the month of May 2021.
 
@@
 
-Distributions for revenue and tables for key demographics were compared.
-
-```{r}
-survey_2_data <- read_csv(here::here("outputs/survey_2_data.csv"))
-survey_2_data
-```
-
 After Survey 1 data was collected, on June 28th, shutdowns were announced for the six treatment LHAs.
@@
 
-Survey 2 was conducted August 3rd to 27th 2021, and it asked about July 2021.
+Survey 2 was conducted August 3rd to 27th 2021, and it asked about the month of July 2021.
 
@@
 * Demographic information
-- Disability status
-- Indigenous status
-- Visible minority (non-Indigenous) status
+- Disability status: According to the UN Convention on the Rights of Persons with Disabilities, persons with disabilities are described as having "long-term physical, mental, intellectual or sensory impairments which in interaction with various barriers may hinder their full and effective participation in society on an equal basis with others."
+- Indigenous status: According to the Government of Canada, Indigenous people include "First Nations (North American Indian), Métis or Inuit and/or those who reported Registered or Treaty Indian status, that is registered under the Indian Act of Canada, and/or those who reported membership in a First Nation or Indian band".
+- Visible minority (non-Indigenous) status: "Visible minority" is defined by the Government of Canada as "persons, other than aboriginal peoples, who are non-Caucasian in race or non-white in colour."
 - Gender identity
@@
 
+```{r, include = FALSE}
+survey_1 <- read_csv(here("outputs/data/survey_1.csv"))
+survey_2 <- read_csv(here("outputs/data/survey_2.csv"))
+```
+
+## Survey 1 results
+
 Survey 1 data as baseline
 
-Counterfactuals
+Counterfactuals established.
+
+## Survey 2 results
 

### 2021-02-19 outputs/paper/data_simulation.Rmd
graphs, tables, and cross-referencing

@@
 survey_1 <- survey_1 %>%
-  mutate(disability = sample(c("yes", "no"),
+  mutate(disability = sample(c("yes", "no", "nonanswer"),
                              size = num_total,
-                             prob = c(0.005, .995),
+                             prob = c(0.005, .985, 0.01),
                              replace = TRUE))
@@
 survey_2 <- survey_2 %>%
-  mutate(disability = sample(c("yes", "no"),
+  mutate(disability = sample(c("yes", "no", "nonanswer"),
                              size = num_total,
-                             prob = c(0.005, .995),
+                             prob = c(0.005, .985, 0.01),
                              replace = TRUE))
@@
 
-set.seed(19893)
+set.seed(19894)
 survey_1 <- survey_1 %>%
@@
 
-set.seed(19894)
+set.seed(19895)
 survey_2 <- survey_2 %>%

### 2021-02-19 scripts/extra_graphs_tables_for_paper.Rmd
graphs, tables, and cross-referencing

---
title: "R Notebook"
output: html_notebook
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(bookdown)
library(kableExtra)
library(here)

#REPLACE LINE 81 WITH:
```
This survey cost $5,606. A detailed breakdown of costs can be found on [Appendix X](#appendixX).
```{r}
#INCLUDE IN APPENDIX [REPLACE X WITH CORRECT NUMBER, AFTER SURVEY APPENDIX]
```
# Appendix X {#appendixX}
```{r echo=FALSE, message=FALSE, warning=FALSE}
restaurants = 2006
survey_total = 2
indiv_postage = 0.85 # https://www.canadapost.ca/cpc/en/business/postal-services/mailing/letter-discounts.page?
minimum_wage = 14.25 # https://www.ontario.ca/document/your-guide-employment-standards-act-0/minimum-wage
management_service = 195 # https://www.alchemer.com/plans-pricing/small-teams/
average_call_mins = 7
response_rate = .3

phone_interviewer_cost = round(restaurants*survey_total*response_rate, 2)*average_call_mins/60*minimum_wage

postage_cost = (restaurants*2)*indiv_postage

survey_budget <- data.frame(
  Item = c ("Data Management", "Phone Interviewer Wages", "Postage", "TOTAL"),
  Cost = c (management_service, phone_interviewer_cost, postage_cost, sum(management_service, phone_interviewer_cost, postage_cost)),
  Description = c ("Online survey management account fees",
                   "1,203 calls (7 minutes on average) at $14.25/hr",
                   "4,012 mailers at $0.85/ea",
                   "")
)

survey_budget %>% 
  kable(digits = 2,
        caption = "2021 Ontario Restaurant Survey Budget") %>% 
  kable_styling() %>% 
  row_spec(0, bold = T, color = "white", background = "grey") %>% 
  row_spec(4, bold = T)
```
```{r echo=FALSE, message=FALSE, warning=FALSE}
#GRAPHS SURVEY 1

survey_1 <- read_csv(here("outputs/data/survey_1.csv"))

ggplot(survey_1, aes(x = service_type, fill = group)) +                       
  geom_histogram(stat = "count", position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = disability, fill = group)) +                       
  geom_histogram(stat = "count", position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = woman, fill = group)) +                       
  geom_histogram(stat = "count", position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = visible, fill = group)) +                       
  geom_histogram(stat = "count", position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = revenue, fill = group)) +                       
  geom_histogram(position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = ft, fill = group)) +                       
  geom_histogram(position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = pt, fill = group)) +                       
  geom_histogram(position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

survey_1 %>%
  group_by(group, service_type) %>%
  summarise(count_service_type = n(),
  ) %>%
  mutate(perc_service_type = count_service_type / sum(count_service_type)) %>%
  ggplot(aes(x = service_type, y = perc_service_type, fill = group)) +                       
  geom_bar(stat = "identity", position = "dodge", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = service_type, fill = group)) +                       
  geom_histogram(stat = "count", position = "dodge", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = disability, fill = group)) +                       
  geom_histogram(stat = "count", position = "dodge", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = woman, fill = group)) +                       
  geom_histogram(stat = "count", position = "dodge", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_1, aes(x = visible, fill = group)) +                       
  geom_histogram(stat = "count", position = "dodge", alpha = 0.5, bins = 50) +
  theme_minimal()

```
```{r echo=FALSE, message=FALSE, warning=FALSE}
#GRAPHS SURVEY 2
survey_2 <- read_csv(here("outputs/data/survey_2.csv"))

ggplot(survey_2, aes(x = service_type, fill = group)) +                       
  geom_histogram(stat = "count", position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_2, aes(x = disability, fill = group)) +                       
  geom_histogram(stat = "count", position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_2, aes(x = woman, fill = group)) +                       
  geom_histogram(stat = "count", position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_2, aes(x = visible, fill = group)) +                       
  geom_histogram(stat = "count", position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_2, aes(x = revenue, fill = group)) +                       
  geom_histogram(position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_2, aes(x = ft, fill = group)) +                       
  geom_histogram(position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()

ggplot(survey_2, aes(x = pt, fill = group)) +                       
  geom_histogram(position = "identity", alpha = 0.5, bins = 50) +
  theme_minimal()
```

```{r typeimpactcontrol, echo = FALSE, message = FALSE, warning = FALSE}
survey_2 %>% 
  filter(group == "control") %>%
  summary_factorlist("service_type", c("revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N = ",
                     total_col = FALSE) %>%
  mutate(service_type = c("", "Revenue", "Number of full-time employees", "Number of part time employees")) %>%
  knitr::kable(caption = "Metrics of control group restaurants based on service type",
               booktabs = TRUE,
               col.names = c("Service Type", "", "Dine-in Only", "Takeout Only", "Both")) %>%
  kableExtra::kable_styling()
```

```{r typeimpacttreat, echo = FALSE, message = FALSE, warning = FALSE}
survey_2 %>% 
  filter(group == "treatment") %>%
  summary_factorlist("service_type", c("revenue", "ft", "pt"),
                     p = FALSE, 
                     add_dependent_label = TRUE, 
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     col_totals_prefix = "N = ",
                     total_col = FALSE) %>%
  mutate(service_type = c("", "Revenue", "Number of full-time employees", "Number of part time employees")) %>%
  knitr::kable(caption = "Different impact on treatment restaurants based on service type",
               booktabs = TRUE,
               col.names = c("Service Type", "", "Dine-in Only", "Takeout Only", "Both")) %>%
  kableExtra::kable_styling()
```

### 2021-02-19 outputs/paper/paper.Rmd

@@
 library(here) # for working in an RProject
+library(finalfit) # for a summary table
+library(gridExtra)  # for paired graphs
 
@@
 This was the sample at the cluster level.
-This sample is shown in Table \@ref(table:treatmentcontrolgroups).
+This sample is shown in Table \@ref(tab:treatmentcontrolgroups).
 
@@
 
+```{r, include = FALSE}
+treatment_control_groups <- read_csv(here::here("outputs/treatment_control_groups.csv"))
+```
+
 ```{r treatmentcontrolgroups, echo = FALSE, message = FALSE, warning = FALSE}
-treatment_control_groups <- read_csv(here::here("outputs/treatment_control_groups.csv"))
 treatment_control_groups %>%
-  knitr::kable() %>%
+  knitr::kable(caption = "Cluster sample randomly selecting Local Health Authorities from strata based on population size",
+               booktabs = TRUE) %>%
   kableExtra::kable_styling()
@@
 Once collected into one dataframe, this was the frame at the unit level.
-A sample of this frame is shown in Table \@ref(table:sampleallunitsdata).
+A sample of this frame is shown in Table \@ref(tab:sampleallunitsdata).
+
+```{r, include = FALSE}
+all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv")) 
+```
 
 ```{r sampleallunitsdata, echo = FALSE, message = FALSE, warning = FALSE}
-all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv"))
 all_units_data %>%
   slice(1:10) %>%
-  knitr::kable() %>%
-  kableExtra::kable_styling()
+  knitr::kable(caption = "Example segment of the unit level sampling frame",
+               booktabs = TRUE) %>%
+  column_spec(1, width = "14em") %>%
+  column_spec(2, width = "14em") %>%
+  column_spec(3, width = "6em") %>%
+  column_spec(4, width = "6em") %>%
+  kableExtra::kable_styling(latex_options = c("scale_down"))
 ```
@@
 
-This survey cost <<<<<<<<LORENA>>>>>>>>>>>>>.
+This survey cost $5,606. A detailed breakdown of costs can be found on [Appendix A](#appendixA).
 
@@
 * Demographic information
-- Disability status: According to the UN Convention on the Rights of Persons with Disabilities, persons with disabilities are described as having "long-term physical, mental, intellectual or sensory impairments which in interaction with various barriers may hinder their full and effective participation in society on an equal basis with others."
-- Indigenous status: According to the Government of Canada, Indigenous people include "First Nations (North American Indian), Métis or Inuit and/or those who reported Registered or Treaty Indian status, that is registered under the Indian Act of Canada, and/or those who reported membership in a First Nation or Indian band".
-- Visible minority (non-Indigenous) status: "Visible minority" is defined by the Government of Canada as "persons, other than aboriginal peoples, who are non-Caucasian in race or non-white in colour."
+- Disability status
+- Indigenous status
+- Visible minority (non-Indigenous) status
 - Gender identity
@@
 ```{r, include = FALSE}
-survey_1 <- read_csv(here("outputs/data/survey_1.csv"))
-survey_2 <- read_csv(here("outputs/data/survey_2.csv"))
+survey_1 <- read_csv(here("outputs/data/survey_1.csv")) %>%
+    mutate(group = fct_relevel(group, "treatment", "control"),
+           service_type = fct_relevel(service_type, "dinein", "takeout", "both"),
+           disability = fct_relevel(disability, "yes", "no", "nonanswer"),
+           woman = fct_relevel(woman, "yes", "no", "nonanswer"),
+           indigenous = fct_relevel(indigenous, "yes", "no", "nonanswer"),
+           visible = fct_relevel(visible, "yes", "no", "nonanswer"))
+
+survey_2 <- read_csv(here("outputs/data/survey_2.csv")) %>%
+    mutate(group = fct_relevel(group, "treatment", "control"),
+           service_type = fct_relevel(service_type, "dinein", "takeout", "both"),
+           disability = fct_relevel(disability, "yes", "no", "nonanswer"),
+           woman = fct_relevel(woman, "yes", "no", "nonanswer"),
+           indigenous = fct_relevel(indigenous, "yes", "no", "nonanswer"),
+           visible = fct_relevel(visible, "yes", "no", "nonanswer"))
 ```
@@
 
-Survey 1 data as baseline
+Survey 1 data as baseline  Table \@ref(tab:survey1summary) Figure \@ref(fig:baselinerevenue) Figure \@ref(fig:baselineemployees)
 
@@
 
+```{r survey1summary, echo = FALSE, message = FALSE, warning = FALSE}
+survey_1 %>% 
+  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "revenue", "ft", "pt"),
+                     p = FALSE, 
+                     add_dependent_label = TRUE, 
+                     dependent_label_prefix = "",
+                     add_col_totals = TRUE,
+                     include_row_missing_col = FALSE,
+                     col_totals_rowname = "",
+                     col_totals_prefix = "N = ",
+                     total_col = FALSE) %>%
+  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
+  knitr::kable(caption = "Summary statistics for treatment and control baselines",
+               booktabs = TRUE,
+               col.names = c("", "", "Treatment", "Control")) %>%
+  kableExtra::kable_styling()
+```
+
+```{r baselinerevenue, fig.cap="Revenue distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+ggplot(survey_1, aes(x = revenue / 1000, fill = group)) +                       
+  geom_histogram(position = "dodge", binwidth = 5) +
+  theme_minimal() +
+  scale_x_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300)) +
+  labs(fill = NULL,
+       x = "Revenue in May 2021 (in thousands of Canadian dollars)",
+       y = "Number of restaurants")
+```
+
+```{r baselineemployees, fig.cap="Employment distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=6, echo = FALSE, message = FALSE, warning = FALSE}
+p1 <- ggplot(survey_1, aes(x = pt, fill = group)) +                       
+  geom_histogram(position = "dodge", binwidth = 1, show.legend = FALSE) +
+  coord_flip() +
+  xlim(0,35) +
+  scale_y_continuous(limits = c(0,150), breaks = c(0,25,50,75,100,125,150)) +
+  theme_minimal() +
+  labs(x = "Number of employees in a restaurant",
+       y = "Number of restaurants",
+       title = "Part-time employees")
+
+p2 <- ggplot(survey_1, aes(x = ft, fill = group)) +                       
+  geom_histogram(position = "dodge", binwidth = 1) +
+  coord_flip() +
+  xlim(0,35) +
+  scale_y_continuous(limits = c(0,100), breaks = c(0,25,50,75,100)) +
+  theme_minimal() +
+  labs(fill = NULL,
+       x = NULL,
+       y = "Number of restaurants",
+       title = "Full-time employees")
+
+grid.arrange(p1, p2, ncol = 2)
+```
+
 ## Survey 2 results
 
-Survey 2 data to contrast treatment and control.
+Survey 2 data to contrast treatment and control. Table \@ref(tab:survey2summary)
+
+```{r survey2summary, echo = FALSE, message = FALSE, warning = FALSE}
+survey_2 %>% 
+  summary_factorlist("group", c("service_type", "disability", "woman", "indigenous", "visible", "shutdown", "revenue", "ft", "pt"),
+                     p = FALSE, 
+                     add_dependent_label = TRUE, 
+                     dependent_label_prefix = "",
+                     add_col_totals = TRUE,
+                     include_row_missing_col = FALSE,
+                     col_totals_rowname = "",
+                     col_totals_prefix = "N = ",
+                     total_col = FALSE) %>%
+  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
+  knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
+               booktabs = TRUE,
+               col.names = c("", "", "Treatment", "Control")) %>%
+   kableExtra::kable_styling()
+```
 
@@
 ### FINDING ONE
-Closures had a negative impact on revenues and employment counts
+Closures had a negative impact on revenues and employment counts Figure \@ref(fig:postrevenue) Figure \@ref(fig:postemployees)
+
+```{r postrevenue, fig.cap="Revenue distribution for treatment and control groups, from Survey 2", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+ggplot(survey_2, aes(x = revenue / 1000, fill = group)) +                       
+  geom_histogram(position = "dodge", binwidth = 5) +
+  theme_minimal() +
+  scale_x_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300)) +
+  labs(fill = NULL,
+       x = "Revenue in July 2021 (in thousands of Canadian dollars)",
+       y = "Number of restaurants")
+```
+
+```{r postemployees, fig.cap="Employment distribution for treatment and control groups, from Survey 2", fig.width=10, fig.height=6, echo = FALSE, message = FALSE, warning = FALSE}
+p1 <- ggplot(survey_2, aes(x = pt, fill = group)) +                       
+  geom_histogram(position = "dodge", binwidth = 1, show.legend = FALSE) +
+  coord_flip() +
+  xlim(0,35) +
+  scale_y_continuous(limits = c(0,150), breaks = c(0,25,50,75,100,125,150)) +
+  theme_minimal() +
+  labs(x = "Number of employees in a restaurant",
+       y = "Number of restaurants",
+       title = "Part-time employees")
+
+p2 <- ggplot(survey_2, aes(x = ft, fill = group)) +                       
+  geom_histogram(position = "dodge", binwidth = 1) +
+  coord_flip() +
+  xlim(0,35) +
+  scale_y_continuous(limits = c(0,100), breaks = c(0,25,50,75,100)) +
+  theme_minimal() +
+  labs(fill = NULL,
+       x = NULL,
+       y = "Number of restaurants",
+       title = "Full-time employees")
+
+grid.arrange(p1, p2, ncol = 2)
+```
 
@@
 ### FINDING TWO
-Closures had a stronger negative impact on dine-in only restaurants
+
+Closures had a stronger negative impact on dine-in only restaurants Figure \@ref(fig:servicetypeimpact)
+
+```{r servicetypeimpact, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+survey_2 %>%
+  filter(service_type != "NA") %>%
+  ggplot(aes(x = service_type, y = revenue / 1000, fill = group)) +
+  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
+  labs(fill = NULL,
+       x = "Service type provided",
+       y = "Mean revenue (in thousands of Canadian dollars") +
+  scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
+  theme_minimal()
+```
 
@@
 ### FINDING THREE
-Closures had a stronger negative impact on indigenous or visible minority-owned businesses.
+Closures had a stronger negative impact on indigenous or visible minority-owned businesses. Figure \@ref(fig:minorityimpact)
+
+```{r minorityimpact, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+bind_rows(
+  survey_2 %>%
+    filter(indigenous == "yes" | visible == "yes") %>%
+     mutate(minority = "Visible minority / Indigenous")
+  ,
+  survey_2 %>%
+   filter(indigenous == "no" & visible == "no") %>%
+    mutate(minority = "No")
+) %>% 
+  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
+  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
+  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
+  labs(fill = NULL,
+       x = "Racial and ethic minorities",
+       y = "Mean revenue (in thousands of Canadian dollars") +
+  theme_minimal()
+```
 
@@
 
+# Appendix A
+
+```{r echo=FALSE, message=FALSE, warning=FALSE}
+restaurants = 2006
+survey_total = 2
+indiv_postage = 0.85 # https://www.canadapost.ca/cpc/en/business/postal-services/mailing/letter-discounts.page?
+minimum_wage = 14.25 # https://www.ontario.ca/document/your-guide-employment-standards-act-0/minimum-wage
+management_service = 195 # https://www.alchemer.com/plans-pricing/small-teams/
+average_call_mins = 7
+response_rate = .3
+
+phone_interviewer_cost = round(restaurants*survey_total*response_rate, 2)*average_call_mins/60*minimum_wage
+
+postage_cost = (restaurants*2)*indiv_postage
+
+survey_budget <- data.frame(
+  Item = c ("Data Management", "Phone Interviewer Wages", "Postage", "TOTAL"),
+  Cost = c (management_service, phone_interviewer_cost, postage_cost, sum(management_service, phone_interviewer_cost, postage_cost)),
+  Description = c ("Online survey management account fees",
+                   "1,203 calls (7 minutes on average) at $14.25/hr",
+                   "4,012 mailers at $0.85/ea",
+                   "")
+)
+
+survey_budget %>% 
+  kable(digits = 2,
+        caption = "2021 Ontario Restaurant Survey Budget") %>% 
+  kable_styling() %>% 
+  row_spec(0, bold = T, color = "white", background = "gray") %>% 
+  row_spec(4, bold = T) %>%
+  kableExtra::kable_styling(latex_options = c("hold_position"))
+```
+
+# Appendix B
+
+TODO: add survey screenshot
+
+# Appendix C
+
+TODO: add complete list of survey questions
+
 \newpage

### 2021-02-19 outputs/paper/data_simulation.Rmd
fix nonresponse. add notes for content to write. polish tables.

@@
 survey_2
+
 ```
@@
 
-set.seed(19894)
+set.seed(891)
 survey_1 <- survey_1 %>%
   mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
-  filter(nonresponse != "no")
+  filter(nonresponse != "yes")
 
-set.seed(19894)
+set.seed(891)
 survey_1 <- survey_1 %>%
@@
 
-set.seed(19895)
+set.seed(198)
 survey_2 <- survey_2 %>%
   mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
-  filter(nonresponse != "no")
+  filter(nonresponse != "yes")
 
-set.seed(19895)
+set.seed(198)
 survey_2 <- survey_2 %>%

### 2021-02-19 outputs/paper/paper.Rmd

@@
 subtitle: "SUBTITLE"
-abstract: "ABSTRACT"
+abstract: "Four sentences. 1) what was done, 2) what was found, and 3) why this matters (all at a high level). Top level finding"
 thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
@@
 
+<<<<tells a reader everything they need to know, including putting it into a broader context.>>>>
+
+The experiment was comissioned by ___.
+
+<<<<<<you’re interested in, what you did, what you found, why it’s important, etc.>>>>>>>>
+
+<<<Outline paper structure>>>
+
 # Data
@@
 #TODO: citations for R and all packages used.
+
+## Methodology
 
@@
 The stratification was used because there were very differently sized LHAs, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of nonequivalent treatment and control groups.
+Given the limitations of cluster sampling, stratifying the clusters by size helped ensure the experiment would be representative of Ontario.
+<stuff about the statistical properties of cluster and stratified sampling somewhere in here, cite textbook reading>.
 
@@
 
+The demographic information was collected so that disparate impacts on different communities could be identified.
+Revenue and number of employees were collected as measures of the restaurant's performance and impact on the local employment levels.
+These were the primary indicators of interest, due to the <GOVERNMENT ORGANIZATION>>>>> focus on economic stability and employment levels.
+
 After Survey 1 data was collected, on June 28th, shutdowns were announced for the six treatment LHAs.
@@
 This type of partial shutdown was selected because it has been the most common type of shutdown since the pandemic began.
+
+<Something about enforcement of closures-- how have fines worked during covid closures?)
+
+Because it is very difficult for a restaurant to move location in under two weeks, the control and treatment groups were effectively separated.
 
@@
 - Number of part-time employees (less than 30 hours/week)
+
+<<<<<<<<<<<<survey strengths and weaknesses>>>>>>>>>>>>>
 
@@
 
+<<<<<Consider: do we need to plot more raw data?>>>>>>>>>>>
+
+It was necessary to collect data before the intervention to establish that the treatment and control groups were in fact comparable.
+
 Survey 1 data as baseline  Table \@ref(tab:survey1summary) Figure \@ref(fig:baselinerevenue) Figure \@ref(fig:baselineemployees)
@@
                col.names = c("", "", "Treatment", "Control")) %>%
-  kableExtra::kable_styling()
+  kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
 ```
@@
   theme_minimal() +
-  scale_x_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300)) +
+  scale_x_continuous(limits = c(0, 250), breaks = c(0, 50, 100, 150, 200, 250, 300)) +
   labs(fill = NULL,
@@
 
+<<<<<Consider: do we need to plot more raw data?>>>>>>>>>>>
+
 Survey 2 data to contrast treatment and control. Table \@ref(tab:survey2summary)
@@
                col.names = c("", "", "Treatment", "Control")) %>%
-   kableExtra::kable_styling()
+   kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
 ```
@@
 ## Overview
+
+<<< overview of the results>>>
+
+<<<how they fit in existing literature -- need some references here>>>>
 
@@
 
-```{r servicetypeimpact, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+```{r servicetypeimpact, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
 survey_2 %>%
@@
 
-```{r minorityimpact, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+```{r minorityimpact, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=5, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
 bind_rows(
@@
   labs(fill = NULL,
-       x = "Racial and ethic minorities",
+       x = "Racial and ethnic minorities",
        y = "Mean revenue (in thousands of Canadian dollars") +
@@
 Suggestion: grants for minority business owners
+
+## Ethics ? Or integrate in other sections.
 
@@
 
-Survey non-response.
+Survey non-response. Figure \@ref(fig:nonresponse)
+
+```{r nonresponse, fig.cap="More than half of surveyed restaurants did not respond", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+num_treat_sample <- as.numeric(count(table_for_surveys %>% filter(group == "treatment")))
+
+num_control_sample <- as.numeric(count(table_for_surveys %>% filter(group == "control")))
+
+num_treat_complete_survey1 <- sum(complete.cases(survey_1 %>% filter(group == "treatment")))
+
+num_control_complete_survey1 <- sum(complete.cases(survey_1 %>% filter(group == "control")))
+
+num_treat_partial_survey1 <- sum(!complete.cases(survey_1 %>% filter(group == "treatment")))
+
+num_control_partial_survey1 <- sum(!complete.cases(survey_1 %>% filter(group == "control")))
+
+num_treat_nonre_survey1 <- num_treat_sample - num_treat_complete_survey1 - num_treat_partial_survey1
+
+num_control_nonresurvey1 <- num_control_sample - num_control_complete_survey1 - num_control_partial_survey1
+
+num_treat_complete_survey2 <- sum(complete.cases(survey_2 %>% filter(group == "treatment")))
+
+num_control_complete_survey2 <- sum(complete.cases(survey_2 %>% filter(group == "control")))
+
+num_treat_partial_survey2 <- sum(!complete.cases(survey_2 %>% filter(group == "treatment")))
+
+num_control_partial_survey2 <- sum(!complete.cases(survey_2 %>% filter(group == "control")))
+
+num_treat_nonre_survey2 <- num_treat_sample - num_treat_complete_survey2 - num_treat_partial_survey2
+
+num_control_nonresurvey2 <- num_control_sample - num_control_complete_survey2 - num_control_partial_survey2
+
+tibble(Group = c("Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control"), 
+        Response = c("Complete", "Complete", "Partial", "Partial", "No response", "No response", "Complete", "Complete", "Partial", "Partial", "No response", "No response"), 
+        Survey = c("Survey 1", "Survey 1","Survey 1","Survey 1","Survey 1","Survey 1", "Survey 2", "Survey 2", "Survey 2", "Survey 2", "Survey 2", "Survey 2"), 
+        Count = c(num_treat_complete_survey1, num_control_complete_survey1, num_treat_partial_survey1, num_control_partial_survey1, num_treat_nonre_survey1, num_control_nonresurvey1,
+          num_treat_complete_survey2, num_control_complete_survey2, num_treat_partial_survey2, num_control_partial_survey2, num_treat_nonre_survey2, num_control_nonresurvey2)) %>%
+  ggplot(aes(x = Response, y = Count, fill = Group)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  facet_wrap(~Survey) +
+  theme_minimal()
+
+```
 

### 2021-02-20 outputs/paper/paper.Rmd
add lorena's text and update graphs

@@
 
-<<<<tells a reader everything they need to know, including putting it into a broader context.>>>>
-
-The experiment was comissioned by ___.
-
-<<<<<<you’re interested in, what you did, what you found, why it’s important, etc.>>>>>>>>
-
-<<<Outline paper structure>>>
+The COVID-19 pandemic has presented challenges that continue to test our resilience, creativity, and ability to recover.
+From online learning to curbside shopping, the changes are tangible on a local level.
+To better understand the impact of intermittent lockdowns on restaurant businesses specifically, and to provide the Ontario Ministry of Economic Development, Job Creation and Trade with evidence-based advice, Petit Poll conducted a comprehensive study of over 1,200 restaurants in 12 regions of Ontario.
+This report describes the experiment design and rationale, measurement strategies, data characteristics, main findings, recommendations, limitations, and broader implications.
+Importantly, the intervention revealed three key effects of closures: (1) closures had a negative impact on revenues and employment counts, (2) closures had a stronger negative impact on dine-in only restaurants, and (3) closures had a stronger negative impact on Indigenous or visible minority-owned businesses.
+These findings provide more detail to an already stark picture: while the health of Ontarians has to be prioritized, and the transmission of COVID-19 has to be aggressively contained, it is impossible to ignore the economic consequences of prolonged business closures.
+In particular, support for Indigenous and visible minority-owned businesses is imperative, as these populations continue to bear the brunt of systemic inequalities.
+Preparing and supporting dine-in establishments to transition to takeout only, and providing furloughed workers with vital financial support, must be equally prioritized.
 
@@
                booktabs = TRUE) %>%
-  kableExtra::kable_styling()
+  kableExtra::kable_styling() %>%
+  collapse_rows()
 ```
@@
 
-This survey cost $5,606. A detailed breakdown of costs can be found on [Appendix A](#appendixA).
+This survey cost $6711.18. A detailed breakdown of costs can be found on [Appendix A](#appendixA).
 
@@
            visible = fct_relevel(visible, "yes", "no", "nonanswer"))
+
+count(full_join(survey_1, survey_2, by = "ID"))
 ```
@@
 
-It was necessary to collect data before the intervention to establish that the treatment and control groups were in fact comparable.
+The initial survey provided an overview of the characteristics of the treatment and control groups.
+As indicated in Table \@ref(tab:survey1summary), the groups are equivalent, showing no notable differences across any of the variables studied.
+It was necessary to collect data before the intervention to ensure that the treatment and control groups were in fact comparable.
 
-Survey 1 data as baseline  Table \@ref(tab:survey1summary) Figure \@ref(fig:baselinerevenue) Figure \@ref(fig:baselineemployees)
+Survey 1 data was used to effectively establish a baseline for comparison.
+In addition to the use of random selection of participants and random assignment to either treatment or control, establishing a baseline allows for an accurate estimation of the counterfactual.
+The counterfactual – or the representation of what would have happened had the intervention not taken place – is essential to measuring, and reporting on, the effect of the mandated restaurant closures.
+
+Figure \@ref(fig:baselinerevenue) Figure \@ref(fig:baselineemployees)
 
@@
                      col_totals_rowname = "",
-                     col_totals_prefix = "N = ",
-                     total_col = FALSE) %>%
+                     total_col = FALSE,
+                     col_totals_prefix = "N (%) = ") %>%
   mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
   knitr::kable(caption = "Summary statistics for treatment and control baselines",
-               booktabs = TRUE,
+               booktabs = TRUE, linesep = "",
                col.names = c("", "", "Treatment", "Control")) %>%
@@
        x = "Revenue in May 2021 (in thousands of Canadian dollars)",
-       y = "Number of restaurants")
+       y = "Number of restaurants",
+       title = "Revenue distributions were similar in the treatment and control samples")
 ```
@@
 
-grid.arrange(p1, p2, ncol = 2)
+grid.arrange(p1, p2, ncol = 2, top = "Employment distributions were similar in the treatment and control samples")
 ```
@@
 
-Survey 2 data to contrast treatment and control. Table \@ref(tab:survey2summary)
+The second survey results showed marked differences between treatment and control groups in most areas.
+A summary of these results is found in Table \@ref(tab:survey2summary).
+Naturally, a salient difference is found in service type, with dine-in restaurants decreasing due to mandated shutdowns – the intervention itself – with 7% of restaurants in the control group providing dine-in service, and only 4% in the treatment group.
+Similarly, the mean revenue decreases noticeably for the treatment group (\$45,959.60) compared to the control group ($70675.60).
+The mean number of employees, both full-time and part-time, shows a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
 
@@
                      col_totals_rowname = "",
-                     col_totals_prefix = "N = ",
-                     total_col = FALSE) %>%
+                     total_col = FALSE,
+                     col_totals_prefix = "N (%) = ") %>%
   mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
   knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
-               booktabs = TRUE,
+               booktabs = TRUE, linesep = "",
                col.names = c("", "", "Treatment", "Control")) %>%
@@
 
-<<< overview of the results>>>
-
-<<<how they fit in existing literature -- need some references here>>>>
+Understanding the impact of COVID-19 closures of small businesses can help the Government of Ontario prepare to rebuild once the immediate health treat is contained.
+In particular, the contributions of restaurant businesses to the local economy have to be studied in terms of employment and revenue generation.
+According to The Associated Press, there was a 20% decline in employment in the restaurant, hotel, and entertainment sector between November 2019 and November 2020[@ap].
+The National Restaurant Association reports a total loss industry-wide of $120 billion between March and May 2020 alone [@rd].
+Although these figures are based on United States data, the findings from our experiment show a similarly concerning reality in Ontario.
+Swift action to protect and uplift the local economy will be crucial in the upcoming months.
 
@@
        x = "Revenue in July 2021 (in thousands of Canadian dollars)",
-       y = "Number of restaurants")
+       y = "Number of restaurants",
+       title = "The revenue distribution was lower for the treatment sample")
 ```
@@
 
-grid.arrange(p1, p2, ncol = 2)
+grid.arrange(p1, p2, ncol = 2, top = "Employment distributions were lower for the treatment sample")
 ```
@@
 
-```{r servicetypeimpact, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
-survey_2 %>%
-  filter(service_type != "NA") %>%
-  ggplot(aes(x = service_type, y = revenue / 1000, fill = group)) +
-  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
+```{r servicetypeimpact, fig.cap = "Survey 2 revenue distributions for service types with means marked", fig.width=7, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
+# from https://stackoverflow.com/questions/47651868/split-violin-plot-with-ggplot2-with-quantiles
+
+GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, draw_group = function(self, data, ..., draw_quantiles = NULL){
+  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
+  grp <- data[1,'group']
+  newdata <- plyr::arrange(transform(data, x = if(grp%%2==1) xminv else xmaxv), if(grp%%2==1) y else -y)
+  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
+  newdata[c(1,nrow(newdata)-1,nrow(newdata)), 'x'] <- round(newdata[1, 'x']) 
+  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
+    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <= 
+                                              1))
+    quantiles <- create_quantile_segment_frame(data, draw_quantiles)
+    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
+    aesthetics$alpha <- rep(1, nrow(quantiles))
+    both <- cbind(quantiles, aesthetics)
+    quantile_grob <- GeomPath$draw_panel(both, ...)
+    ggplot2:::ggname("geom_split_violin", grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
+  }
+  else {
+    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
+  }
+})
+
+geom_split_violin <- function (mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) {
+  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, position = position, show.legend = show.legend, inherit.aes = inherit.aes, params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
+}
+
+means <- survey_2 %>%
+  filter(service_type != "NA" & revenue != "NA") %>%
+  group_by(group, service_type) %>%
+  summarise(mean = mean(revenue) / 1000)
+
+ggplot() +
+  geom_split_violin(data = (survey_2 %>% filter(service_type != "NA")), aes(x = service_type, y = revenue / 1000, fill = group), color = NA) +
+  geom_errorbar(data = means, aes(x = service_type, y = mean, ymax = mean, ymin = mean, fill = group), position = "dodge") +
   labs(fill = NULL,
        x = "Service type provided",
-       y = "Mean revenue (in thousands of Canadian dollars") +
+       title = "Revenues were more heavily impacted for dine-in only establishments",
+       y = "Revenue (in thousands of Canadian dollars)") +
   scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
@@
 
-```{r minorityimpact, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=5, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
-bind_rows(
+```{r minorityimpact, fig.cap="Survey 2 revenue distributions for minority status with means marked", fig.width=6, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
+data <- bind_rows(
   survey_2 %>%
@@
 ) %>% 
-  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
-  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
-  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
+  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No"))
+
+means <- data %>%
+  filter(service_type != "NA" & revenue != "NA") %>%
+  group_by(group, minority) %>%
+  summarise(mean = mean(revenue) / 1000)
+
+ggplot() +
+  geom_split_violin(data = data, aes(x = minority, y = revenue / 1000, fill = group), color = NA) +
+  geom_errorbar(data = means, aes(x = minority, y = mean, ymax = mean, ymin = mean, fill = group), position = "dodge") +
   labs(fill = NULL,
        x = "Racial and ethnic minorities",
-       y = "Mean revenue (in thousands of Canadian dollars") +
+       title = "Minority-owned businesses were more heavily impacted",
+       y = "Revenue (in thousands of Canadian dollars)") +
   theme_minimal()
@@
 
-```{r nonresponse, fig.cap="More than half of surveyed restaurants did not respond", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+```{r nonresponse, fig.cap="Nonresponse and partial response rates for Survey 1 and 2", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
 num_treat_sample <- as.numeric(count(table_for_surveys %>% filter(group == "treatment")))
@@
   geom_bar(stat = "identity", position = "dodge") +
+  labs(title = "More than half of surveyed restaurants did not respond") +
   facet_wrap(~Survey) +
@@
 minimum_wage = 14.25 # https://www.ontario.ca/document/your-guide-employment-standards-act-0/minimum-wage
-management_service = 195 # https://www.alchemer.com/plans-pricing/small-teams/
+management_service = 1300 # https://www.alchemer.com/plans-pricing/small-teams/
 average_call_mins = 7

### 2021-02-20 scripts/extra_graphs_tables_for_paper.Rmd
add lorena's text and update graphs

@@
 ```
+
+```{r}
+bind_rows(
+  survey_2 %>%
+    filter(indigenous == "yes" | visible == "yes") %>%
+     mutate(minority = "Visible minority / Indigenous")
+  ,
+  survey_2 %>%
+   filter(indigenous == "no" & visible == "no") %>%
+    mutate(minority = "No")
+) %>% 
+  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
+  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
+  geom_violin() +
+  labs(fill = NULL,
+       x = "Racial and ethnic minorities",
+       y = "Mean revenue (in thousands of Canadian dollars") +
+  theme_minimal()
+```
+
+```{r}
+bind_rows(
+  survey_2 %>%
+    filter(indigenous == "yes" | visible == "yes") %>%
+     mutate(minority = "Visible minority / Indigenous")
+  ,
+  survey_2 %>%
+   filter(indigenous == "no" & visible == "no") %>%
+    mutate(minority = "No")
+) %>% 
+  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
+  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
+  geom_split_violin() +
+  labs(fill = NULL,
+       x = "Racial and ethnic minorities",
+       y = "Mean revenue (in thousands of Canadian dollars") +
+  theme_minimal()
+```
+
+```{r}
+bind_rows(
+  survey_2 %>%
+    filter(indigenous == "yes" | visible == "yes") %>%
+     mutate(minority = "Visible minority / Indigenous")
+  ,
+  survey_2 %>%
+   filter(indigenous == "no" & visible == "no") %>%
+    mutate(minority = "No")
+) %>% 
+  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
+  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
+  geom_violin() +
+  labs(fill = NULL,
+       x = "Racial and ethnic minorities",
+       y = "Mean revenue (in thousands of Canadian dollars") +
+  theme_minimal()
+```
+
+```{r servicetypeimpactx, fig.cap="Revenues more heavily impacted for dine-in only establishments", fig.width=6, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
+survey_2 %>%
+  filter(service_type != "NA") %>%
+  ggplot(aes(x = service_type, y = revenue / 1000, fill = group)) +
+  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
+  labs(fill = NULL,
+       x = "Service type provided",
+       y = "Mean revenue (in thousands of Canadian dollars") +
+  scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
+  theme_minimal()
+```
+
+```{r minorityimpactx, fig.cap="Minority-owned businesses were more heavily impacted", fig.width=4.5, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE, out.width = '60%', fig.align = "center"}
+bind_rows(
+  survey_2 %>%
+    filter(indigenous == "yes" | visible == "yes") %>%
+     mutate(minority = "Visible minority / Indigenous")
+  ,
+  survey_2 %>%
+   filter(indigenous == "no" & visible == "no") %>%
+    mutate(minority = "No")
+) %>% 
+  mutate(minority = fct_relevel(minority, "Visible minority / Indigenous", "No")) %>%
+  ggplot(aes(x = minority, y = revenue / 1000, fill = group)) +
+  geom_bar(position = "dodge", stat = "summary", fun.y = mean) +
+  labs(fill = NULL,
+       x = "Racial and ethnic minorities",
+       y = "Mean revenue (in thousands of Canadian dollars") +
+  theme_minimal()
+```

### 2021-02-20 scripts/04_restaurant_survey_frame.R
tidy up repo. clean up code in data_simulation. clearly mark #TODOs in paper. edit graphs.

@@ -5,7 +5,7 @@
 # Contact: amy.farrow@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-# - Need to have run 01, 03, and 03 scripts
+# - Need to have run 03_clean_restaurant_list_csvs
 
 
 #### Workspace setup ####
@@ -69,4 +69,5 @@ table_for_surveys <- table_for_surveys %>%
   mutate(ID = pull(tibble(sample(seq(1, first(count(table_for_surveys)), by = 1), size = first(count(table_for_surveys)), replace = FALSE)))) %>%
   select(-surveyed)
 
-write_csv(table_for_surveys, here::here("outputs/table_for_surveys.csv"))
+# Save the table for conducting the surveys
+write_csv(table_for_surveys, here::here("outputs/data/table_for_surveys.csv"))

### 2021-02-20 scripts/06_import_2016_census_data.R

@@ -1,184 +1,0 @@
-#### Preamble ####
-# Purpose: Get demographic & food service employment data of Ontario Public Health Regions from Statistics Canada
-# Author: Lala K. Sondjaja
-# Date: Sys.date()
-# Contact: k.sondjaja@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None
-
-### Install packages ###
-#install.packages("tidyverse")
-#install.packages("jsonlite")
-#install.packages("here")
-
-### Load packages ###
-library(tidyverse)
-library(here)
-library(janitor)
-
-### Load census dataset by Health Regions ###
-### Download link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058 ###
-### GEO_CODE indicates public health regions, taken from Census 2016 links:
-### https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0
-
-census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
-census_2016 <- janitor::clean_names(census_2016)
-
-names(census_2016)
-
-
-### Select demographic data to include, relating to employment, income, immigration status, minority groups, commute, etc. ###
-# Many categories
-# demographic_info <- c(1, 6, 8:33, 60:67, 100:104, 661:663, 694:707, 724:726, 1135:1136, 1139, 1140:1150, 1157, 1158, 1170, 1188, 1198, 1216, 1287, 1289:1292, 1324:1337, 1683:1697, 1884:1929)
-
-# Narrowed down categories
-demographic_info <- c(1, 8, 1324, 1290, 1917)
-
-
-### Function to get data from specific regions and rows ###
-
-get_region_data <- function(y){
-  census_2016 %>%
-    filter(geo_code_por == y,
-           member_id_profile_of_health_regions_2247 %in% demographic_info) %>%
-    select(dim_profile_of_health_regions_2247, member_id_profile_of_health_regions_2247, dim_sex_3_member_id_1_total_sex, dim_sex_3_member_id_2_male, dim_sex_3_member_id_3_female)
-}
-
-### Get data from the randomly selected Health Regions ###
-
-ontario <- get_region_data(35)
-
[…]

### 2021-02-20 scripts/notes_for_revenue_simulation.R

@@ -1,60 +1,0 @@
-# From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310030401&pickMembers%5B0%5D=2.1&pickMembers%5B1%5D=3.116
-# there are 27,885 employers in ontario 2020.
-
-# From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310030501&pickMembers%5B0%5D=2.116
-# there are 10,054 non-employers in ontario in 2020.
-
-# so 37,939 food service businesses in 2020.
-
-
-
-
-#### 2019:
-
-# From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022201&pickMembers%5B0%5D=2.1&pickMembers%5B1%5D=3.423
-# 25,836 employers
-
-# From https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310022301&pickMembers%5B0%5D=2.423
-# 6,968 non-employers
-
-# So 32,804 businesses in 2019
-
-# https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=2110017101&pickMembers%5B0%5D=1.7&pickMembers%5B1%5D=2.2&cubeTimeFrame.startYear=2015&cubeTimeFrame.endYear=2019&referencePeriods=20150101%2C20190101
-# full-service restaurants have 13,456,600,000 in revenue in 2019.
-# https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=2110017101&pickMembers%5B0%5D=1.7&pickMembers%5B1%5D=2.3&cubeTimeFrame.startYear=2015&cubeTimeFrame.endYear=2019&referencePeriods=20150101%2C20190101
-# limited-service eating places have 14,082,700,000 in revenue in 2019.
-
-# so averaging 839,510 in annual revenue.
-
-# 69,959 average per month.
-
-# This is including non-restaurants, presumably, because caterers would be included in "food services and drinking places"
-
-# From http://www.mbel.io/2019/08/23/kaggle-restaurant-revenue-prediction/
-# we can see the distribution looks like an F distribution, or a log normal distribution.
-# rf(n, df1, df2, ncp) = rf(num_rest, 10, 5) should have a mean of 5/3
-# so we would multiply by 41,975 to get the mean where we want.
-
-# looks like 2% closed permanently: https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=3310025001
[…]

### 2021-02-20 outputs/paper/data_simulation.Rmd

@@
 
+Analysis for this project uses the R statistical programming language [@R], and more specifically, the `tidyverse` package for data manipulation [@tidyverse].
+Because the data is managed using R Projects, `here` is used to reference file locations [@here].
+`kableExtra` formats tables [@kableExtra].
+`bookdown` is used to format the report [@bookdown].
+
+First, we read in the skeleton for the survey data.
+This is what we would hypothetically know about a restaurant before they took the survey.
+We keep only the ID numbers, the group, and the last 3 characters of the postal code, which the survey-taker will have to enter to verify identity.
+All other variables, like name and full address, are only kept in the only frame for surveying, which contains no private information.
+
 ```{r, warning = FALSE}
 # read in the data
-# NOTE: scripts 01_scrape_health_depts, 04_clean_restaurant_list_csvs, and 02_sampling_frame must have been run already
+# NOTE: scripts 01_scrape_health_depts, 
+# 02_stratified_cluster_sampling,
+# 03_clean_restaurant_list_csvs, 
+# 04_restaurant_survey_frame,
+# and 05_import_yelp_data must have been run already
 
-table_for_surveys <- read_csv(here::here("outputs/table_for_surveys.csv"))
+table_for_surveys <- read_csv(here::here("outputs/data/table_for_surveys.csv"))
 
@@
 
+From there, data was simulated for all questions asked on the survey.
+
 # Type of service provided
+
+First, some research:
 
@@
 ```{r, warning = FALSE}
+# randomly assign service_provided using ratios above
+
 set.seed(19)
@@
 ```{r, warning = FALSE}
+# randomly assign disability status using ratios above
+
 set.seed(19893)
@@
 
+Some research for racial and ethnic minorities and women in Canada and in business:
+
 ```{r, warning = FALSE}
 ### Load census dataset by Health Regions ###
-### Download link: https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058 ###
+### Download link: 
+### https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/details/
+### download-telecharger/comp/GetFile.cfm?Lang=E&FILETYPE=CSV&GEONO=058
 census_2016 <- read.csv(here("inputs", "data", "census_2016.csv"))
@@
            member_id_profile_of_health_regions_2247 %in% demographic_info) %>%
-    select(dim_profile_of_health_regions_2247, member_id_profile_of_health_regions_2247, dim_sex_3_member_id_1_total_sex, dim_sex_3_member_id_2_male, dim_sex_3_member_id_3_female)
+    select(dim_profile_of_health_regions_2247, 
+           member_id_profile_of_health_regions_2247, 
+           dim_sex_3_member_id_1_total_sex, 
+           dim_sex_3_member_id_2_male, 
+           dim_sex_3_member_id_3_female)
 }
@@
 # GEO_CODE indicates public health regions, taken from Census 2016 links:
-#https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=&Geo2=&Code2=&GEOCODE=35&type=0
+# https://www12.statcan.gc.ca/census-recensement/2016/dp-pd/prof/
+# search-recherche/lst/results-resultats.cfm?Lang=E&TABID=1&G=1&Geo1=&Code1=
+# &Geo2=&Code2=&GEOCODE=35&type=0
 
@@
 northwest <- get_region_data(3549)
-# southwestern <- get_region_data(3502)
-# Southwestern is a newer health unit. it was created by almagamating oxford and elgin-st. thomas units:
+# Southwestern was created by almagamating oxford and elgin-st. thomas units:
 oxford <- get_region_data(3552)
@@
 
-populationss <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
+populationss <- c("Total_Population", 
+                  "Indigenous_Population_25%_sample", 
+                  "Visible_Minority_25%_sample", 
+                  "Accommodation_and_Food_Services_25%_sample", 
+                  "Total_Population_Women")
 
 get_pop_info <- function(x){
-  c(as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Population, 2016"]),
-    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Aboriginal identity"]),
-    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "Total visible minority population"]),
-    as.numeric(x$dim_sex_3_member_id_1_total_sex[x$dim_profile_of_health_regions_2247 == "72 Accommodation and food services"]),
-    as.numeric(x$dim_sex_3_member_id_3_female[x$dim_profile_of_health_regions_2247 == "Total - Age groups and average age of the population - 100% data"]))
+  c(as.numeric(x$dim_sex_3_member_id_1_total_sex
+               [x$dim_profile_of_health_regions_2247 == "Population, 2016"]),
+    as.numeric(x$dim_sex_3_member_id_1_total_sex
+               [x$dim_profile_of_health_regions_2247 == "Aboriginal identity"]),
+    as.numeric(x$dim_sex_3_member_id_1_total_sex
+               [x$dim_profile_of_health_regions_2247 == 
+                   "Total visible minority population"]),
+    as.numeric(x$dim_sex_3_member_id_1_total_sex
+               [x$dim_profile_of_health_regions_2247 == 
+                   "72 Accommodation and food services"]),
+    as.numeric(x$dim_sex_3_member_id_3_female
+               [x$dim_profile_of_health_regions_2247 == 
+                   "Total - Age groups and average age of the population - 100% data"]))
 }
@@
 
-populations <- bind_cols(populationss, ontario_pop, haliburton_pop, algoma_pop, hamilton_pop, windsor_essex_pop, simcoe_muskoka_pop, timiskaming_pop, brant_pop, sudbury_pop, oxford_pop, elgin_pop, northwest_pop, waterloo_pop, durham_pop)
+populations <- bind_cols(populationss, 
+                         ontario_pop, 
+                         haliburton_pop, 
+                         algoma_pop, 
+                         hamilton_pop, 
+                         windsor_essex_pop, 
+                         simcoe_muskoka_pop, 
+                         timiskaming_pop, 
+                         brant_pop, 
+                         sudbury_pop, 
+                         oxford_pop, 
+                         elgin_pop, 
+                         northwest_pop, 
+                         waterloo_pop, 
+                         durham_pop)
 
-colnames(populations) <- c("Info", "Ontario", "Haliburton", "Algoma", "Hamilton", "Windsor_Essex", "Simcoe_Muskoka", "Timiskaming",
-                           "Brant", "Sudbury", "Oxford", "Elgin", "Northwest", "Waterloo", "Durham")
+colnames(populations) <- c("Info", "Ontario", "Haliburton", "Algoma", 
+                           "Hamilton", "Windsor_Essex", "Simcoe_Muskoka", 
+                           "Timiskaming", "Brant", "Sudbury", "Oxford", 
+                           "Elgin", "Northwest", "Waterloo", "Durham")
 
@@
   mutate(Southwestern = Oxford + Elgin) %>%
-  mutate(total_treat = Haliburton + Algoma + Hamilton + Windsor_Essex + Simcoe_Muskoka + Timiskaming,
-         total_control = Brant + Sudbury + Northwest + Waterloo + Durham + Southwestern) %>%
+  mutate(total_treat = 
+           Haliburton + Algoma + Hamilton + Windsor_Essex + Simcoe_Muskoka + Timiskaming,
+         total_control = 
+           Brant + Sudbury + Northwest + Waterloo + Durham + Southwestern) %>%
   select(-Oxford, -Elgin)
@@
 ```{r, warning = FALSE}
+# Split the population info into our treatment and control groups.
+
 populations_split <- matrix(ncol=4, nrow=5)
-populations_split[,1] <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
+populations_split[,1] <- c("Total_Population", 
+                           "Indigenous_Population_25%_sample", 
+                           "Visible_Minority_25%_sample", "
+                           Accommodation_and_Food_Services_25%_sample", 
+                           "Total_Population_Women")
 populations_split[,2] <- ontario_pop
@@
 
-treatment <- c(total_pop_treatment, indigenous_treatment, minority_treatment, food_services_treatment, women_treatment)
+treatment <- c(total_pop_treatment, 
+               indigenous_treatment, 
+               minority_treatment, 
+               food_services_treatment, 
+               women_treatment)
 populations_split[,3] <- treatment
@@
 
-control <- c(total_pop_control, indigenous_control, minority_control, food_services_control, women_control)
+control <- c(total_pop_control, 
+             indigenous_control, 
+             minority_control, 
+             food_services_control, 
+             women_control)
 populations_split[,4] <- control
@@
 ```{r, warning = FALSE}
-### Get percentage proportions of demographic groups of interest ###
+### Get percentage proportions of demographic groups of interest
 
@@
   for(j in 1:5){
-    populations_split_percentage[j,i] <- round(as.numeric(populations_split[j,i])/as.numeric(populations_split[1,i]), digits=3)
+    populations_split_percentage[j,i] <- 
+      round(as.numeric(populations_split[j,i])/as.numeric(populations_split[1,i]), 
+            digits=3)
   }
@@
 #populations_percentage[1, 2:4] <- c(1, 1, 1)
-populations_split_percentage[,1] <- c("Total_Population", "Indigenous_Population_25%_sample", "Visible_Minority_25%_sample", "Accommodation_and_Food_Services_25%_sample", "Total_Population_Women")
+populations_split_percentage[,1] <- c("Total_Population", 
+                                      "Indigenous_Population_25%_sample", 
+                                      "Visible_Minority_25%_sample", 
+                                      "Accommodation_and_Food_Services_25%_sample", 
+                                      "Total_Population_Women")
 
 populations_split_percentage <- as.data.frame(populations_split_percentage)
-colnames(populations_split_percentage) <- c("Info", "Ontario", "Treatment", "Control")
+colnames(populations_split_percentage) <- c("Info", 
+                                            "Ontario", 
+                                            "Treatment", 
+                                            "Control")
 
@@
 ```{r, warning = FALSE}
+# Randomly assign racial and ethnic minorities, and women, using the ratios above:
+
 set.seed(19893)
 survey_1 <- survey_1 %>%
-  mutate(woman = sample(c("yes","no","nonanswer"), size = num_total, prob = c(0.154, 0.836, 0.01), replace = TRUE))
+  mutate(woman = sample(c("yes","no","nonanswer"), 
+                        size = num_total, 
+                        prob = c(0.154, 0.836, 0.01), 
+                        replace = TRUE))
 
@@
     filter(group == "treatment") %>%
-    mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_treat, prob = c(0.009, 0.981, 0.01), replace = TRUE))
+    mutate(indigenous = sample(c("yes", "no", "nonanswer"), 
+                               size = num_treat, 
+                               prob = c(0.009, 0.981, 0.01), 
+                               replace = TRUE))
   ,
@@
     filter(group == "control") %>%
-   mutate(indigenous = sample(c("yes", "no", "nonanswer"), size = num_control, prob = c(0.011, 0.979, 0.01), replace = TRUE))
+   mutate(indigenous = sample(c("yes", "no", "nonanswer"), 
+                              size = num_control, 
+                              prob = c(0.011, 0.979, 0.01), 
+                              replace = TRUE))
 )
@@
     mutate(visible = sample(c("yes", "no", "nonanswer"), 
-                               size = first(count(survey_1 %>% filter(group == "treatment", indigenous != "yes"))), 
-                               prob = c(0.057, 0.933, 0.01), replace = TRUE))
+                               size = first(count(survey_1 %>% 
+                                                    filter(group == "treatment", 
+                                                           indigenous != "yes"))), 
+                               prob = c(0.057, 0.933, 0.01), 
+                            replace = TRUE))
   ,
@@
    mutate(visible = sample(c("yes", "no", "nonanswer"), 
-                              size = first(count(survey_1 %>% filter(group == "control", indigenous != "yes"))), 
-                              prob = c(0.08, 0.91, 0.01), replace = TRUE))
+                              size = first(count(survey_1 %>% 
+                                                   filter(group == "control", 
+                                                          indigenous != "yes"))), 
+                              prob = c(0.08, 0.91, 0.01), 
+                           replace = TRUE))
   ,
@@
 ```{r, warning = FALSE}
+# Randomly assign racial and ethnic minorities, and women, using the ratios above:
+
 set.seed(19893)
 survey_2 <- survey_2 %>%
-  mutate(woman = sample(c("yes","no","nonanswer"), size = num_total, prob = c(0.154, 0.836, 0.01), replace = TRUE))
+  mutate(woman = sample(c("yes","no","nonanswer"), 
+                        size = num_total, 
+                        prob = c(0.154, 0.836, 0.01), 
+                        replace = TRUE))
 
@@
     mutate(visible = sample(c("yes", "no", "nonanswer"), 
-                               size = first(count(survey_2 %>% filter(group == "treatment", indigenous != "yes"))), 
-                               prob = c(0.057, 0.933, 0.01), replace = TRUE))
+                               size = first(count(survey_2 %>% 
+                                                    filter(group == "treatment", 
+                                                           indigenous != "yes"))), 
+                               prob = c(0.057, 0.933, 0.01), 
+                            replace = TRUE))
   ,
@@
    mutate(visible = sample(c("yes", "no", "nonanswer"), 
-                              size = first(count(survey_2 %>% filter(group == "control", indigenous != "yes"))), 
+                              size = first(count(survey_2 %>% 
+                                                   filter(group == "control", 
+                                                          indigenous != "yes"))), 
                               prob = c(0.08, 0.91, 0.01), replace = TRUE))
@@
 ```{r, warning = FALSE}
+# Randomly assign shutdown using the ratios above only for the treatment group:
+
 set.seed(19893)
@@
 ```{r, warning = FALSE}
+# Randomly sample from the scaled F distribution to generate restaurant revenues:
+
 set.seed(19894)
@@
 ```{r, warning = FALSE}
+# Randomly sample from the scaled F distribution to generate restaurant revenues, and apply a random number around 1 to add variation:
+
 set.seed(19894)
@@
   select(-factor)
+
+# Reduce the treatment revenues to those that shutdown:
 
@@
   arrange(ID)
+
+# reduce the treatment revenues for those with more dine-in and less take-out service:
 
@@
 
+# reduce the treatment revenues further for racial and ethnic minority owned businesses:
+
 survey_2 <-
@@
     survey_2 %>%
-      filter((visible == "yes" | indigenous == "yes") & group == "treatment") %>%
+      filter((visible == "yes" | indigenous == "yes") 
+             & group == "treatment") %>%
       mutate(revenue = 0.88 * revenue)
@@
 2.4 FTE -> 1.9 FT + 1 PT.
-0.79 = 1.9 / 2.4 = 1.9 / (1.9 + 0.5)
-0.42 = 1 / 2.4 = 0.42 = 1 / (1.9 + 0.5)
+
+$ 1.9 / (1.9 + 0.5) = 1.9 / 2.4 = 0.79 $
+
+$ 1 / (1.9 + 0.5) = 1 / 2.4 = 0.42 $
 
@@
 ```{r, warning = FALSE}
+# Use revenue to generate realistic numbers of employees for restaurants:
+
 set.seed(19893)
@@
 X is some number less than or equal to 1.9.
-x / (x + 0.5)
-1 / (x + 0.5)
 
 ```{r, warning = FALSE}
+# Use revenue to generate realistic numbers of employees for restaurants:
+
 set.seed(19893)
@@
 ```{r, warning = FALSE}
+# Randomly select only a subset of all the generated responses to keep, simulating nonresponse:
+# Also randomly select columns to delete in partial responses, and delete the data from those rows/columns:
+
 num_cols_1 = 11
@@
 survey_1 <- survey_1 %>%
-  mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
+  mutate(nonresponse = sample(c("yes","partial","no"), 
+                              size = num_total, 
+                              prob = c(0.6, 0.01, 0.39), 
+                              replace = TRUE)) %>%
   filter(nonresponse != "yes")
@@
 survey_1 <- survey_1 %>%
-  mutate(which_partial = sample(c(4:num_cols_1), size = first(count(survey_1)), replace = TRUE))
+  mutate(which_partial = sample(c(4:num_cols_1), 
+                                size = first(count(survey_1)), 
+                                replace = TRUE))
 
@@
 ```{r, warning = FALSE}
+# Randomly select only a subset of all the generated responses to keep, simulating nonresponse:
+# Also randomly select columns to delete in partial responses, and delete the data from those rows/columns:
+
 num_cols_2 = 12
@@
 survey_2 <- survey_2 %>%
-  mutate(nonresponse = sample(c("yes","partial","no"), size = num_total, prob = c(0.6, 0.01, 0.39), replace = TRUE)) %>%
+  mutate(nonresponse = sample(c("yes","partial","no"), 
+                              size = num_total, 
+                              prob = c(0.6, 0.01, 0.39), 
+                              replace = TRUE)) %>%
   filter(nonresponse != "yes")
@@
 survey_2 <- survey_2 %>%
-  mutate(which_partial = sample(c(4:num_cols_1), size = first(count(survey_2)), replace = TRUE))
+  mutate(which_partial = sample(c(4:num_cols_1), 
+                                size = first(count(survey_2)), 
+                                replace = TRUE))
 
@@
 ```{r, warning = FALSE}
+# Save the two survey results tables:
+
 write_csv(survey_1, here("outputs/data/survey_1.csv"))
+
 write_csv(survey_2, here("outputs/data/survey_2.csv"))

### 2021-02-20 outputs/paper/paper.Rmd

@@
 library(gridExtra)  # for paired graphs
+library(cowplot)  # for plotting side by side
 
-# NOTE: scripts 01_scrape_health_depts, 04_clean_restaurant_list_csvs, and 02_sampling_frame, 
-# and markdown file data_simulation must have been run already
+# NOTE: scripts 01_scrape_health_depts, 
+# 02_stratified_cluster_sampling,
+# 03_clean_restaurant_list_csvs, 
+# 04_restaurant_survey_frame,
+# 05_import_yelp_data,
+# and Rmarkdown file data_simulation must have been run already
 
@@
 
-#TODO: citations for R and all packages used.
+#TODO: CITATIONS FOR R AND ALL PACKAGES LOADED ABOVE
 
@@
 Given the limitations of cluster sampling, stratifying the clusters by size helped ensure the experiment would be representative of Ontario.
-<stuff about the statistical properties of cluster and stratified sampling somewhere in here, cite textbook reading>.
+
+#TO DO: ADD STUFF ABOUT STATISTICAL PROPERTIES OF CLUSTER AND STRATIFIED SAMPLING. CITE TEXTBOOK READING
 
 ```{r, include = FALSE}
-treatment_control_groups <- read_csv(here::here("outputs/treatment_control_groups.csv"))
+treatment_control_groups <- read_csv(here::here("outputs/data/treatment_control_groups.csv"))
 ```
@@
   kableExtra::kable_styling() %>%
-  collapse_rows()
+  collapse_rows() %>%
+  column_spec(1, color = "#972D15")
 ```
@@
   column_spec(4, width = "6em") %>%
-  kableExtra::kable_styling(latex_options = c("scale_down"))
+  kableExtra::kable_styling(latex_options = c("scale_down")) %>%
+  row_spec(0, color = "#972D15")
 ```
@@
 ```{r, include = FALSE}
-table_for_surveys <- read_csv(here::here("outputs/table_for_surveys.csv"))
+table_for_surveys <- read_csv(here::here("outputs/data/table_for_surveys.csv"))
 ```
@@
 Revenue and number of employees were collected as measures of the restaurant's performance and impact on the local employment levels.
-These were the primary indicators of interest, due to the <GOVERNMENT ORGANIZATION>>>>> focus on economic stability and employment levels.
+These were the primary indicators of interest, due to the Ontario Ministry of Economic Development, Job Creation and Trade's focus on economic stability and employment levels.
 
@@
 
-<Something about enforcement of closures-- how have fines worked during covid closures?)
+#TODO: ADD SOMETHING ABOUT ENFORCEMENT OF CLOSURES. FINES? HOW HAS IT WORKED SO FAR? CITE SOURCE.
 
@@
 
-<<<<<<<<<<<<survey strengths and weaknesses>>>>>>>>>>>>>
+#TODO: ADD SURVEY STRENGTHS AND WEAKNESSES
 
@@
     mutate(group = fct_relevel(group, "treatment", "control"),
-           service_type = fct_relevel(service_type, "dinein", "takeout", "both"),
+           service_type = fct_relevel(service_type, "dinein", "both", "takeout"),
            disability = fct_relevel(disability, "yes", "no", "nonanswer"),
@@
 
-## Survey 1 results
+## Results ^[More information about the Survey 1 and Survey 2 results can be found in [the report *Data for the Ontario Restauarant Closures Experiment*](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment/blob/main/outputs/paper/data_simulation.pdf).]
 
-<<<<<Consider: do we need to plot more raw data?>>>>>>>>>>>
+### Survey 1
+
+#TODO: HOW CAN WE PLOT MORE RAW DATA?
 
@@
                      col_totals_prefix = "N (%) = ") %>%
-  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
+  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is Indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
   knitr::kable(caption = "Summary statistics for treatment and control baselines",
@@
                col.names = c("", "", "Treatment", "Control")) %>%
-  kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
+  kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19), stripe_color = "#fbf7e6") %>%
+  column_spec(1, color = "#972D15")
 ```
@@
        y = "Number of restaurants",
-       title = "Revenue distributions were similar in the treatment and control samples")
+       title = "Revenue distributions were similar in the treatment and control samples") +
+  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
 ```
@@
   xlim(0,35) +
-  scale_y_continuous(limits = c(0,150), breaks = c(0,25,50,75,100,125,150)) +
+  scale_y_continuous(limits = c(0,135), breaks = c(0,25,50,75,100,125,150)) +
   theme_minimal() +
@@
        y = "Number of restaurants",
-       title = "Part-time employees")
+       title = "Part-time employees") +
+  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
 
@@
   xlim(0,35) +
-  scale_y_continuous(limits = c(0,100), breaks = c(0,25,50,75,100)) +
+  scale_y_continuous(limits = c(0,75), breaks = c(0,25,50,75)) +
   theme_minimal() +
@@
        y = "Number of restaurants",
-       title = "Full-time employees")
+       title = "Full-time employees")  +
+  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
 
-grid.arrange(p1, p2, ncol = 2, top = "Employment distributions were similar in the treatment and control samples")
+# using https://stackoverflow.com/questions/37052059/how-to-add-a-title-for-a-grid-layout-figure-in-ggplot2
+p <- plot_grid(p1, p2, align = "h", nrow = 1, rel_widths = c(0.555,0.445))
+title <- ggdraw() + draw_label("Employment distributions were similar in the treatment and control samples")
+plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1))
 ```
 
-## Survey 2 results
+### Survey 2
 
-<<<<<Consider: do we need to plot more raw data?>>>>>>>>>>>
+#TODO: HOW CAN WE PLOT MORE RAW DATA?
 
@@
                      col_totals_prefix = "N (%) = ") %>%
-  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
+  mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is Indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
   knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
@@
                col.names = c("", "", "Treatment", "Control")) %>%
-   kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19))
+   kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19), stripe_color = "#fbf7e6") %>%
+  column_spec(1, color = "#972D15")
 ```
@@
 ### FINDING ONE
+
+#TODO: WRITE ABOUT FINDING 1
 Closures had a negative impact on revenues and employment counts Figure \@ref(fig:postrevenue) Figure \@ref(fig:postemployees)
@@
        y = "Number of restaurants",
-       title = "The revenue distribution was lower for the treatment sample")
+       title = "The revenue distribution was lower for the treatment sample") +
+  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
 ```
@@
   xlim(0,35) +
-  scale_y_continuous(limits = c(0,150), breaks = c(0,25,50,75,100,125,150)) +
+  scale_y_continuous(limits = c(0,135), breaks = c(0,25,50,75,100,125)) +
   theme_minimal() +
@@
        y = "Number of restaurants",
-       title = "Full-time employees")
+       title = "Full-time employees") +
+  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
 
-grid.arrange(p1, p2, ncol = 2, top = "Employment distributions were lower for the treatment sample")
+p <- plot_grid(p1, p2, align = "h", nrow = 1, rel_widths = c(0.555,0.445))
+title <- ggdraw() + draw_label("Employment distributions were lower for the treatment sample")
+plot_grid(title, p, ncol=1, rel_heights=c(0.1, 1))
 ```
 
+#TODO: WRITE ABOUT SUGGESTION
 Suggestion: funding for businesses and temporary unemployment
@@
 
+#TODO: WRITE ABOUT FINDING 2
 Closures had a stronger negative impact on dine-in only restaurants Figure \@ref(fig:servicetypeimpact)
 
-```{r servicetypeimpact, fig.cap = "Survey 2 revenue distributions for service types with means marked", fig.width=7, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
+```{r servicetypeimpact, fig.cap = "Survey 2 revenue distributions for service types with means marked", fig.width=7, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '80%', fig.align = "center"}
 # from https://stackoverflow.com/questions/47651868/split-violin-plot-with-ggplot2-with-quantiles
@@
   geom_split_violin(data = (survey_2 %>% filter(service_type != "NA")), aes(x = service_type, y = revenue / 1000, fill = group), color = NA) +
-  geom_errorbar(data = means, aes(x = service_type, y = mean, ymax = mean, ymin = mean, fill = group), position = "dodge") +
+  geom_errorbar(data = means, 
+                aes(x = service_type, y = mean, ymax = mean, ymin = mean, fill = group), 
+                position = "dodge",
+                color = "#972D15") +
   labs(fill = NULL,
@@
        y = "Revenue (in thousands of Canadian dollars)") +
-  scale_x_discrete(labels = c( "Dine-in Only", "Take-out only", "Both")) +
-  theme_minimal()
+  scale_x_discrete(labels = c( "Dine-in Only", "Both dine-in and take-out", "Take-out only")) +
+  theme_minimal() +
+  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
 ```
 
+#TODO: WRITE ABOUT SUGGESTION
 Suggestion: technical support for restaurants to increase takeout business
@@
 ### FINDING THREE
-Closures had a stronger negative impact on indigenous or visible minority-owned businesses. Figure \@ref(fig:minorityimpact)
+
+#TODO: WRITE ABOUT FINDING THREE
+Closures had a stronger negative impact on Indigenous or visible minority-owned businesses. Figure \@ref(fig:minorityimpact)
 
@@
   geom_split_violin(data = data, aes(x = minority, y = revenue / 1000, fill = group), color = NA) +
-  geom_errorbar(data = means, aes(x = minority, y = mean, ymax = mean, ymin = mean, fill = group), position = "dodge") +
+  geom_errorbar(data = means,
+                aes(x = minority, y = mean, ymax = mean, ymin = mean, fill = group),
+                position = "dodge",
+                color = "#972D15") +
   labs(fill = NULL,
        x = "Racial and ethnic minorities",
-       title = "Minority-owned businesses were more heavily impacted",
+       title = "Revenues were more heavily impacted for minority-owned businesses",
        y = "Revenue (in thousands of Canadian dollars)") +
-  theme_minimal()
+  theme_minimal() +
+  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
 ```
 
+#TODO: WRITE ABOUT SUGGESTION
 Suggestion: grants for minority business owners
 
-## Ethics ? Or integrate in other sections.
+##TODO: ADD AN ETHICS SECTION HERE? OR INTEGRATE IN THE REST?
 
@@
 
-External validity, internal validity, cluster sampling.
-Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them.
-It was ethically unsound to run the experiment on the entire province, so sampling was necessary.
+#TODO: TALK ABOUT EXTERNAL VALIDITY AND THE ISSUES WITH CLUSTER SAMPLING.
+Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them. It was ethically unsound to run the experiment on the entire province, so sampling was necessary.
 
-Legally registered businesses only.
+#TODO: TALK ABOUT HOW IT ONLY CATCHES LEGALLY REGISTERED BUSINESSES
 
-Survey non-response. Figure \@ref(fig:nonresponse)
+#TODO: TALK ABOUT SURVEY NON-RESPONSE AND HOW IT AFFECTS ACCURACY. CITE READINGS. Figure \@ref(fig:nonresponse)
 
@@
   facet_wrap(~Survey) +
-  theme_minimal()
+  theme_minimal() +
+  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
 
@@
 
-Self-reported information.
+#TODO: TALK ABOUT THE ISSUES WITH SELF-REPORTED INFORMATION. CITE READING.
 
@@
 
-For statistical analysis, this would require propensity score weighting.
+#TODO: TALK ABOUT POTENTIALLY USING PROPENSITY SCORE WEIGHTING TO MAKE SURE THAT THE RESULTS REFLECT ONTARIO'S RACIAL DEMOGRAPHICS.
+SEE DATA_SIMULATION FILE FOR COMPARISON OF ONTARIO, TREATMENT, AND CONTROL.
+CITE READING.
+
+#TODO: TALK ABOUT RESEARCH INTO HOW TO EFFECTIVELY SUPPORT BUSINESSES
 
@@
 
-phone_interviewer_cost = round(restaurants*survey_total*response_rate, 2)*average_call_mins/60*minimum_wage
+phone_interviewer_cost = round(restaurants * survey_total*response_rate, 2) * average_call_mins / 60 * minimum_wage
 
-postage_cost = (restaurants*2)*indiv_postage
+postage_cost = (restaurants * 2) * indiv_postage
 
@@
   kable_styling() %>% 
-  row_spec(0, bold = T, color = "white", background = "gray") %>% 
+  row_spec(0, bold = T, color = "white", background = "#972D15") %>% 
   row_spec(4, bold = T) %>%
@@
 
-TODO: add survey screenshot
+TODO: ADD A SURVEY SCREENSHOT. REFERENCE IN THE MAIN PAPER.
 
@@
 
-TODO: add complete list of survey questions
+TODO: ADD A COMPLETE LIST OF SURVEY QUESTIONS AND OPTIONS. REFERENCE IN THE MAIN PAPER.
 

### 2021-02-20 outputs/paper/paper.Rmd
edit

@@
 library(finalfit) # for a summary table
-library(gridExtra)  # for paired graphs
 library(cowplot)  # for plotting side by side
@@
 
-#TODO: CITATIONS FOR R AND ALL PACKAGES LOADED ABOVE
+#TODO: CITATIONS FOR R AND ALL PACKAGES LOADED ABOVE, AND IN SCRIPTS/SIMULATION FILE
 
@@
 * Demographic information
-- Disability status: According to the UN Convention on the Rights of Persons with Disabilities, persons with disabilities are described as having "long-term physical, mental, intellectual or sensory impairments which in interaction with various barriers may hinder their full and effective participation in society on an equal basis with others."
-- Indigenous status: According to the Government of Canada, Indigenous people include "First Nations (North American Indian), Métis or Inuit and/or those who reported Registered or Treaty Indian status, that is registered under the Indian Act of Canada, and/or those who reported membership in a First Nation or Indian band".
-- Visible minority (non-Indigenous) status: "Visible minority" is defined by the Government of Canada as "persons, other than aboriginal peoples, who are non-Caucasian in race or non-white in colour."
-- Gender identity
+    + Disability status: According to the UN Convention on the Rights of Persons with Disabilities, persons with disabilities are described as having "long-term physical, mental, intellectual or sensory impairments which in interaction with various barriers may hinder their full and effective participation in society on an equal basis with others."
+    + Indigenous status: According to the Government of Canada, Indigenous people include "First Nations (North American Indian), Métis or Inuit and/or those who reported Registered or Treaty Indian status, that is registered under the Indian Act of Canada, and/or those who reported membership in a First Nation or Indian band".
+    + Visible minority (non-Indigenous) status: "Visible minority" is defined by the Government of Canada as "persons, other than aboriginal peoples, who are non-Caucasian in race or non-white in colour."
+    + Gender identity
 * Type of service provided (dine-in, take-out, or both)
@@
 * Employees
-- Number of full-time employees (30 hours/week or more)
-- Number of part-time employees (less than 30 hours/week)
+    + Number of full-time employees (30 hours/week or more)
+    + Number of part-time employees (less than 30 hours/week)
 
@@
 * Demographic information
-- Disability status
-- Indigenous status
-- Visible minority (non-Indigenous) status
-- Gender identity
+    + Disability status
+    + Indigenous status
+    + Visible minority (non-Indigenous) status
+    + Gender identity
 * Type of service provided (dine-in, take-out, or both)
@@
        y = "Revenue (in thousands of Canadian dollars)") +
-  scale_x_discrete(labels = c( "Dine-in Only", "Both dine-in and take-out", "Take-out only")) +
+  scale_x_discrete(labels = c( "Dine-in only", "Both dine-in and take-out", "Take-out only")) +
   theme_minimal() +

### 2021-02-21 outputs/paper/paper.Rmd
Writing P1
P2 to follow!

--- 2021-02-20 outputs/paper/paper.Rmd
@@
 
-#TODO: CITATIONS FOR R AND ALL PACKAGES LOADED ABOVE
+Analysis for this report uses the R statistical programming language [@R], and more specifically, the tidyverse package for data manipulation [@tidyverse].
+To facilitate a reproducible workflow, here is used to reference file locations [@here].
+Graphs and tables use features from cowplot, finalfit, gridExtra, and kableExtra [@cowplot] [@finalfit] [@gridExtra] [@kableExtra].
+Finally, bookdown is used to format the report [@bookdown].
+
+In addition to survey data collected by Petit Poll, this report relies on publicly available federal census data [@census_2016] and data from provincial public health departments[@inspection].
+
+This section presents details on the data collection approach and methods, and the steps taken to ensure accuracy.
 
@@
 
-This experiment used two-stage stratified cluster sampling with survey data collection.
+This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into groups, or stata, and subsequently divided into clusters.
+A random sample is drawn from each stratum and each cluster [@gertler].
 
@@
 
-A list of Ontario local health authorities (LHAs) that carry out food inspections was used to identify units that inspect restaurants.
-Using census data from 2016, these LHAs were sorted by population covered by the LHA, and the list was stratified into equally sized strata of small (less than 150,000 population), medium (150,000 to 400,000 population), and large (more than 400,000 population) LHAs.
-This list of stratified LHAs was the frame at the cluster level.
+A list of Ontario local health authorities (LHAs) was used to identify units that carry out food inspections of restaurants.
+Using census data from 2016, these LHAs were sorted by population size, and the list was stratified into equally sized strata: small LHAs (population of less than 150,000), medium LHAs (population of 150,000 to 400,000), and large LHAs (population of more than 400,000).
+The stratified LHAs produced the frame, or list of units of interest from which to draw a sample, at the cluster level.
 
@@
 
-Once the treatment and control LHAs were selected, each corresponding Food Inspection unit was contacting, and a list of all registered restaurants in each LHA was obtained.
+Once the treatment and control LHAs were selected, each corresponding Food Inspection unit was contacted, and a list of all registered restaurants in each LHA was obtained.
 Each restaurant was listed by name and address.
@@
 The table for surveys was used to generate 2,006 mailers to be sent to each restaurant on the list.
-Each mailer was a small envelope containing a sheet that explained the survey, provided a link to the survey, and provided a QR code that went to the same place as the link.
+Each mailer was a small envelope containing a sheet that invited the restaurant owner to participate, explained the survey, provided a link to the survey, and provided a QR code that went to the same place as the link.
 There was also a copy of the survey contained in a mailer envelope and a contact number, allowing restaurant owners to complete the survey by phone or mail if they did not feel able to complete it online.
 This procedure was repeated for Survey 1 and Survey 2.
-If there was no response within two weeks, the restaurant was contacted by phone, and again if there was no response five days later.
+If there was no response within two weeks, the restaurant was contacted by phone, and again five days letter if there was no response.
 
 Each link and paper survey was personalized to the restaurant's ID number.
-The link lead to the survey, which asked for confirmation of the last three letters of the restaurant's postal code.
+The link lead to the survey, which asked for confirmation of the last three digits of the restaurant's postal code.
 This was to ensure that no mailing mistakes were made, and to prevent duplicate data collection.
@@
 
-This survey cost $6711.18. A detailed breakdown of costs can be found on [Appendix A](#appendixA).
+This survey cost $6,711.18. A detailed breakdown of costs can be found on [Appendix A](#appendixA).
 
-The data from the survey was tied to the ID number and last three digits of the postal code, but not the restaurant name or address.
+The data from the survey was tied to the ID number and last three digits of the postal code, but not the restaurant name or address, and the restaurant owner's name was not collected.
 This was to ensure data privacy.
 The identifying information was kept in a separate dataframe (Table for Surveys) than the survey answers (Survey 1 Data, Survey 2 Data).
+
+#TODO: MAKE TIMELINE TABLE AND REFERENCE (###)
+
+A project timeline can be found in Table ###.
 
@@
 Take-out and delivery were permitted.
-This type of partial shutdown was selected because it has been the most common type of shutdown since the pandemic began.
+This type of partial shutdown was selected because it has been the mandated type of shutdown during the Grey level, or lockdown, of the provincial COVID-19 response framework [@restrict].
 
-#TODO: ADD SOMETHING ABOUT ENFORCEMENT OF CLOSURES. FINES? HOW HAS IT WORKED SO FAR? CITE SOURCE.
+To date, mandated closure enforcement has included issuing fines from $750 to $100,000 to businesses found in violation of the province of Ontario's emergency orders [@enforce].
+Additionally, provincial offences officers, including police officers, have the authority to disperse crowds indoors as well as outdoors [@police].
 
@@
 
-Survey 2 collected the following data:
+Survey 2 followed a similar format as Survey 1, with the addition of a question about closures. It collected the following data:
 
@@
 * Closures (none, temporary, or permanent)
-* Revenue in May 2021
+* Revenue in July 2021
 * Employees
@@
 
-#TODO: ADD SURVEY STRENGTHS AND WEAKNESSES
+The scope of this experiment required a structured questionnaire that was easy to distribute, easy to answer, cost effective, reliable, and that provided flexibility of mode of response, including online, over the phone, or on paper.
+With these features in mind, a survey was an appropriate choice.
+However, due to the rigidity of pre-determined questions, the survey format might lack potential depth, reducing complex circumstances to simple data points that are easier to collect, manage, and analyze.
+To account for this, the questions were carefully designed to gather, exactly and only, the necessary data for our study.
 
@@
 
-## Results ^[More information about the Survey 1 and Survey 2 results can be found in [the report *Data for the Ontario Restauarant Closures Experiment*](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment/blob/main/outputs/paper/data_simulation.pdf).]
+## Results ^[More information about the Survey 1 and Survey 2 results can be found in [the report *Data for the Ontario Restaurant Closures Experiment*](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment/blob/main/outputs/paper/data_simulation.pdf).]
+
+Reaching restaurant owners to better understand their businesses, and the impact of closures, was a crucial component of this experiment.
+Approximately 39% of individuals selected to participate completed or partially completed the surveys.
+This section provides an overview of the data gathered from each survey.
 
@@
 
-The initial survey provided an overview of the characteristics of the treatment and control groups.
+The initial survey provided a clear description of the characteristics of the treatment and control groups.
 As indicated in Table \@ref(tab:survey1summary), the groups are equivalent, showing no notable differences across any of the variables studied.
@@
 
-Figure \@ref(fig:baselinerevenue) Figure \@ref(fig:baselineemployees)
-
-Counterfactuals established.
+The baseline for reported revenue, based on information from May 2021, can be found in Figure \@ref(fig:baselinerevenue).
+The baseline for employement of full-time and part-time employees is shown in Figure \@ref(fig:baselineemployees).
 
@@
 
-The second survey results showed marked differences between treatment and control groups in most areas.
+The second survey results showed marked differences between treatment and control groups in most variables.
 A summary of these results is found in Table \@ref(tab:survey2summary).
 Naturally, a salient difference is found in service type, with dine-in restaurants decreasing due to mandated shutdowns – the intervention itself – with 7% of restaurants in the control group providing dine-in service, and only 4% in the treatment group.
-Similarly, the mean revenue decreases noticeably for the treatment group (\$45,959.60) compared to the control group ($70675.60).
-The mean number of employees, both full-time and part-time, shows a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
+Similarly, the mean revenue decreases noticeably for the treatment group (\$45,959.60) compared to the control group ($70,675.60).
+The mean numbers of employees, both full-time and part-time, show a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
+A visual representation of the differences between treatment and control groups for revenue and number of employees can be found in Figure \@ref(fig:postrevenue) and Figure \@ref(fig:postemployees) respectively.
+
+#TODO: ADD SENTENCE ABOUT REST OF VARIABLES?
 
@@
 
+Petit Poll commends the Ontario Ministry of Economic Development, Job Creation and Trade for its commitment to learn more about the impact of restaurant closures in the province.
+This study has uncovered three main findings, supplemented in this section by a series of recommendations.
+Additionally, this section elaborates on relevant ethical considerations, potential biases and limitations.
+The final section presents some initial thoughts for future related research.
+
 ## Overview
@@
 Although these figures are based on United States data, the findings from our experiment show a similarly concerning reality in Ontario.
-Swift action to protect and uplift the local economy will be crucial in the upcoming months.
+
+The experiment, which consisted of an initial survey, a two-week restaurant closure intervention, and a second survey, revealed that the impact of closures is not distributed equally across service types, nor across restaurant owner demographics.
+Swift action to protect and uplift the local economy, particularly dine-in restaurants and restaurants owned by Indigenous peoples or members of visible minority groups, will be crucial in the upcoming months.
 
@@
 
-### FINDING ONE
+To prevent a misleading estimate of the counterfactual in this experiment, the effects of the intervention are not evaluated by comparing the survey results before and after the intervention, but rather by comparing the treatment and control groups after the intervention.
+The following subsections provide further detail on each of the main findings.
 
-#TODO: WRITE ABOUT FINDING 1
-Closures had a negative impact on revenues and employment counts Figure \@ref(fig:postrevenue) Figure \@ref(fig:postemployees)
+### Closures had a negative impact on revenues and employment counts
+
+As noted in the results from survey 2, the intervention led to a noticeable difference in reported revenues.
+The mean reported revenue for the treatment group was \$45,959.60 and $70,675.60 for the control.
+The revenue distribution for both groups is show in Figure \@ref(fig:postrevenue).
+
+The mean numbers of employees, both full-time and part-time, show a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
+Figure \@ref(fig:postemployees) shows further detail of this finding.
+
+With these effects in mind, Petit Poll supports the Government of Ontario's programs in support of small businesses: the Ontario Small Business Support Grant, the Personal Protective Equipment Relief Grant, and the current Property Tax and Energy Rebate Grants [@relief].
+Additionally, based on the evidence shown in this report, it is important to consider developing provincial financial support programs for furloughed employees, in addition to standing federal programs like Employment Insurance, that directly address the negative impact of COVID-19 closures.
+Ensuring the protection of workers in the restaurant industry, not only physically as the spread of the virus is contained, but economically with financial aid will be crucial to the success of mandated closures.
 
@@
 
-#TODO: WRITE ABOUT SUGGESTION
-Suggestion: funding for businesses and temporary unemployment
+### Closures had a stronger negative impact on dine-in only restaurant
 
-### FINDING TWO
+#TODO: ADD MEANS (###)
 
-#TODO: WRITE ABOUT FINDING 2
-Closures had a stronger negative impact on dine-in only restaurants Figure \@ref(fig:servicetypeimpact)
+It is worth noting that the negative impact on revenue was not equally distributed across all three types of establishments.
+Dine-in restaurants suffered significant losses, with restaurant owners in the treatment group who selected "dine-in" reporting a mean revenue of ###, those who selected "take-out" reporting ###, and "both", ###.
+The control group reported ###, ###, and ### for dine-in, take-out, and both, respectively.
+Figure \@ref(fig:servicetypeimpact) shows a comparison of revenue distributions for restaurants offering dine-in service, take-out, or both.
+
+The effect of mandated closures attenuated for take-out only restaurants.
+This indicates that providing restaurant owners with support to transition their regular operations to take-out only service should be considered.
+The City of Toronto-funded Digital Main Street, created by the Toronto Association of Business Improvement Areas, might serve as an exemplary approach.
+The program provides businesses with the tools and information to build an online presence.
+The free program includes an online learning platform, training programs, and support staff [@mainstreet].
+A parallel provincial program aimed directly at restaurant owners who wish to transition out of dine-in only service might help alleviate the economic pressures of COVID-19 mandated closures, while maintaining the necessary health emergency protocols.
 
@@
 
-#TODO: WRITE ABOUT SUGGESTION
-Suggestion: technical support for restaurants to increase takeout business
+### Closures had a stronger negative impact on Indigenous or visible minority-owned businesses
 
-### FINDING THREE
+#TODO: ADD MEANS (###)
 
-#TODO: WRITE ABOUT FINDING THREE
-Closures had a stronger negative impact on Indigenous or visible minority-owned businesses. Figure \@ref(fig:minorityimpact)
+The negative impact of mandated closures was not distributed equally across restaurant owner demographics.
+As indicated in Figure \@ref(fig:minorityimpact) restaurant owners who identified as Indigenous or as members of a visible minority group reported lower revenues in the treatment group than in the control.
+The mean revenue for those who identified as visible minority or Indigenous in the treatment group was ### and ### for those who did not.
+In the control group, the mean revenue for those who identified as Indigenous or as members of a visible minority group was ### and ### for those who did not.
+
+Protecting populations that face systemic inequalities is absolutely imperative to the success of any proposed pandemic response.
+Following the approach of the federal government might be a fruitful start.
+Currently, the Government of Canada offers interest-free loans and non-repayable contributions to Indigenous-owned businesses [@ibi].
+Further, the federal government has announced and collected applications to the Black Entrepreneurship Program, an initiative to ensure Black-owned businesses thrive [@bep].
+Petit Poll recommends Ontario take similar, yet bolder steps to ensure Indigenous and visible minority owners are not left behind in during the COVID-19 pandemic.
+To do so, restaurant-industry specific interest-free loans, non-repayable contributions, free educational programming, mentorship, and additional supports should be extended to Indigenous and visible minority restaurant owners in the province.
 
@@
 
-#TODO: WRITE ABOUT SUGGESTION
-Suggestion: grants for minority business owners
+### Implications
 
-##TODO: ADD AN ETHICS SECTION HERE? OR INTEGRATE IN THE REST?
+##TODO: Talk about broad economic interdependencies: restaurants as a key feature in neighbourhoods, closures impacting the desirability of an area, impacting the real estate market
+
+##TODO: Talk about individual level: gainful employment and psychological wellbeing, especially the role of the service industry in financial independence for oppressed/undereducated/immigrants or otherwise made-vulnerable folks
+
+## Ethics
+
+##TODO: WRITE ABOUT ETHICS AND BIAS, FIRST IN TERMS OF SURVEYS
+https://www.qualtrics.com/blog/ethical-issues-for-online-surveys/
+https://www.statcan.gc.ca/eng/dai/btd/variance_bias
 
@@
 
+#TODO: talk about research on individual impact (we look at owners and not employees, might be missing key info there)
+
+#TODO: briefly talk about potential unevenness of impact on franchises vs independent businesses.
+How were they impacted and what does that mean for our findings, are there connected?
+Are franchises more likely to already have take-out?
+Or be visible minority-owned?
+
 \newpage
@@
 
-# Appendix A
+# Appendix A {#appendixA}
 
@@
 
-# Appendix B
+# Appendix B {#appendixB}
 
@@
 
-# Appendix C
+# Appendix C {#appendixC}
 

### 2021-02-21 outputs/paper/paper.Rmd
Update
Typo fixes

@@
 
-From each strata, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control.
+From each stratum, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control.
 This was the sample at the cluster level.
@@
 
-Understanding the impact of COVID-19 closures of small businesses can help the Government of Ontario prepare to rebuild once the immediate health treat is contained.
+Understanding the impact of COVID-19 closures on small businesses can help the Government of Ontario prepare to rebuild once the immediate health threat is contained.
 In particular, the contributions of restaurant businesses to the local economy have to be studied in terms of employment and revenue generation.
@@
 
-The mean numbers of employees, both full-time and part-time, show a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
+The mean number of employees, both full-time and part-time, show a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
 Figure \@ref(fig:postemployees) shows further detail of this finding.
 
-With these effects in mind, Petit Poll supports the Government of Ontario's programs in support of small businesses: the Ontario Small Business Support Grant, the Personal Protective Equipment Relief Grant, and the current Property Tax and Energy Rebate Grants [@relief].
+With these effects in mind, Petit Poll supports the Government of Ontario's programs in benefit of small businesses: the Ontario Small Business Support Grant, the Personal Protective Equipment Relief Grant, and the current Property Tax and Energy Rebate Grants [@relief].
 Additionally, based on the evidence shown in this report, it is important to consider developing provincial financial support programs for furloughed employees, in addition to standing federal programs like Employment Insurance, that directly address the negative impact of COVID-19 closures.
-Ensuring the protection of workers in the restaurant industry, not only physically as the spread of the virus is contained, but economically with financial aid will be crucial to the success of mandated closures.
+Ensuring the protection of workers in the restaurant industry specifically, not only physically as the spread of the virus is contained, but economically with financial aid will be crucial to the success of mandated closures.
 
@@
 
-It is worth noting that the negative impact on revenue was not equally distributed across all three types of establishments.
+It is worth noting that the negative impact on revenue was not equally distributed across the three types of establishments.
 Dine-in restaurants suffered significant losses, with restaurant owners in the treatment group who selected "dine-in" reporting a mean revenue of ###, those who selected "take-out" reporting ###, and "both", ###.
@@
 
-The effect of mandated closures attenuated for take-out only restaurants.
+The effect of mandated closures is attenuated for take-out only restaurants.
 This indicates that providing restaurant owners with support to transition their regular operations to take-out only service should be considered.
@@
 The program provides businesses with the tools and information to build an online presence.
-The free program includes an online learning platform, training programs, and support staff [@mainstreet].
+The free program includes an online learning platform, training programs, and dedicated support staff [@mainstreet].
 A parallel provincial program aimed directly at restaurant owners who wish to transition out of dine-in only service might help alleviate the economic pressures of COVID-19 mandated closures, while maintaining the necessary health emergency protocols.
@@
 
-The negative impact of mandated closures was not distributed equally across restaurant owner demographics.
+The negative impact of mandated closures was not distributed equally across restaurant owner demographics either.
 As indicated in Figure \@ref(fig:minorityimpact) restaurant owners who identified as Indigenous or as members of a visible minority group reported lower revenues in the treatment group than in the control.
@@
 Petit Poll recommends Ontario take similar, yet bolder steps to ensure Indigenous and visible minority owners are not left behind in during the COVID-19 pandemic.
-To do so, restaurant-industry specific interest-free loans, non-repayable contributions, free educational programming, mentorship, and additional supports should be extended to Indigenous and visible minority restaurant owners in the province.
+To do so, restaurant industry-specific interest-free loans, non-repayable contributions, free educational programming, mentorship, and additional supports should be extended to Indigenous and visible minority restaurant owners across the province.
 

### 2021-02-21 outputs/paper/paper.Rmd
add percents to results and timeline in methodology

@@
 library(cowplot)  # for plotting side by side
+library(lubridate)  # for timeline
 
@@
 
-Analysis for this report uses the R statistical programming language [@R], and more specifically, the tidyverse package for data manipulation [@tidyverse].
-To facilitate a reproducible workflow, here is used to reference file locations [@here].
-Graphs and tables use features from cowplot, finalfit, gridExtra, and kableExtra [@cowplot] [@finalfit] [@gridExtra] [@kableExtra].
-Finally, bookdown is used to format the report [@bookdown].
+Analysis for this report uses the `R` statistical programming language [@R], and more specifically, the `tidyverse` package for data manipulation [@tidyverse].
+To facilitate a reproducible workflow, `here` is used to reference file locations [@here].
+Graphs and tables use features from `cowplot` [@cowplot], `finalfit` [@finalfit], `lubridate` [@lubridate], and `kableExtra` [@kableExtra].
+Finally, `bookdown` is used to format the report [@bookdown].
 
@@
 
-#TO DO: ADD STUFF ABOUT STATISTICAL PROPERTIES OF CLUSTER AND STRATIFIED SAMPLING. CITE TEXTBOOK READING
+#TODO: ADD STUFF ABOUT STATISTICAL PROPERTIES OF CLUSTER AND STRATIFIED SAMPLING. CITE TEXTBOOK READING
 
@@
 ```
+
 The randomly sampled restaurants were all assigned ID numbers in a random order.
@@
 There was also a copy of the survey contained in a mailer envelope and a contact number, allowing restaurant owners to complete the survey by phone or mail if they did not feel able to complete it online.
+If there was no response within two weeks, the restaurant was contacted by phone, and again five days letter if there was no response.
 This procedure was repeated for Survey 1 and Survey 2.
-If there was no response within two weeks, the restaurant was contacted by phone, and again five days letter if there was no response.
 
@@
 
-#TODO: MAKE TIMELINE TABLE AND REFERENCE (###)
+```{r timeline, fig.cap = "Timeline of restaurant closure experiment with surveys", fig.width = 8, fig.height = 4, echo = FALSE, message = FALSE, warning = FALSE}
+# from https://benalexkeen.com/creating-a-timeline-graphic-using-r-and-ggplot2/
+df <- data.frame(
+  year = c(2021, 2021, 2021, 2021, 2021, 2021, 2021),
+  month = c(6, 6, 6, 7, 7, 8, 8),
+  day = c(3, 26, 28, 1, 15, 3, 27),
+  milestone = c("Survey 1 begins", "Survey 1 ends", "Closures \nannounced", "Closures begin", "Closures end", "Survey 2 begins", "Survey 2 ends"),
+  status = c("Survey 1", "Survey 1", "Treatment", "Treatment", "Treatment", "Survey 2", "Survey 2")
+)
 
-A project timeline can be found in Table ###.
+df$date <- with(df, ymd(sprintf('%04d%02d%02d', year, month, day)))
+df <- df[with(df, order(date)), ]
+
+status_levels <- c("Survey 1", "Treatment", "Survey 2")
+status_colors <- c("#D8B70A", "#972D15", "#5BBCD6")
+
+df$status <- factor(df$status, levels=status_levels, ordered=TRUE)
+
+directions <- c(1, 1, -1, -1, -1, 1, 1)
+
+line_pos <- data.frame(
+    "date"=unique(df$date),
+    "position"= c(0.2, 0.2, -0.2, -0.4, -0.6, 0.2, 0.2),
+    "direction"=rep(directions, length.out=length(unique(df$date)))
+)
+
+df <- merge(x=df, y=line_pos, by="date", all = TRUE)
+df <- df[with(df, order(date, status)), ]
+
+text_offset <- 0.05
+
+df$month_count <- ave(df$date==df$date, df$date, FUN=cumsum)
+df$text_position <- (df$month_count * text_offset * df$direction) + df$position
+
+month_date_range <- c(as_date("2021-05-01"), as_date("2021-06-01"), as_date("2021-07-01"), as_date("2021-08-01"), as_date("2021-09-01"))  
+month_format <- format(month_date_range, '%b')
+month_df <- data.frame(month_date_range, month_format)
+
+#### PLOT ####
+ggplot(df,aes(x = date, y = 0, col = status, label = milestone)) +
+  labs(col = "") +
+  scale_color_manual(values = status_colors, labels = status_levels, drop = FALSE) +
+  theme_classic() +
+  # Plot horizontal black line for timeline
+  geom_hline(yintercept = 0, color = "black", size = 0.3) +
+  # Plot vertical segment lines for milestones
+  geom_segment(data = df[df$month_count == 1,], aes(y = position, yend = 0, xend = date), color = 'black', size = 0.2) +
+  geom_segment(aes(x = as_date("2021-05-01"), xend = as_date("2021-05-31"), y = 0, yend = 0), color = "#D8B70A", size = 1) +
+  geom_segment(aes(x = as_date("2021-07-01"), xend = as_date("2021-07-31"), y = 0, yend = 0, ), color = "#5BBCD6", size = 1) +
+  # Plot scatter points at zero and date
+  geom_point(aes(y = 0), size = 3) +
+  # Don't show axes, appropriately position legend
+  theme(axis.line.y=element_blank(),
+                 axis.text.y = element_blank(),
+                 axis.title.x = element_blank(),
+                 axis.title.y = element_blank(),
+                 axis.ticks.y = element_blank(),
+                 axis.text.x = element_blank(),
+                 axis.ticks.x = element_blank(),
+                 axis.line.x = element_blank(),
+                 legend.position = "bottom"
+                ) +
+  # Show text for each month
+  geom_text(data = month_df, aes(x = month_date_range, y = -0.05, label = month_format), size = 3, vjust = 0.5, color = 'black') +
+  # Show text for each milestone
+  geom_text(aes(x = c(as_date("2021-06-03"), as_date("2021-06-26"), as_date("2021-06-25"), as_date("2021-07-01"), as_date("2021-07-15"), as_date("2021-08-03"), as_date("2021-08-27")),
+                y = text_position, label = milestone),size=3) +
+  geom_text(aes(x = as_date("2021-05-16"), y = 0.1, label = "Study period of Survey 1"), size = 3, color = "#D8B70A") +
+  geom_text(aes(x = as_date("2021-07-16"), y = 0.1, label = "Study period of Survey 2"), size = 3, color = "#5BBCD6")
+```
+
+A project timeline can be found in Figure \@ref(fig:timeline).
 
@@
 After Survey 1 data was collected, on June 28th, shutdowns were announced for the six treatment LHAs.
-The shutdowns ran from July 1s to July 14th, inclusive.
+The shutdowns ran from July 1st to July 14th, inclusive.
 This length of time was considered to be the minimum effective length for a shutdown to stop circulation of the virus.
@@
 Reaching restaurant owners to better understand their businesses, and the impact of closures, was a crucial component of this experiment.
-Approximately 39% of individuals selected to participate completed or partially completed the surveys.
+Approximately 40% of individuals selected to participate completed or partially completed the surveys.
 This section provides an overview of the data gathered from each survey.
@@
 
-The baseline for reported revenue, based on information from May 2021, can be found in Figure \@ref(fig:baselinerevenue).
-The baseline for employement of full-time and part-time employees is shown in Figure \@ref(fig:baselineemployees).
+The baseline distributions for reported revenue in the treatment and control groups, based on information from May 2021, can be found in Figure \@ref(fig:baselinerevenue).
+The baseline distributions for number of full-time and part-time employees in the treatment and control groups, also based on information from May 2021, is shown in Figure \@ref(fig:baselineemployees).
 
@@
 
-### Closures had a stronger negative impact on dine-in only restaurant
-
-#TODO: ADD MEANS (###)
+### Closures had a stronger negative impact on dine-in only restaurants
 
 It is worth noting that the negative impact on revenue was not equally distributed across the three types of establishments.
-Dine-in restaurants suffered significant losses, with restaurant owners in the treatment group who selected "dine-in" reporting a mean revenue of ###, those who selected "take-out" reporting ###, and "both", ###.
-The control group reported ###, ###, and ### for dine-in, take-out, and both, respectively.
+Compared to the control group, treatment group dine-in restaurants suffered significant losses in average revenue.
+Restaurant owners in the treatment group who only offered dine-in service reported a mean revenue of \$34,609.40, those who offered both take-out and dine-in service reported \$42,889.41, and those who offered only take-out service reported \$53,156.02.
+The control group reported \$67,744.79, \$70,062.17, and \$72,860.20 for dine-in only, both, and take-out only respectively.
 Figure \@ref(fig:servicetypeimpact) shows a comparison of revenue distributions for restaurants offering dine-in service, take-out, or both.
@@
 
-#TODO: ADD MEANS (###)
-
 The negative impact of mandated closures was not distributed equally across restaurant owner demographics either.
-As indicated in Figure \@ref(fig:minorityimpact) restaurant owners who identified as Indigenous or as members of a visible minority group reported lower revenues in the treatment group than in the control.
-The mean revenue for those who identified as visible minority or Indigenous in the treatment group was ### and ### for those who did not.
-In the control group, the mean revenue for those who identified as Indigenous or as members of a visible minority group was ### and ### for those who did not.
+As indicated in Figure \@ref(fig:minorityimpact), treatment group restaurant owners who identified as Indigenous or as members of a visible minority group reported a larger loss in average revenues, compared to the control, than those who did not identify as Indigenous or a visible minority.
+The mean revenue for those who identified as visible minority or Indigenous in the treatment group was \$28,749.17, and it was \$47,572.93 for those who did not.
+In the control group, the mean revenue for those who identified as Indigenous or as members of a visible minority group was \$73,983.60, and it was \$70,777.57 for those who did not.
 
@@
 Further, the federal government has announced and collected applications to the Black Entrepreneurship Program, an initiative to ensure Black-owned businesses thrive [@bep].
-Petit Poll recommends Ontario take similar, yet bolder steps to ensure Indigenous and visible minority owners are not left behind in during the COVID-19 pandemic.
+Petit Poll recommends Ontario take similar, yet bolder, steps to ensure Indigenous and visible minority owners are not left behind in during the COVID-19 pandemic.
 To do so, restaurant industry-specific interest-free loans, non-repayable contributions, free educational programming, mentorship, and additional supports should be extended to Indigenous and visible minority restaurant owners across the province.

### 2021-02-21 outputs/paper/paper.Rmd
typo

@@
 
-In addition to survey data collected by Petit Poll, this report relies on publicly available federal census data [@census_2016] and data from provincial public health departments[@inspection].
+In addition to survey data collected by Petit Poll, this report relies on publicly available federal census data [@census_2016] and data from provincial public health departments [@inspection].
 

### 2021-02-22 outputs/paper/data_simulation.Rmd
add readme, update bibtex, add lorena's text, add readme, add abstract, add title

@@
 
-colnames(populations) <- c("Info", "Ontario", "Haliburton", "Algoma", 
-                           "Hamilton", "Windsor_Essex", "Simcoe_Muskoka", 
-                           "Timiskaming", "Brant", "Sudbury", "Oxford", 
-                           "Elgin", "Northwest", "Waterloo", "Durham")
+colnames(populations) <- c("Info", "Ontario", "haliburton", "algoma", 
+                           "hamilton", "windsor", "simcoe", 
+                           "timiskaming", "brant", "sudbury", "oxford", 
+                           "elgin", "northwestern", "waterloo", "durham")
 
 populations <- populations %>%
-  mutate(Southwestern = Oxford + Elgin) %>%
+  mutate(southwestern = oxford + elgin) %>%
   mutate(total_treat = 
-           Haliburton + Algoma + Hamilton + Windsor_Essex + Simcoe_Muskoka + Timiskaming,
+           haliburton + algoma + hamilton + windsor + simcoe + timiskaming,
          total_control = 
-           Brant + Sudbury + Northwest + Waterloo + Durham + Southwestern) %>%
-  select(-Oxford, -Elgin)
+           brant + sudbury + northwestern + waterloo + durham + southwestern) %>%
+  select(-oxford, -elgin)
 
 populations
+
+write_csv(populations, here("outputs/data/populations"))
 ```

### 2021-02-22 outputs/paper/paper.Rmd
add readme, update bibtex, add lorena's text, add readme, add abstract, add title

@@
 ---
-title: "TITLE"
+title: "COVID-19 Closures Negatively Impacts Restaurant Revenue and Employment"
 author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
-date: "`r format(Sys.time(), '%d %B %Y')`"
+date: "September 20th, 2021"
 output:
@@
     toc: no
-subtitle: "SUBTITLE"
-abstract: "Four sentences. 1) what was done, 2) what was found, and 3) why this matters (all at a high level). Top level finding"
+subtitle: "A random controlled trial, with surveys, to identify the impact of mandatory partial closures on Ontario restaurants"
+abstract: "This report covers an experiment conducted by Petit Poll to test the impact of COVID-19 closures on Ontario restaurants.
+A randomized controlled trial was conducted and surveys were used to collect results.
+The data show that restaurant revenue and employee counts were negatively impacted by a mandatory two-week partial closure, and dine-in restaurants and restaurants owned by visible minorites were more negatively impacted.
+These results suggest that if more closures are necessary, Ontario should support restaurant owners by offering support for take-out services and minority-owned businesses."
 thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
@@
 In particular, support for Indigenous and visible minority-owned businesses is imperative, as these populations continue to bear the brunt of systemic inequalities.
-Preparing and supporting dine-in establishments to transition to takeout only, and providing furloughed workers with vital financial support, must be equally prioritized.
+Preparing and supporting dine-in establishments to transition to take-out only, and providing furloughed workers with vital financial support, must be equally prioritized.
 
@@
 all_units_data %>%
-  slice(1:10) %>%
+  slice(101,1100,2101,3101,4100,5100,6100,7100,8100,9101) %>%
   knitr::kable(caption = "Example segment of the unit level sampling frame",
@@
 Survey 1 was conducted June 3rd to 27th 2021, and it asked about the month of May 2021.
+The survey can be found online by clicking here: [2021 Ontario Restaurant Survey 1](https://forms.gle/ZDc5HJBWmJu5snHf9).
 
@@
 Survey 2 was conducted August 3rd to 27th 2021, and it asked about the month of July 2021.
+The survey can be found online by clicking here: [2021 Ontario Restaurant Survey 2](https://forms.gle/JWn6VU299uTyufj99).
 
@@
 
-As noted in the results from survey 2, the intervention led to a noticeable difference in reported revenues.
+As noted in the results from Survey 2, the intervention led to a noticeable difference in reported revenues.
 The mean reported revenue for the treatment group was \$45,959.60 and $70,675.60 for the control.
@@
 Further, the federal government has announced and collected applications to the Black Entrepreneurship Program, an initiative to ensure Black-owned businesses thrive [@bep].
-Petit Poll recommends Ontario take similar, yet bolder, steps to ensure Indigenous and visible minority owners are not left behind in during the COVID-19 pandemic.
+Petit Poll recommends Ontario take similar, yet bolder, steps to ensure Indigenous and visible minority owners are not left behind during the COVID-19 pandemic.
 To do so, restaurant industry-specific interest-free loans, non-repayable contributions, free educational programming, mentorship, and additional supports should be extended to Indigenous and visible minority restaurant owners across the province.
 
-```{r minorityimpact, fig.cap="Survey 2 revenue distributions for minority status with means marked", fig.width=6, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
+```{r minorityimpact, fig.cap="Survey 2 revenue distributions for minority status with means marked", fig.width=6.25, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
 data <- bind_rows(
@@
 
-##TODO: Talk about broad economic interdependencies: restaurants as a key feature in neighbourhoods, closures impacting the desirability of an area, impacting the real estate market
+The findings from this experiment uncover the negative impact that mandated closures have on restaurant businesses specifically.
+In a national emergency, these effects have to be contextualized by assessing the impact on a broader societal level.
+As the COVID-19 pandemic continues to test our resilience, it is important to consider the economic inter-dependencies that rely on the health of restaurant businesses.
+As noted in Forbes [-@forbes], a key feature of neighbourhood desirability is access to a wide range of shops and restaurants.
+Restaurant closures, leading to vacant commercial lots, might have a negative impact on the real estate market, setting off an unfortunate ripple effect that could destabilize the economy further.
+Preventing the permanent closure of restaurants might prove to be a worthwhile investment in the months following the pandemic.
 
-##TODO: Talk about individual level: gainful employment and psychological wellbeing, especially the role of the service industry in financial independence for oppressed/undereducated/immigrants or otherwise made-vulnerable folks
+On an individual level, these findings point at the importance of employment.
+Gainful employment is directly tied to psychological wellbeing, with experts citing work as one of the most important determinants of quality of life, second only to personal relationships.
+[@sage] During a crisis that has the potential to severely impact the population's mental health, ensuring individuals retain their employment is vital.
+Employment, aside from providing an income and the possibility of financial independence, fosters a positive network of social support — a crucial social determinant of health [@who].
+Prioritizing efforts to establish positive networks of social support seems particularly necessary during a pandemic that requires measures of physical distancing.
+
+These examples provide a mere glance at the economic and social implications of our findings.
+To better understand these implications on a micro and macro level, Petit Poll recommends the Ontario Ministry of Economic Development, Job Creation and Trade, consult with relevant government authorities and departments.
 
@@
 
-##TODO: WRITE ABOUT ETHICS AND BIAS, FIRST IN TERMS OF SURVEYS
-https://www.qualtrics.com/blog/ethical-issues-for-online-surveys/
-https://www.statcan.gc.ca/eng/dai/btd/variance_bias
+This experiment would not have been possible without the participation of hundreds of restaurant owners.
+It is Petit Poll's greatest priority to ensure all studies adhere to the highest ethical standards, especially when involving human participants.
+Ethical requirements for this project, particularly the survey portion, included:
+
+- Anonymity, by determining that collecting the restaurant owner's name was unnecessary, and processing survey data with numerical IDs rather than the restaurant name or address.
+- Confidentiality, by employing a professional data management account throughout the entirety of the project.
+- Informed consent, by providing a clear explanation of the purposes of the study, the nature of the survey, and contact details should participants require additional information. 
+- Voluntary participation and disclosure, by allowing respondents to engage or refuse to engage in the study and allowing non-response of demographic questions.
+
+Additionally, in order to reduce potential biases, the survey portion of this experiment used a thoroughly-tested questionnaire, a robust methodology, expert interviewers, and invested in following up with selected participants who did not initially respond.
+
+#TODO: talk a bit more about who might have been excluded
 
@@
 
-#TODO: TALK ABOUT EXTERNAL VALIDITY AND THE ISSUES WITH CLUSTER SAMPLING.
-Unavoidable because shutdowns were by health unit for COVID, and we were trying to replicate them. It was ethically unsound to run the experiment on the entire province, so sampling was necessary.
+Although great care was taken with every step of the design of this experiment, with the goal of gathering data that would accurately represent current conditions, the authors acknowledge to following limitations.
 
-#TODO: TALK ABOUT HOW IT ONLY CATCHES LEGALLY REGISTERED BUSINESSES
+Cluster sampling has inherent constraints that might affect external validity, including the reduction of the population, in this case the entirety of restaurant business in Ontario, to smaller groups, potentially affect representation.
+This may lead to a higher potential of sampling error and biases, as the factor by which the population is clustered might introduce unforeseen conditions.
+However, cluster sampling by local health authority population sizes was necessary as the goal of this experiment was to replicate current protocols for mandated closures, which have been dictated by local health authorities.
+The ethical implications of experimenting in the entirety of the population proved to be unsound, as the negative effects of closures would have been exacerbated.
+Sampling was necessary to understand the impact while containing its potentially devastating effects.
+
+A second limitation arises from the decision to use food inspection records to collect information on current restaurants.
+We acknowledge that this process would effectively erase from our study all businesses that do not currently operate in accordance to the legal requirement to properly license a restaurant business.
+As such, should the Ontario Ministry of Economic Development, Job Creation and Trade need to understand the COVID-19 impact on non-licensed restaurant businesses, we recommend further research.
 
@@
 
-```{r nonresponse, fig.cap="Nonresponse and partial response rates for Survey 1 and 2", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+```{r nonresponse, fig.cap="Non-response and partial response rates for Survey 1 and 2", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
 num_treat_sample <- as.numeric(count(table_for_surveys %>% filter(group == "treatment")))
@@
 
-#TODO: talk about research on individual impact (we look at owners and not employees, might be missing key info there)
+This experiment collected information about restaurant owners in Ontario to study the economic and social impact of closures on a business level.
+To understand the effects on an individual level, questionnaires that are aimed at employees would be a feasible adaptation of this study.
 
-#TODO: briefly talk about potential unevenness of impact on franchises vs independent businesses.
-How were they impacted and what does that mean for our findings, are there connected?
-Are franchises more likely to already have take-out?
-Or be visible minority-owned?
+Finally, this experiment did not differentiate between independent restaurant businesses and franchises or chains.
+To better develop support programs, it might be advantageous to deliberately inquire about the type of business model under which the restaurant operates.
+As this experiment revealed, dine-in and visible minority-owned restaurants were the most affected by closures.
+Understanding whether take-out service is more frequent in franchises, or if less members of visible minority groups own independent restaurants, for example, would allow for the informed allocation of funds towards targeted support programs.
 

### 2021-02-22 outputs/paper/paper.Rmd

@@
 ---
-title: "COVID-19 Closures Negatively Impacts Restaurant Revenue and Employment"
+title: "COVID-19 Closures Negatively Impact Restaurant Revenue and Employment"
 author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
@@
 To account for this, the questions were carefully designed to gather, exactly and only, the necessary data for our study.
+
+[Appendix B](#appendixB) contains screen captures of the online version of Survey 1 and Survey 2.
+For images of the sheet included in the mailers for Survey 1 and Survey 2 sent to restaurant owners, containing all survey questions and answer options, refer to [Appendix C](#appendixC).
 
@@
 
-# Appendix {-}
-
 # Appendix A {#appendixA}
@@
 
+\newpage
 # Appendix B {#appendixB}
 
-TODO: ADD A SURVEY SCREENSHOT. REFERENCE IN THE MAIN PAPER.
+```{r page1, echo=FALSE, fig.cap="Screen capture of the first section of Survey 1 and Survey 2.", out.width = '70%', fig.align="center"}
+knitr::include_graphics(here("outputs/images/page1.png"))
+```
+
+```{r page2a, echo=FALSE, fig.cap="Screen capture of the second section of Survey 1.", out.width = '75%', fig.align="center"}
+knitr::include_graphics(here("outputs/images/page2a.png"))
+```
+
+```{r page2b, echo=FALSE, fig.cap="Screen capture of the second section of Survey 2.", out.width = '75%', fig.align="center"}
+knitr::include_graphics(here("outputs/images/page2b.png"))
+```
+
+```{r page3, echo=FALSE, fig.cap="Screen capture of the third section of Survey 1 and Survey 2.", out.width = '75%', fig.align="center"}
+knitr::include_graphics(here("outputs/images/page3.png"))
+```
+
+```{r page4, echo=FALSE, fig.cap="Screen capture of the fourth section of Survey 1 and Survey 2.", out.width = '75%', fig.align="center"}
+knitr::include_graphics(here("outputs/images/page4.png"))
+```
+
+\clearpage
 
@@
 
-TODO: ADD A COMPLETE LIST OF SURVEY QUESTIONS AND OPTIONS. REFERENCE IN THE MAIN PAPER.
+```{r survey1png, echo=FALSE, fig.cap="Image of the mailer sent to restaurant owners containing Survey 1.", out.width = '78%', fig.align="center"}
+knitr::include_graphics(here("outputs/images/survey1.png"))
+```
+```{r survey2png, echo=FALSE, fig.cap="Image of the mailer sent to restaurant owners containing Survey 2.", out.width = '78%', fig.align="center"}
+knitr::include_graphics(here("outputs/images/survey2.png"))
+```
 

### 2021-02-22 outputs/paper/data_simulation.Rmd

@@
   bookdown::pdf_document2:
-    toc: no
+    toc: yes
 subtitle: "Simulation Methods and Parameterization Research"
@@
 ```
+
+# Introduction
 
@@
 
+## Research
+
 First, some research:
@@
 ```
+
 ```{r, warning = FALSE}
@@
 ```
+
 According to Ontario restaurant data from Yelp [@yelp_dataset], approximately 6% of restaurants
@@
 ## Survey 1
+
 ```{r, warning = FALSE}
@@
 ## Survey 2
+
 ```{r, warning = FALSE}
@@
 
-# Demographic traits of owners
+# Demographic traits of owners: disability
+
+## Research
 
@@
 ```
+
+# Demographic traits of owners: racial and ethnic minorities and gender
+
+## Research
 
@@
 
-# Survey 2
+## Research
 
@@
 3% closed of restaurants in the US closed permanently between March and June [@restaurantclosures]. This period was about six times as long as our two week closure.
+
+# Survey 2
 
@@
 
-## Survey 1
+## Research into restaurant revenue
 
@@
 
+## Survey 1
+
 ```{r, warning = FALSE}
@@
 
-## Survey 2
+## Research into changes in revenue due to closures
 
@@
 
+## Survey 2
+
 ```{r, warning = FALSE}
-# Randomly sample from the scaled F distribution to generate restaurant revenues, and apply a random number around 1 to add variation:
+# Randomly sample from the scaled F distribution to generate restaurant revenues, 
+# and apply a random number around 1 to add variation:
 
@@
 
+## Research
+
 $82,000 in yearly sales (gross revenue) per full-time equivalent employee [@restfact]
@@
 
-2.4 FTE -> 1.9 FT + 1 PT.
+$1.9 / (1.9 + 0.5) = 1.9 / 2.4 = 0.79$
 
-$ 1.9 / (1.9 + 0.5) = 1.9 / 2.4 = 0.79 $
-
-$ 1 / (1.9 + 0.5) = 1 / 2.4 = 0.42 $
+$1 / (1.9 + 0.5) = 1 / 2.4 = 0.42$
 
 ## Survey 1
+
 ```{r, warning = FALSE}
@@
 
+## Research
+
 A professional mail survey with follow up found a non-response rate of 61% [@nonresponse].
@@
 
+## Survey 1
+
 ```{r, warning = FALSE}
-# Randomly select only a subset of all the generated responses to keep, simulating nonresponse:
-# Also randomly select columns to delete in partial responses, and delete the data from those rows/columns:
+# Randomly select only a subset of all the generated responses to keep, 
+# simulating nonresponse. Also randomly select columns to delete in partial responses, 
+# and delete the data from those rows/columns:
 
@@
 
+## Survey 2
+
 ```{r, warning = FALSE}
-# Randomly select only a subset of all the generated responses to keep, simulating nonresponse:
-# Also randomly select columns to delete in partial responses, and delete the data from those rows/columns:
+# Randomly select only a subset of all the generated responses to keep, 
+# simulating nonresponse. Also randomly select columns to delete in partial responses, 
+# and delete the data from those rows/columns:
 
@@
 
+# Budget
+
+```{r}
+# research for typical budget numbers
+restaurants = 2006
+survey_total = 2
+# https://www.canadapost.ca/cpc/en/business/postal-services/mailing/letter-discounts.page?
+indiv_postage = 0.85 
+# https://www.ontario.ca/document/your-guide-employment-standards-act-0/minimum-wage
+minimum_wage = 14.25 
+# https://www.alchemer.com/plans-pricing/small-teams/
+management_service = 1300 
+average_call_mins = 7
+response_rate = .3
+
+# calculate costs
+phone_interviewer_cost = 
+  round(restaurants * survey_total*response_rate, 2) * average_call_mins / 60 * minimum_wage
+
+postage_cost = (restaurants * 2) * indiv_postage
+
+# save the information in a dataframe
+survey_budget <- data.frame(
+  Item = c ("Data Management", "Phone Interviewer Wages", "Postage", "TOTAL"),
+  Cost = c (management_service, 
+            phone_interviewer_cost, 
+            postage_cost, 
+            sum(management_service, phone_interviewer_cost, postage_cost)),
+  Description = c ("Online survey management account fees",
+                   "1,203 calls (7 minutes on average) at $14.25/hr",
+                   "4,012 mailers at $0.85/ea",
+                   "")
+)
+
+write_csv(survey_budget, here("outputs/data/survey_budget.csv"))
+```
+
 \newpage

### 2021-02-22 outputs/paper/paper.Rmd

@@
 
-This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into groups, or stata, and subsequently divided into clusters.
+This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into groups, or strata, and subsequently divided into clusters.
 A random sample is drawn from each stratum and each cluster [@gertler].
 
-The population was all restaurants in Ontario.
-
+The population for this study was all restaurants in Ontario.
 A list of Ontario local health authorities (LHAs) was used to identify units that carry out food inspections of restaurants.
@@
 The stratified LHAs produced the frame, or list of units of interest from which to draw a sample, at the cluster level.
-
 From each stratum, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control.
@@
 The clusters were used because pandemic shutdowns operated based on LHA, and the goal was to recreate the effect as closely as possible.
-
 The stratification was used because there were very differently sized LHAs, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of nonequivalent treatment and control groups.
@@
 ```{r, include = FALSE}
+# Import table that shows LHAs selected for treatment and control groups
 treatment_control_groups <- read_csv(here::here("outputs/data/treatment_control_groups.csv"))
@@
 ```{r treatmentcontrolgroups, echo = FALSE, message = FALSE, warning = FALSE}
+# format table to show LHAs that were selected for treatment and control groups
 treatment_control_groups %>%
@@
 ```{r, include = FALSE}
+# import table that contains the complete list of restaurants in treatment and control groups
 all_units_data <- read_csv(here::here("outputs/data/all_units_data.csv")) 
@@
 ```{r sampleallunitsdata, echo = FALSE, message = FALSE, warning = FALSE}
+# format table to show a few rows of the complete list of restaurants in treatment and control groups
 all_units_data %>%
@@
 
-A simple random sample of 15% of the treatment list and 15% of the control list was randomly selected to be surveyed. This was the sample at the unit level.
-
+A simple random sample of 15% of the treatment list and 15% of the control list was randomly selected to be surveyed.
+This was the sample at the unit level.
 This selection was used to create a panel, so the same restaurants would be surveyed for the first survey and the second survey.
 Attempting to sample only 15% of the restaurants allowed time and money to be spent on follow-up and multiple methods of data collecting, reducing the non-response bias.
+The randomly sampled restaurants were all assigned ID numbers in a random order.
 
 ```{r, include = FALSE}
+# import the table that was used to send out survey mailers
 table_for_surveys <- read_csv(here::here("outputs/data/table_for_surveys.csv"))
 ```
-
-The randomly sampled restaurants were all assigned ID numbers in a random order.
 
@@
 Once verified, the survey-taker was given the main survey.
-
-This survey cost $6,711.18. A detailed breakdown of costs can be found on [Appendix A](#appendixA).
+This survey cost $6,711.18.
+A detailed breakdown of costs can be found on [Appendix A](#appendixA).
 
@@
 ```{r timeline, fig.cap = "Timeline of restaurant closure experiment with surveys", fig.width = 8, fig.height = 4, echo = FALSE, message = FALSE, warning = FALSE}
-# from https://benalexkeen.com/creating-a-timeline-graphic-using-r-and-ggplot2/
+### from https://benalexkeen.com/creating-a-timeline-graphic-using-r-and-ggplot2/
+
+# create basic dataframe with the milestone events on the line
 df <- data.frame(
@@
 
+# append event date
 df$date <- with(df, ymd(sprintf('%04d%02d%02d', year, month, day)))
@@
 
+# set the colors for the milestone events
 status_levels <- c("Survey 1", "Treatment", "Survey 2")
@@
 
+# decide if the milestones will be labelled above or below the line
 directions <- c(1, 1, -1, -1, -1, 1, 1)
 
+# set the distance and direction of milestone labels
 line_pos <- data.frame(
@@
 
+# set the date range for the timeline
 month_date_range <- c(as_date("2021-05-01"), as_date("2021-06-01"), as_date("2021-07-01"), as_date("2021-08-01"), as_date("2021-09-01"))  
@@
 
-#### PLOT ####
+# plot the data
 ggplot(df,aes(x = date, y = 0, col = status, label = milestone)) +
@@
   geom_segment(data = df[df$month_count == 1,], aes(y = position, yend = 0, xend = date), color = 'black', size = 0.2) +
+  # plot colored lines for ongoing events
   geom_segment(aes(x = as_date("2021-05-01"), xend = as_date("2021-05-31"), y = 0, yend = 0), color = "#D8B70A", size = 1) +
@@
                 y = text_position, label = milestone),size=3) +
+  # add labels for the ongoing events
   geom_text(aes(x = as_date("2021-05-16"), y = 0.1, label = "Study period of Survey 1"), size = 3, color = "#D8B70A") +
@@
 A project timeline can be found in Figure \@ref(fig:timeline).
-
 Survey 1 was conducted June 3rd to 27th 2021, and it asked about the month of May 2021.
-The survey can be found online by clicking here: [2021 Ontario Restaurant Survey 1](https://forms.gle/ZDc5HJBWmJu5snHf9).
-
-Survey 1 Data was used to confirm that the two-stage stratified cluster sampling had created treatment and control groups that were roughly equivalent.
-
+The survey can be found online by clicking here: [2021 Ontario Restaurant Survey 1](https://forms.gle/ZDc5HJBWmJu5snHf9).Survey 1 Data was used to confirm that the two-stage stratified cluster sampling had created treatment and control groups that were roughly equivalent.
 Survey 1 collected the following data:
@@
 The survey can be found online by clicking here: [2021 Ontario Restaurant Survey 2](https://forms.gle/JWn6VU299uTyufj99).
-
-Survey 2 followed a similar format as Survey 1, with the addition of a question about closures. It collected the following data:
+Survey 2 followed a similar format as Survey 1, with the addition of a question about closures.
+It collected the following data:
 
@@
 ```{r, include = FALSE}
+# import survey 1 and 2 data, relevelling the factors so that tables and graphs will display correctly
 survey_1 <- read_csv(here("outputs/data/survey_1.csv")) %>%
@@
 
+# count the full number of restaurants who replied to at least one survey
 count(full_join(survey_1, survey_2, by = "ID"))
@@
 ### Survey 1
-
-#TODO: HOW CAN WE PLOT MORE RAW DATA?
 
@@
 ```{r survey1summary, echo = FALSE, message = FALSE, warning = FALSE}
+# summarize results for survey 1
 survey_1 %>% 
@@
   mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is Indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
+
+# put the results in a table
   knitr::kable(caption = "Summary statistics for treatment and control baselines",
@@
 ```{r baselinerevenue, fig.cap="Revenue distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+# plot survey 1 revenue distribution, separating treatment and control
 ggplot(survey_1, aes(x = revenue / 1000, fill = group)) +                       
@@
 ```{r baselineemployees, fig.cap="Employment distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=6, echo = FALSE, message = FALSE, warning = FALSE}
+# plot survey 1 employement numbers, separating treatment and control
+
+# make the full time employment count plot
 p1 <- ggplot(survey_1, aes(x = pt, fill = group)) +                       
@@
 
+# make the part time employment count plot
 p2 <- ggplot(survey_1, aes(x = ft, fill = group)) +                       
@@
 # using https://stackoverflow.com/questions/37052059/how-to-add-a-title-for-a-grid-layout-figure-in-ggplot2
+# display the full-time and part-time plots side by side
 p <- plot_grid(p1, p2, align = "h", nrow = 1, rel_widths = c(0.555,0.445))
@@
 ### Survey 2
-
-#TODO: HOW CAN WE PLOT MORE RAW DATA?
 
@@
 ```{r survey2summary, echo = FALSE, message = FALSE, warning = FALSE}
+# summarize results for survey 1
 survey_2 %>% 
@@
   mutate(group = c("", "Service type", "", "", "Owner has disability", "", "", "Owner identifies as woman", "", "", "Owner is Indigenous", "", "", "Owner is a visible minority (non-Indigenous)", "", "", "Closure", "", "", "Revenue", "Number of full-time employees", "Number of part-time employees")) %>%
+
+# put the results in a table
   knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
@@
 The revenue distribution for both groups is show in Figure \@ref(fig:postrevenue).
-
 The mean number of employees, both full-time and part-time, show a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
@@
 ```{r postrevenue, fig.cap="Revenue distribution for treatment and control groups, from Survey 2", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+# plot survey 2 revenue distribution, separating treatment and control
 ggplot(survey_2, aes(x = revenue / 1000, fill = group)) +                       
@@
 ```{r postemployees, fig.cap="Employment distribution for treatment and control groups, from Survey 2", fig.width=10, fig.height=6, echo = FALSE, message = FALSE, warning = FALSE}
+# plot survey 2 employement numbers, separating treatment and control
+
+# make the full time employment count plot
 p1 <- ggplot(survey_2, aes(x = pt, fill = group)) +                       
@@
 
+# make the part time employment count plot
 p2 <- ggplot(survey_2, aes(x = ft, fill = group)) +                       
@@
 
+# using https://stackoverflow.com/questions/37052059/how-to-add-a-title-for-a-grid-layout-figure-in-ggplot2
+# display the full-time and part-time plots side by side
 p <- plot_grid(p1, p2, align = "h", nrow = 1, rel_widths = c(0.555,0.445))
@@
 ```{r servicetypeimpact, fig.cap = "Survey 2 revenue distributions for service types with means marked", fig.width=7, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '80%', fig.align = "center"}
+# plot distributions of revenue, split by treatment/control and by type of service offered
+
 # from https://stackoverflow.com/questions/47651868/split-violin-plot-with-ggplot2-with-quantiles
-
 GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, draw_group = function(self, data, ..., draw_quantiles = NULL){
@@
 })
-
 geom_split_violin <- function (mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, show.legend = NA, inherit.aes = TRUE) {
@@
 
+# create summary data of means for the plot
 means <- survey_2 %>%
@@
 
+# create plot using summary data of means, original dataframe, and the split violin function above:
 ggplot() +
   geom_split_violin(data = (survey_2 %>% filter(service_type != "NA")), aes(x = service_type, y = revenue / 1000, fill = group), color = NA) +
+  # add lines to indicate means of the distributions
   geom_errorbar(data = means, 
@@
 ```{r minorityimpact, fig.cap="Survey 2 revenue distributions for minority status with means marked", fig.width=6.25, fig.height=5, echo = FALSE, message = FALSE, warning = FALSE, out.width = '70%', fig.align = "center"}
+# plot distributions of revenue, split by treatment/control and by type of service offered
+
+# create summary data for the plot
 data <- bind_rows(
@@
 
+# create summary data of means for the plot
 means <- data %>%
@@
 
+# create plot using summary data of means, original dataframe, and the split violin function above:  
 ggplot() +
   geom_split_violin(data = data, aes(x = minority, y = revenue / 1000, fill = group), color = NA) +
+  # add lines to indicate means of the distributions
   geom_errorbar(data = means,
@@
 ```{r nonresponse, fig.cap="Non-response and partial response rates for Survey 1 and 2", fig.width=8, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+# plot nonresponse, response, and partial response numbers for survey 1 and survey 2
+
+# calculate relevant numbers for the plot for the sample
 num_treat_sample <- as.numeric(count(table_for_surveys %>% filter(group == "treatment")))
@@
 
+# calculate relevant numbers for the plot for survey 1
 num_treat_complete_survey1 <- sum(complete.cases(survey_1 %>% filter(group == "treatment")))
@@
 
+# calculate relevant numbers for the plot for survey 2
 num_treat_complete_survey2 <- sum(complete.cases(survey_2 %>% filter(group == "treatment")))
@@
 
+# make tibble containing above numbers
 tibble(Group = c("Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control", "Treatment", "Control"), 
@@
           num_treat_complete_survey2, num_control_complete_survey2, num_treat_partial_survey2, num_control_partial_survey2, num_treat_nonre_survey2, num_control_nonresurvey2)) %>%
+  # plot the data
   ggplot(aes(x = Response, y = Count, fill = Group)) +
@@
   scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
-
 ```
@@
 ```{r echo=FALSE, message=FALSE, warning=FALSE}
-restaurants = 2006
-survey_total = 2
-indiv_postage = 0.85 # https://www.canadapost.ca/cpc/en/business/postal-services/mailing/letter-discounts.page?
-minimum_wage = 14.25 # https://www.ontario.ca/document/your-guide-employment-standards-act-0/minimum-wage
-management_service = 1300 # https://www.alchemer.com/plans-pricing/small-teams/
-average_call_mins = 7
-response_rate = .3
+# import survey budget table
+survey_budget <- read_csv(here("outputs/data/survey_budget.csv"))
 
-phone_interviewer_cost = round(restaurants * survey_total*response_rate, 2) * average_call_mins / 60 * minimum_wage
-
-postage_cost = (restaurants * 2) * indiv_postage
-
-survey_budget <- data.frame(
-  Item = c ("Data Management", "Phone Interviewer Wages", "Postage", "TOTAL"),
-  Cost = c (management_service, phone_interviewer_cost, postage_cost, sum(management_service, phone_interviewer_cost, postage_cost)),
-  Description = c ("Online survey management account fees",
-                   "1,203 calls (7 minutes on average) at $14.25/hr",
-                   "4,012 mailers at $0.85/ea",
-                   "")
-)
-
+# display survey budget in a table
 survey_budget %>% 
@@
 \newpage
+
 # Appendix B {#appendixB}
@@
 ```
+
 ```{r survey2png, echo=FALSE, fig.cap="Image of the mailer sent to restaurant owners containing Survey 2.", out.width = '78%', fig.align="center"}

### 2021-02-22 outputs/paper/paper.Rmd
More writing, pre-colour test

@@
 
-This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into groups, or strata, and subsequently divided into clusters.
-A random sample is drawn from each stratum and each cluster [@gertler].
+This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into clusters, and subsequently divided into groups, or strata.
+A random sample is drawn from each cluster and each stratum [@gertler].
 
@@
 
-#TODO: ADD SENTENCE ABOUT REST OF VARIABLES?
-
 ```{r survey2summary, echo = FALSE, message = FALSE, warning = FALSE}
@@
 
-#TODO: talk a bit more about who might have been excluded
+Finally, in order to ascertain that the recommendations for each of the findings in this report promote and advance human rights, we highlight the right to work as noted by the Ontario Human Rights Commission (OHRC).
+In response to the COVID-19 pandemic, the OHRC calls for the upholding of this right by providing special supports to vulnerable groups, including racialized communities and workers in precarious employment.
+The OHRC recognizes the loss of employment that leads to loss of household income and increased poverty as a direct impact of COVID-19 on vulnerable groups [@ohrc2].
 
@@
 
-#TODO: TALK ABOUT SURVEY NON-RESPONSE AND HOW IT AFFECTS ACCURACY. CITE READINGS. Figure \@ref(fig:nonresponse)
+Two types of survey non-response, unit and item non-response, present another limitation.
+The first, in which an individual refuses to participate, and the second, in which a participant refuses to answer a particular question, might affect the accuracy of inferences if the individuals who participate are systemically different from those who do not [@imai].
 
@@
 
-#TODO: TALK ABOUT THE ISSUES WITH SELF-REPORTED INFORMATION. CITE READING.
+A final limitation is the use of self-reported information.
+A main concern is the incidence of social desirability bias, in which respondents might provide answers they deem socially acceptable, rather than the truth [@imai].
+In this experiment, such bias could be present in the answers of Survey 2 which asks respondents about closures.
+Victims to this type of bias, respondents might have claimed they voluntarily ceased their restaurant operations to limit the spread of COVID-19 when they had not.
 
@@
 To understand the effects on an individual level, questionnaires that are aimed at employees would be a feasible adaptation of this study.
+
+Particularly, future research might consider studying the impact of closures on populations made vulnerable by the COVID-19 pandemic.
+The discrimination against the East Asian community that the pandemic exacerbated [@ohrc1], fueled by sensationalist media reports and mis- and disinformation online, might have targeted restaurant businesses directly.
+A comprehensive study would reveal further information.
 

### 2021-02-23 outputs/paper/paper.Rmd
add toc, add external/internal validity references, add stratified cluster clarifications, add explanation about representative populations and next steps.

@@
   bookdown::pdf_document2:
-    toc: no
+    toc: yes
 subtitle: "A random controlled trial, with surveys, to identify the impact of mandatory partial closures on Ontario restaurants"
@@
 
-This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into clusters, and subsequently divided into groups, or strata.
-A random sample is drawn from each cluster and each stratum [@gertler].
+This experiment used two-stage stratified cluster sampling for survey data collection, a process by which a population is divided into clusters, and these clusters are subsequently divided into strata.
+A random sample is drawn from each stratum and each cluster.
+Use of a simple random sample at each stage increases the external validity of the experiment, or the accuracy with which the sampled population represents the target population  [@gertler].
 
-The population for this study was all restaurants in Ontario.
-A list of Ontario local health authorities (LHAs) was used to identify units that carry out food inspections of restaurants.
-Using census data from 2016, these LHAs were sorted by population size, and the list was stratified into equally sized strata: small LHAs (population of less than 150,000), medium LHAs (population of 150,000 to 400,000), and large LHAs (population of more than 400,000).
-The stratified LHAs produced the frame, or list of units of interest from which to draw a sample, at the cluster level.
+The target population for this study was all restaurants in Ontario.
+Because restaurant inspection is carried out by different authorities across the province, a list of Ontario local health authorities (LHAs) was collected.
+These LHAs were the primary sampling units, forming the primary sampling frame, or list of units of interest from which to draw a sample.
+Using census data from 2016, the primary sampling frame was stratified into small LHAs (population of less than 150,000), medium LHAs (population of 150,000 to 400,000), and large LHAs (population of more than 400,000).
+Each strata contained the same number of LHAs.
 From each stratum, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control.
-This was the sample at the cluster level.
-This sample is shown in Table \@ref(tab:treatmentcontrolgroups).
+This primary sample is shown in Table \@ref(tab:treatmentcontrolgroups).
 
-The clusters were used because pandemic shutdowns operated based on LHA, and the goal was to recreate the effect as closely as possible.
-The stratification was used because there were very differently sized LHAs, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of nonequivalent treatment and control groups.
-Given the limitations of cluster sampling, stratifying the clusters by size helped ensure the experiment would be representative of Ontario.
+This cluster design was used because pandemic shutdowns in Ontario have operated based on LHA, and the goal was to recreate the effect as closely as possible.
+It also allowed for more consistent enforcement of closures.
+The stratification was used because there were very differently sized LHAs, the larger typically in urban areas and the smaller in rural areas, and randomly selecting only 12 LHAs from a list of 33 left too high a likelihood of differently sized treatment and control groups.
+Stratification can create a more balanced survey sample [@samplingtheory].
+Given the limitations of sampling from a primary sampling frame of only 33 clusters, stratifying the frame by size of cluster helped ensure the treatment and control groups would be comparable and that the sample population would be representative of the target population.
 
-#TODO: ADD STUFF ABOUT STATISTICAL PROPERTIES OF CLUSTER AND STRATIFIED SAMPLING. CITE TEXTBOOK READING
-
-```{r, include = FALSE}
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
 # Import table that shows LHAs selected for treatment and control groups
@@
 treatment_control_groups %>%
-  knitr::kable(caption = "Cluster sample randomly selecting Local Health Authorities from strata based on population size",
+  knitr::kable(caption = "Primary sample of Local Health Authorities from strata based on population size",
+               col.names = c("Group", 
+                             "Large Population LHAs", 
+                             "Medium Population LHAs", 
+                             "Small Population LHAs"),
                booktabs = TRUE) %>%
@@
 
-Once the treatment and control LHAs were selected, each corresponding Food Inspection unit was contacted, and a list of all registered restaurants in each LHA was obtained.
-Each restaurant was listed by name and address.
-Once collected into one dataframe, this was the frame at the unit level.
-A sample of this frame is shown in Table \@ref(tab:sampleallunitsdata).
+Once the treatment and control LHAs were selected, each corresponding Food Inspection unit was contacted, and a list of all registered restaurants, the secondary sample units, in each LHA was obtained.
+Each restaurant was listed by name and address, forming the secondary sampling frame.
+A portion of this frame is shown in Table \@ref(tab:sampleallunitsdata).
 
@@
   slice(101,1100,2101,3101,4100,5100,6100,7100,8100,9101) %>%
-  knitr::kable(caption = "Example segment of the unit level sampling frame",
+  knitr::kable(caption = "Example segment of the secondary sampling frame",
                booktabs = TRUE) %>%
@@
 
-A simple random sample of 15% of the treatment list and 15% of the control list was randomly selected to be surveyed.
-This was the sample at the unit level.
-This selection was used to create a panel, so the same restaurants would be surveyed for the first survey and the second survey.
+A simple random sample of 15% of the treatment list and 15% of the control list was selected to be surveyed, forming the secondary sample.
+As a result of the simple random sample, the number of restaurants from each LHA was roughly proportionate to the total population of restaurants in each LHA.
+This selection was used to create a panel, so the same restaurants would be contacted for the first survey and the second survey.
 Attempting to sample only 15% of the restaurants allowed time and money to be spent on follow-up and multiple methods of data collecting, reducing the non-response bias.
@@
 This survey cost $6,711.18.
-A detailed breakdown of costs can be found on [Appendix A](#appendixA).
+A detailed breakdown of costs can be found in [Appendix A](#appendixA).
 
@@
 The initial survey provided a clear description of the characteristics of the treatment and control groups.
-As indicated in Table \@ref(tab:survey1summary), the groups are equivalent, showing no notable differences across any of the variables studied.
-It was necessary to collect data before the intervention to ensure that the treatment and control groups were in fact comparable.
-
-Survey 1 data was used to effectively establish a baseline for comparison.
-In addition to the use of random selection of participants and random assignment to either treatment or control, establishing a baseline allows for an accurate estimation of the counterfactual.
+As indicated in Table \@ref(tab:survey1summary), the groups are comparable, showing no notable differences across any of the variables studied.
+Survey 1 was necessary to collect data before the intervention to ensure that the treatment and control groups were in fact comparable, verifying the efficacy of the randomized treatment assignment and allowing for an accurate estimation of the counterfactual.
 The counterfactual – or the representation of what would have happened had the intervention not taken place – is essential to measuring, and reporting on, the effect of the mandated restaurant closures.
+If the control is an accurate estimate of the counterfactual, the experiment is internally valid and we can observe the true impact of the treatment [@gertler].
 
@@
 The baseline distributions for number of full-time and part-time employees in the treatment and control groups, also based on information from May 2021, is shown in Figure \@ref(fig:baselineemployees).
+In this figures, the distributions are extremely similar, indicating the comparability of the treatment and control populations with regard to revenue and employment numbers.
 
@@
 
-Cluster sampling has inherent constraints that might affect external validity, including the reduction of the population, in this case the entirety of restaurant business in Ontario, to smaller groups, potentially affect representation.
+Cluster sampling has inherent constraints that might affect external validity, including the reduction of the population, in this case the entirety of restaurant business in Ontario, to smaller groups, potentially affecting representation.
 This may lead to a higher potential of sampling error and biases, as the factor by which the population is clustered might introduce unforeseen conditions.
@@
 The first, in which an individual refuses to participate, and the second, in which a participant refuses to answer a particular question, might affect the accuracy of inferences if the individuals who participate are systemically different from those who do not [@imai].
+This study reduced the impact of non-response bias by allowing participants to complete the survey by online form, mail, or phone, and by following up on non-responses.
 
@@
 
-#TODO: TALK ABOUT POTENTIALLY USING PROPENSITY SCORE WEIGHTING TO MAKE SURE THAT THE RESULTS REFLECT ONTARIO'S RACIAL DEMOGRAPHICS.
-SEE DATA_SIMULATION FILE FOR COMPARISON OF ONTARIO, TREATMENT, AND CONTROL.
-CITE READING.
+For extrapolating results to the whole of Ontario, the demographics of the areas sampled should be compared to the demographics of the entire province.
+While efforts were taken to take a sample of LHA areas representative of all those in Ontario, extreme demographic variation between LHAs made this difficult.
+Considering the LHAs selected for the treatment group, the population is 3.8% Indigenous and 11.9% visible minority [@census_2016].
+If we look at the LHAs selected for the control group, the population is 4.7% Indigenous and 16.6% visible minority [@census_2016].
+Ontario's population as a whole is 2.8% Indigenous and 28.9% visible minority [@census_2016].
+While the units of study in this experiment were restaurants and not individuals, it is worth considering that there may proportionately be more minority-owned restaurants in the entire province than these surveys suggest.
+As minority-owned restaurants were more impacted by the closures in this study, the proportion of minority-owned restaurants may influence the outcome of a pandemic closure.
 

### 2021-02-23 outputs/paper/paper.Rmd

@@
 This selection was used to create a panel, so the same restaurants would be contacted for the first survey and the second survey.
-Attempting to sample only 15% of the restaurants allowed time and money to be spent on follow-up and multiple methods of data collecting, reducing the non-response bias.
+Attempting to sample only 15% of the restaurants allowed time and money to be spent on follow-up and multiple methods of data collection, reducing the non-response bias.
 The randomly sampled restaurants were all assigned ID numbers in a random order.
@@
 There was also a copy of the survey contained in a mailer envelope and a contact number, allowing restaurant owners to complete the survey by phone or mail if they did not feel able to complete it online.
-If there was no response within two weeks, the restaurant was contacted by phone, and again five days letter if there was no response.
+If there was no response within two weeks, the restaurant was contacted by phone, and again five days later if there was no response.
 This procedure was repeated for Survey 1 and Survey 2.
@@
 Once verified, the survey-taker was given the main survey.
-This survey cost $6,711.18.
+The survey portion of the experiment cost $6,711.18.
 A detailed breakdown of costs can be found in [Appendix A](#appendixA).
@@
 The shutdowns ran from July 1st to July 14th, inclusive.
-This length of time was considered to be the minimum effective length for a shutdown to stop circulation of the virus.
+This length of time was considered to be the minimum effective length for a shutdown to stop circulation of the virus in accordance to Public Health Ontario guidelines [@pho].
 During the shutdown, all restaurants in the treatment LHAs were officially banned from offering dine-in and patio services.
@@
 
-To date, mandated closure enforcement has included issuing fines from $750 to $100,000 to businesses found in violation of the province of Ontario's emergency orders [@enforce].
+To date, mandated closure enforcement has included issuing fines from \$750 to $100,000 to businesses found in violation of the province of Ontario's emergency orders [@enforce].
 Additionally, provincial offences officers, including police officers, have the authority to disperse crowds indoors as well as outdoors [@police].
@@
 [Appendix B](#appendixB) contains screen captures of the online version of Survey 1 and Survey 2.
-For images of the sheet included in the mailers for Survey 1 and Survey 2 sent to restaurant owners, containing all survey questions and answer options, refer to [Appendix C](#appendixC).
+For images of the sheets included in the mailers sent to restaurant owners, containing all survey questions and answer options for Survey 1 and Survey 2, refer to [Appendix C](#appendixC).
 
@@
 In particular, the contributions of restaurant businesses to the local economy have to be studied in terms of employment and revenue generation.
-According to The Associated Press, there was a 20% decline in employment in the restaurant, hotel, and entertainment sector between November 2019 and November 2020[@ap].
+According to The Associated Press, there was a 20% decline in employment in the restaurant, hotel, and entertainment sector between November 2019 and November 2020 [@ap].
 The National Restaurant Association reports a total loss industry-wide of $120 billion between March and May 2020 alone [@rd].
@@
 The City of Toronto-funded Digital Main Street, created by the Toronto Association of Business Improvement Areas, might serve as an exemplary approach.
-The program provides businesses with the tools and information to build an online presence.
+The program provides businesses with the tools and information to build an online presence, accommodating for physically-distanced shopping.
 The free program includes an online learning platform, training programs, and dedicated support staff [@mainstreet].
@@
 
-Cluster sampling has inherent constraints that might affect external validity, including the reduction of the population, in this case the entirety of restaurant business in Ontario, to smaller groups, potentially affecting representation.
-This may lead to a higher potential of sampling error and biases, as the factor by which the population is clustered might introduce unforeseen conditions.
-However, cluster sampling by local health authority population sizes was necessary as the goal of this experiment was to replicate current protocols for mandated closures, which have been dictated by local health authorities.
+Cluster sampling has inherent constraints that might affect external validity, including the reduction of the population, in this case the entirety of restaurant business in Ontario, to smaller groups, potentially affecting representation [@roy].
+This may lead to a higher potential of sampling error and biases, as the factor by which the population is clustered might introduce unforeseen conditions [@roy].
+However, cluster sampling by size of local health authority population was necessary as the goal of this experiment was to replicate current protocols for mandated closures, which have been dictated by local health authorities.
 The ethical implications of experimenting in the entirety of the population proved to be unsound, as the negative effects of closures would have been exacerbated.
@@
 In this experiment, such bias could be present in the answers of Survey 2 which asks respondents about closures.
-Victims to this type of bias, respondents might have claimed they voluntarily ceased their restaurant operations to limit the spread of COVID-19 when they had not.
+Victims to this type of bias, respondents might have claimed they voluntarily ceased their restaurant operations to limit the spread of COVID-19 even if they had not.
 
@@
 As minority-owned restaurants were more impacted by the closures in this study, the proportion of minority-owned restaurants may influence the outcome of a pandemic closure.
-
-#TODO: TALK ABOUT RESEARCH INTO HOW TO EFFECTIVELY SUPPORT BUSINESSES
+Therefore, this experiment should be considered a first step in understanding the impact of COVID-19 closures and additional research, aimed deliberately at understanding minority-owned businesses, should be conducted.
 

### 2021-02-23 outputs/paper/paper.Rmd

@@
   collapse_rows() %>%
-  column_spec(1, color = "#972D15")
+  column_spec(1, color = "#cd6423")
 ```
@@
   kableExtra::kable_styling(latex_options = c("scale_down")) %>%
-  row_spec(0, color = "#972D15")
+  row_spec(0, color = "#cd6423")
 ```
@@
 status_levels <- c("Survey 1", "Treatment", "Survey 2")
-status_colors <- c("#D8B70A", "#972D15", "#5BBCD6")
+status_colors <- c("#D8B70A", "#cd6423", "#84b7d0")
 
@@
   geom_segment(aes(x = as_date("2021-05-01"), xend = as_date("2021-05-31"), y = 0, yend = 0), color = "#D8B70A", size = 1) +
-  geom_segment(aes(x = as_date("2021-07-01"), xend = as_date("2021-07-31"), y = 0, yend = 0, ), color = "#5BBCD6", size = 1) +
+  geom_segment(aes(x = as_date("2021-07-01"), xend = as_date("2021-07-31"), y = 0, yend = 0, ), color = "#84b7d0", size = 1) +
   # Plot scatter points at zero and date
@@
   geom_text(aes(x = as_date("2021-05-16"), y = 0.1, label = "Study period of Survey 1"), size = 3, color = "#D8B70A") +
-  geom_text(aes(x = as_date("2021-07-16"), y = 0.1, label = "Study period of Survey 2"), size = 3, color = "#5BBCD6")
+  geom_text(aes(x = as_date("2021-07-16"), y = 0.1, label = "Study period of Survey 2"), size = 3, color = "#84b7d0")
 ```
@@
                col.names = c("", "", "Treatment", "Control")) %>%
-  kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19), stripe_color = "#fbf7e6") %>%
-  column_spec(1, color = "#972D15")
+  kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19), stripe_color = "#f9f9f9") %>%
+  column_spec(1, color = "#cd6423")
 ```
@@
        title = "Revenue distributions were similar in the treatment and control samples") +
-  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
+  scale_fill_manual(values = c("#84b7d0", "#D8B70A"))
 ```
@@
        title = "Part-time employees") +
-  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
+  scale_fill_manual(values = c("#84b7d0", "#D8B70A"))
 
@@
        title = "Full-time employees")  +
-  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
+  scale_fill_manual(values = c("#84b7d0", "#D8B70A"))
 
@@
                col.names = c("", "", "Treatment", "Control")) %>%
-   kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19), stripe_color = "#fbf7e6") %>%
-  column_spec(1, color = "#972D15")
+   kableExtra::kable_styling(latex_options = "striped", stripe_index =c(1,5:7,11:13,17:19), stripe_color = "#f9f9f9") %>%
+  column_spec(1, color = "#cd6423")
 ```
@@
        title = "The revenue distribution was lower for the treatment sample") +
-  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
+  scale_fill_manual(values = c("#84b7d0", "#D8B70A"))
 ```
@@
        title = "Full-time employees") +
-  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
+  scale_fill_manual(values = c("#84b7d0", "#D8B70A"))
 
@@
                 position = "dodge",
-                color = "#972D15") +
+                color = "#cd6423") +
   labs(fill = NULL,
@@
   theme_minimal() +
-  scale_fill_manual(values = c("#5BBCD6", "#D8B70A"))
+  scale_fill_manual(values = c("#84b7d0", "#D8B70A"))
 ```
@@
   kable_styling() %>% 
-  row_spec(0, bold = T, color = "white", background = "#972D15") %>% 
+  row_spec(0, bold = T, color = "white", background = "#cd6423") %>% 
   row_spec(4, bold = T) %>%

### 2021-02-24 outputs/paper/paper.Rmd

@@
 ---
-title: "COVID-19 Closures Negatively Impact Restaurant Revenue and Employment"
+title: "COVID-19 Closures Impact Restaurant Revenue and Employment Unequally"
 author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
@@
     toc: yes
-subtitle: "A random controlled trial, with surveys, to identify the impact of mandatory partial closures on Ontario restaurants"
+subtitle: "A random controlled trial to identify the impact of mandatory partial closures on Ontario restaurants"
 abstract: "This report covers an experiment conducted by Petit Poll to test the impact of COVID-19 closures on Ontario restaurants.
@@
 Survey 1 was conducted June 3rd to 27th 2021, and it asked about the month of May 2021.
-The survey can be found online by clicking here: [2021 Ontario Restaurant Survey 1](https://forms.gle/ZDc5HJBWmJu5snHf9).Survey 1 Data was used to confirm that the two-stage stratified cluster sampling had created treatment and control groups that were roughly equivalent.
+The survey can be found online by clicking here: [2021 Ontario Restaurant Survey 1](https://forms.gle/ZDc5HJBWmJu5snHf9).
 Survey 1 collected the following data:
@@
 The initial survey provided a clear description of the characteristics of the treatment and control groups.
+The data was used to confirm that the two-stage stratified cluster sampling had created treatment and control groups that were roughly equivalent.
 As indicated in Table \@ref(tab:survey1summary), the groups are comparable, showing no notable differences across any of the variables studied.
@@
 
-The baseline distributions for reported revenue in the treatment and control groups, based on information from May 2021, can be found in Figure \@ref(fig:baselinerevenue).
-The baseline distributions for number of full-time and part-time employees in the treatment and control groups, also based on information from May 2021, is shown in Figure \@ref(fig:baselineemployees).
-In this figures, the distributions are extremely similar, indicating the comparability of the treatment and control populations with regard to revenue and employment numbers.
+The pre-treatment distributions for reported revenue in the treatment and control groups, based on information from May 2021, can be found in Figure \@ref(fig:baselinerevenue).
+The pre-treatment distributions for number of full-time and part-time employees in the treatment and control groups, also based on information from May 2021, is shown in Figure \@ref(fig:baselineemployees).
+In these figures, the distributions are extremely similar, indicating the comparability of the treatment and control populations with regard to revenue and employment numbers.
 
@@
 # put the results in a table
-  knitr::kable(caption = "Summary statistics for treatment and control baselines",
+  knitr::kable(caption = "Summary statistics for treatment and control groups, pre-treatment",
                booktabs = TRUE, linesep = "",
@@
 
-```{r baselinerevenue, fig.cap="Revenue distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+```{r baselinerevenue, fig.cap="Revenue distribution for treatment and control groups, pre-treatment", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
 # plot survey 1 revenue distribution, separating treatment and control
@@
 
-```{r baselineemployees, fig.cap="Employment distribution for treatment and control baselines, from Survey 1", fig.width=10, fig.height=6, echo = FALSE, message = FALSE, warning = FALSE}
+```{r baselineemployees, fig.cap="Employment distribution for treatment and control groups, pre-treatment", fig.width=10, fig.height=6, echo = FALSE, message = FALSE, warning = FALSE}
 # plot survey 1 employement numbers, separating treatment and control
@@
 A summary of these results is found in Table \@ref(tab:survey2summary).
-Naturally, a salient difference is found in service type, with dine-in restaurants decreasing due to mandated shutdowns – the intervention itself – with 7% of restaurants in the control group providing dine-in service, and only 4% in the treatment group.
-Similarly, the mean revenue decreases noticeably for the treatment group (\$45,959.60) compared to the control group ($70,675.60).
+Naturally, a salient difference is found in reported revenue, given the treatment group restaurants were unable to offer dine-in service for almost half the month.
+The mean revenue decreases noticeably for the treatment group (\$45,959.60), compared to the control group (\$70,675.60).
 The mean numbers of employees, both full-time and part-time, show a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
@@
 # put the results in a table
-  knitr::kable(caption = "Summary statistics for treatment and control groups post-treatment",
+  knitr::kable(caption = "Summary statistics for treatment and control groups, post-treatment",
                booktabs = TRUE, linesep = "",
@@
 The revenue distribution for both groups is show in Figure \@ref(fig:postrevenue).
-The mean number of employees, both full-time and part-time, show a decrease as well, from 8 and 5 respectively in the control group, to 5 and 3 for the treatment.
+The mean number of employees, both full-time and part-time, show a were noticeably different as well.
+There were an average of 8.0 full-time and 4.7 part-time employees in control group restaurants, but only 5.2 full-time and 3.0 part-time employees in the treatment group restaurants.
 Figure \@ref(fig:postemployees) shows further detail of this finding.
@@
 With these effects in mind, Petit Poll supports the Government of Ontario's programs in benefit of small businesses: the Ontario Small Business Support Grant, the Personal Protective Equipment Relief Grant, and the current Property Tax and Energy Rebate Grants [@relief].
-Additionally, based on the evidence shown in this report, it is important to consider developing provincial financial support programs for furloughed employees, in addition to standing federal programs like Employment Insurance, that directly address the negative impact of COVID-19 closures.
-Ensuring the protection of workers in the restaurant industry specifically, not only physically as the spread of the virus is contained, but economically with financial aid will be crucial to the success of mandated closures.
+Additionally, based on the evidence shown in this report, it is important to consider developing provincial financial support programs for furloughed employees that directly address the negative impact of COVID-19 closures, in addition to standing federal programs like Employment Insurance.
+Ensuring the protection of workers in the restaurant industry specifically, not only physically as the spread of the virus is contained, but economically with financial aid, will be crucial to the success of mandated closures.
 
-```{r postrevenue, fig.cap="Revenue distribution for treatment and control groups, from Survey 2", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
+```{r postrevenue, fig.cap="Revenue distribution for treatment and control groups, post-treatment", fig.width=10, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
 # plot survey 2 revenue distribution, separating treatment and control
@@
 
-```{r postemployees, fig.cap="Employment distribution for treatment and control groups, from Survey 2", fig.width=10, fig.height=6, echo = FALSE, message = FALSE, warning = FALSE}
+```{r postemployees, fig.cap="Employment distribution for treatment and control groups, post-treatment", fig.width=10, fig.height=6, echo = FALSE, message = FALSE, warning = FALSE}
 # plot survey 2 employement numbers, separating treatment and control
@@
 
-- Anonymity, by determining that collecting the restaurant owner's name was unnecessary, and processing survey data with numerical IDs rather than the restaurant name or address.
+- Anonymity, by determining that collecting the restaurant owner's name was unnecessary, and processing survey data with numerical IDs rather than restaurant names or addresses.
 - Confidentiality, by employing a professional data management account throughout the entirety of the project.
@@
 This study reduced the impact of non-response bias by allowing participants to complete the survey by online form, mail, or phone, and by following up on non-responses.
+However, it is important to consider that, despite these measures, closed restaurants may have been less likely to participate, potentially biasing the results.
 
@@
 While the units of study in this experiment were restaurants and not individuals, it is worth considering that there may proportionately be more minority-owned restaurants in the entire province than these surveys suggest.
-As minority-owned restaurants were more impacted by the closures in this study, the proportion of minority-owned restaurants may influence the outcome of a pandemic closure.
+As minority-owned restaurants were more impacted by the closures in this study, the proportion of minority-owned restaurants may influence the societal outcome of a pandemic closure.
 Therefore, this experiment should be considered a first step in understanding the impact of COVID-19 closures and additional research, aimed deliberately at understanding minority-owned businesses, should be conducted.

### 2021-02-24 outputs/paper/paper.Rmd

@@
     toc: yes
-subtitle: "A random controlled trial to identify the impact of mandatory partial closures on Ontario restaurants"
+subtitle: "A randomized controlled trial to identify the impact of mandatory partial closures on Ontario restaurants"
 abstract: "This report covers an experiment conducted by Petit Poll to test the impact of COVID-19 closures on Ontario restaurants.
@@
 The data show that restaurant revenue and employee counts were negatively impacted by a mandatory two-week partial closure, and dine-in restaurants and restaurants owned by visible minorites were more negatively impacted.
-These results suggest that if more closures are necessary, Ontario should support restaurant owners by offering support for take-out services and minority-owned businesses."
+These results suggest that if more closures are necessary, Ontario should assist restaurant owners by offering support for take-out services and minority-owned businesses."
 thanks: 'Code and data are available at: [github.com/amycfarrow/ontariorestaurantclosuresexperiment](https://github.com/amycfarrow/ontariorestaurantclosuresexperiment).'
@@
 Using census data from 2016, the primary sampling frame was stratified into small LHAs (population of less than 150,000), medium LHAs (population of 150,000 to 400,000), and large LHAs (population of more than 400,000).
-Each strata contained the same number of LHAs.
+Each stratum contained the same number of LHAs.
 From each stratum, two LHAs were randomly sampled to participate in the treatment, and two LHAs were randomly selected to participate in the control.
@@
 Each link and paper survey was personalized to the restaurant's ID number.
-The link lead to the survey, which asked for confirmation of the last three digits of the restaurant's postal code.
+The link led to the survey, which asked for confirmation of the last three digits of the restaurant's postal code.
 This was to ensure that no mailing mistakes were made, and to prevent duplicate data collection.
-Once verified, the survey-taker was given the main survey.
+Once verified, the survey-taker was presented with the main survey.
 The survey portion of the experiment cost $6,711.18.
@@
 * Demographic information
-  - Disability status: According to the UN Convention on the Rights of Persons with Disabilities, persons with disabilities are described as having "long-term physical, mental, intellectual or sensory impairments which in interaction with various barriers may hinder their full and effective participation in society on an equal basis with others."
+  - Disability status: According to the United Nations Convention on the Rights of Persons with Disabilities, persons with disabilities are described as having "long-term physical, mental, intellectual or sensory impairments which in interaction with various barriers may hinder their full and effective participation in society on an equal basis with others."
   - Indigenous status: According to the Government of Canada, Indigenous people include "First Nations (North American Indian), Métis or Inuit and/or those who reported Registered or Treaty Indian status, that is registered under the Indian Act of Canada, and/or those who reported membership in a First Nation or Indian band".
@@
 The revenue distribution for both groups is show in Figure \@ref(fig:postrevenue).
-The mean number of employees, both full-time and part-time, show a were noticeably different as well.
+The mean number of employees, both full-time and part-time, were noticeably different as well.
 There were an average of 8.0 full-time and 4.7 part-time employees in control group restaurants, but only 5.2 full-time and 3.0 part-time employees in the treatment group restaurants.

### 2021-02-25 outputs/paper/data_simulation.Rmd
refine data_simulation document. change title to something more specific.

@@
 
+# read in the data
+# NOTE: scripts 01_scrape_health_depts, 
+# 02_stratified_cluster_sampling,
+# 03_clean_restaurant_list_csvs, 
+# 04_restaurant_survey_frame,
+# and 05_import_yelp_data must have been run already
 ```
@@
 
-First, we read in the skeleton for the survey data.
+First, we read in the skeleton for the survey data in Table \@ref(tab:start).
 This is what we would hypothetically know about a restaurant before they took the survey.
@@
 
-```{r, warning = FALSE}
-# read in the data
-# NOTE: scripts 01_scrape_health_depts, 
-# 02_stratified_cluster_sampling,
-# 03_clean_restaurant_list_csvs, 
-# 04_restaurant_survey_frame,
-# and 05_import_yelp_data must have been run already
-
+```{r start, echo = FALSE, message = FALSE, warning = FALSE}
 table_for_surveys <- read_csv(here::here("outputs/data/table_for_surveys.csv"))
@@
 
-survey_1
+survey_1 %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Frame for surveys") %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```
@@
 
-First, some research:
+First, we used Yelp restaurant data to see how many Ontario restaurants offered different types of service in Table \@ref(tab:yelptakeout) and Table \@ref(tab:yelptable) [@yelp_dataset].
 
-```{r, warning = FALSE}
+```{r, include = FALSE}
 # Read in data
@@
 ```
-```{r, warning = FALSE}
+
+```{r yelptakeout, echo = FALSE, message = FALSE, warning = FALSE}
 takeout_percentage <- takeout %>%
@@
 
-takeout_percentage
+takeout_percentage %>%
+  knitr::kable(booktabs = TRUE, caption = "Yelp Ontario take-out data") %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
 ```
 
-```{r, warning = FALSE}
+```{r, include = FALSE}
 # Check proportion of RestaurantsTableService
@@
 
-```{r, warning = FALSE}
+```{r yelptable, echo = FALSE, message = FALSE, warning = FALSE}
 tableserv_percentage <- tableserv %>%
@@
 
-tableserv_percentage
+tableserv_percentage %>%
+  knitr::kable(booktabs = TRUE, caption = "Yelp Ontario table service data") %>%
+  kableExtra::kable_styling() 
 ```
 
-```{r, warning = FALSE}
+We used these percentages to estimate proportions of restaurants with take-out and dine-in service, in Table \@ref(tab:serviceprop).
+
+```{r serviceprop, echo = FALSE, message = FALSE, warning = FALSE}
 # Calculate invalid responses (neither dine-in nor takeout)
@@
 
- service_percentage
+ service_percentage %>%
+  knitr::kable(booktabs = TRUE, caption = "Estimated service type proportions") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-## Survey 1
+## Survey 1 and 2
 
-```{r, warning = FALSE}
+We randomly sampled to assign each restaurant to be "dinein", "both", or "takeout", with probabilities of 0.06, 0.615, and 0.325, in Table \@ref(tab:servicetype1) and Table \@ref(tab:servicetype2).
+
+```{r servicetype1, echo = FALSE, message = FALSE, warning = FALSE}
 # randomly assign service_provided using ratios above
@@
 
-survey_1
+survey_1 %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding service type to Survey 1 data") %>%
+  kableExtra::kable_styling()
 ```
 
-## Survey 2
-
-```{r, warning = FALSE}
+```{r servicetype2, echo = FALSE, message = FALSE, warning = FALSE}
 # randomly assign service_provided using ratios above
@@
 
-survey_2
+survey_2 %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding service type to Survey 2 data") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-## Survey 1
+## Survey 1 and 2
 
-```{r, warning = FALSE}
+We randomly sampled to assign each restaurant to either "yes", "no", or "nonanswer", with probabilities of 0.005, 0.985, and 0.01, in Table \@ref(tab:disability1) and Table \@ref(tab:disability2).
+
+```{r disability1, echo = FALSE, message = FALSE, warning = FALSE}
 # randomly assign disability status using ratios above
@@
                              size = num_total,
-                             prob = c(0.005, .985, 0.01),
+                             prob = c(0.005, 0.985, 0.01),
                              replace = TRUE))
 
-survey_1
+survey_1 %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding owner disability status to Survey 1 data") %>%
+  kableExtra::kable_styling()
 ```
 
-## Survey 2
-
-```{r, warning = FALSE}
+```{r disability2, echo = FALSE, message = FALSE, warning = FALSE}
 # randomly assign disability status using ratios above
@@
 
-survey_2
+survey_2 %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding owner disability status to Survey 2 data") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-Some research for racial and ethnic minorities and women in Canada and in business:
+We researched racial and ethnic minorities and women using census data broken down by local health authorities [@census_2016], shown in Table \@ref(tab:LHApop), Table \@ref(tab:groupscount), and Table \@ref(tab:groupsprop).
 
-```{r, warning = FALSE}
+```{r LHApop, echo = FALSE, message = FALSE, warning = FALSE}
 ### Load census dataset by Health Regions ###
@@
 
-populations
+populations %>%
+  slice(1,2,3,5) %>%
+  select(-Ontario, -total_treat, -total_control) %>%
+  mutate(Info = c("Total Population", "Indigenous", "Visible Minority", "Women")) %>%
+  knitr::kable(booktabs = TRUE, caption = "Populations in Ontario local health authorities") %>%
+  kableExtra::kable_styling(latex_options = "scale_down")
 
+#save this table
 write_csv(populations, here("outputs/data/populations"))
@@
 
-```{r, warning = FALSE}
+```{r groupscount, echo = FALSE, message = FALSE, warning = FALSE}
 # Split the population info into our treatment and control groups.
@@
 
-populations_split
+populations_split %>%
+  slice(1,2,3,5) %>%
+  knitr::kable(booktabs = TRUE, caption = "Populations in treatment and control groups") %>%
+  kableExtra::kable_styling()
 ```
 
-```{r, warning = FALSE}
+```{r groupsprop, echo = FALSE, message = FALSE, warning = FALSE}
 ### Get percentage proportions of demographic groups of interest
@@
 
-populations_split_percentage
+populations_split_percentage %>%
+  slice(1,2,3,5) %>%
+  knitr::kable(booktabs = TRUE, caption = "Proportions in treatment and control groups") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-## Survey 1
-```{r, warning = FALSE}
+## Survey 1 and 2
+
+We randomly sampled to assign each restaurant to either "yes", "no", or "nonanswer", for the owner being Indigenous, a visible minority, or a woman, using the proportions above (with 0.01 set aside for "nonresponse"), in Table \@ref(tab:minority1) and Table \@ref(tab:minority2).
+
+```{r minority1, echo = FALSE, message = FALSE, warning = FALSE}
 # Randomly assign racial and ethnic minorities, and women, using the ratios above:
@@
 
-survey_1
+survey_1 %>%
+  arrange(ID) %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding owner minority status and gender to Survey 1 data") %>%
+  kableExtra::kable_styling()
 ```
 
-## Survey 2
-
-```{r, warning = FALSE}
+```{r minority2, echo = FALSE, message = FALSE, warning = FALSE}
 # Randomly assign racial and ethnic minorities, and women, using the ratios above:
@@
 
-survey_2
+survey_2 %>%
+  arrange(ID) %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding owner minority status and gender to Survey 2 data") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-```{r, warning = FALSE}
+We randomly sampled to assign each restaurant to either "none", "temporary", or "permanent" for shutdowns, with probabilities of 0.558, 0.432, and 0.01, in Table \@ref(tab:closures).
+
+```{r closures, echo = FALSE, message = FALSE, warning = FALSE}
 # Randomly assign shutdown using the ratios above only for the treatment group:
@@
 
-survey_2
+survey_2 %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding closures to Survey 2 data") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-From an analysis of Kaggle restaurant data [@kagglerestaurantdata], we can see that restaurant revenue looks like an F distribution.
-The distribution rf(n, df1, df2, ncp) = rf(num_rest, 10, 5) gives an approximate shape.
-Using the f-distribution formula, we know the distribution has a mean of 10/9, so we would multiply by 62,963 to get the mean to 69,959.
+From an analysis of Kaggle restaurant data [@kagglerestaurantdata], we can see that restaurant revenue looks like an F-distribution.
+The distribution rf(n, df1, df2, ncp) = rf(num_rest, 20, 20) gives an approximately correct shape.
+Using the F-distribution formula, we know the distribution has a mean of 10/9, so we would multiply by 62,963 to get the mean to 69,959.
 
@@
 
-```{r, warning = FALSE}
+We randomly sampled from the above F-distribution to generate revenues for the restaurants, in Table 
+\@ref(tab:revenue1).
+
+```{r revenue1, echo = FALSE, message = FALSE, warning = FALSE}
 # Randomly sample from the scaled F distribution to generate restaurant revenues:
@@
 
-survey_1
+survey_1 %>%
+  arrange(ID) %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding revenue to Survey 1 data") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-```{r, warning = FALSE}
+We started by randomly sampling from the same F-distribution multiplied by 62963, but also multiplied by random sampling from normal distribution centred at 1, with a standard deviation of 0.1, to add some variation from the previous data.
+For the treatment group data, we then applied a factor that reduced revenue based on level of shutdown (0.5 for temporary and 0.25 for permanent), another factor that reduced revenue based on service type (0.55 for dine-in and 0.83 for both), and another factor that reduced revenue based on minority status (0.88 for minority business owners).
+This can be seen in Table \@ref(tab:revenue2).
+
+```{r revenue2, echo = FALSE, message = FALSE, warning = FALSE}
 # Randomly sample from the scaled F distribution to generate restaurant revenues, 
@@
 
-survey_2
+survey_2 %>%
+  arrange(ID) %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding revenue to Survey 2 data") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-$82,000 in yearly sales (gross revenue) per full-time equivalent employee [@restfact]
-
-Therefore 6,833 monthly revenue per full-time equivalent employee.
+Restaurants averaged $82,000 in yearly sales (gross revenue) per full-time equivalent employee [@restfact]. Therefore, we can estimate 6,833 monthly revenue per full-time equivalent employee.
 
 In January 2021, there were 2187300 full time sales and service employees in Canada and 1164000 part time sales and service employees [@hourswages].
-Therefore there are 1.9 full time employees per part time employee.
-Part time employees in service and sales averaged 16.6 hours per week. We will assume that 2 PTE = 1 FTE, or 1 PTE = 0.5 FTE.
+Therefore, there are 1.9 full time employees per part time employee.
+Part time employees in service and sales averaged 16.6 hours per week [@hourswages]. We will assume that 2 PTE = 1 FTE, or 1 PTE = 0.5 FTE.
 Therefore, for every 1.9 + 1 employees, there are 1.9 + 1*0.5 FTE. For every 2.9 employees, there are 2.4 FTE.
@@
 
-```{r, warning = FALSE}
+We divided revenue by 6833, multiplied by 0.79 and rounded to find the number of full time employees, and multiplied by 0.42 and rounded to find the number of part time employees, in Table \@ref(tab:employ1).
+
+```{r employ1, echo = FALSE, message = FALSE, warning = FALSE}
 # Use revenue to generate realistic numbers of employees for restaurants:
@@
 
-survey_1
+survey_1 %>%
+  arrange(ID) %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding employment numbers to Survey 1 data") %>%
+  kableExtra::kable_styling()
 ```
@@
 
-For the second survey, we will assume that treatment restaurants shifted towards part time random amounts-- that is, the number of full time employees per part time employee dropped from 1.9.
-X is some number less than or equal to 1.9.
+For the second survey, we will assume that treatment restaurants shifted towards part time random amounts-- that is, the number of full time employees per part time employee dropped from 1.9, a small drop that varied per restaurant.
 
-```{r, warning = FALSE}
+We divided revenue by 6833. We used the absolute value of random sample of a normal distribution centred at zero, with a standard deviation of 0.1, as a factor to decrease the part-time ratio of 1.9.
+We then used the new ratio to calculate the number of full-time and part-time employees. This can be seen in Table \@ref(tab:employ2).
+
+```{r employ2, echo = FALSE, message = FALSE, warning = FALSE}
 # Use revenue to generate realistic numbers of employees for restaurants:
@@
 
-survey_2
-
+survey_2 %>%
+  arrange(ID) %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding employment numbers to Survey 2 data") %>%
+  kableExtra::kable_styling(latex_options = "scale_down")
 ```
@@
 
-## Survey 1
+## Survey 1 and 2
 
-```{r, warning = FALSE}
+We randomly sampled to assign each row as "yes", "partial", or "no", with probabilities 0.6, 0.01, and 0.39, for nonresponse.
+We then discarded all the "no" rows.
+For the partial rows, we randomly selected a column to delete the data for.
+This can be seen in Table \@ref(tab:response1) and Table \@ref(tab:response2).
+
+```{r response1, echo = FALSE, message = FALSE, warning = FALSE}
 # Randomly select only a subset of all the generated responses to keep, 
@@
 
-survey_1
+survey_1 %>%
+  arrange(ID) %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding nonresponse to Survey 1 data") %>%
+  kableExtra::kable_styling()
 ```
 
-## Survey 2
-
-```{r, warning = FALSE}
+```{r response2, echo = FALSE, message = FALSE, warning = FALSE}
 # Randomly select only a subset of all the generated responses to keep, 
@@
 
-survey_2
+survey_2 %>%
+  arrange(ID) %>%
+  slice(101:110) %>%
+  knitr::kable(booktabs = TRUE, linesep ='', caption = "Adding nonresponse to Survey 2 data") %>%
+  kableExtra::kable_styling(latex_options = c("scale_down", "hold_position"))
 ```
 
-```{r, warning = FALSE}
+```{r, include = FALSE}
 # Save the two survey results tables:
@@
 
-```{r}
+We Calculated our budget based on Canada Post's business costs [@canadapost], Ontario's minimum wage [@minimumwage], and pricing for data management systems for surveys [@alchemer].
+The budget can be seen in Table \@ref(tab:budget).
+
+```{r budget, echo = FALSE, message = FALSE, warning = FALSE}
 # research for typical budget numbers
@@
 
+survey_budget %>%
+  knitr::kable(booktabs = TRUE, caption = "Total survey budget") %>%
+  kableExtra::kable_styling(latex_options = "hold_position")
+
+#save the survey for presentation in the main report.
 write_csv(survey_budget, here("outputs/data/survey_budget.csv"))
 ```
+
+\clearpage
 

### 2021-02-25 outputs/paper/paper.Rmd
refine data_simulation document. change title to something more specific.

@@
 ---
-title: "COVID-19 Closures Impact Restaurant Revenue and Employment Unequally"
+title: "Impact of COVID-19 Closures on Revenue and Employment More Severe for Minority-Owned and Dine-In Restaurants"
 author: "Lorena Almaraz De La Garza, Amy Farrow, and Kumalasari Sondjaja"
@@
     toc: yes
-subtitle: "A randomized controlled trial to identify the impact of mandatory partial closures on Ontario restaurants"
+subtitle: "A randomized controlled trial of mandatory partial closures and Ontario restaurants"
 abstract: "This report covers an experiment conducted by Petit Poll to test the impact of COVID-19 closures on Ontario restaurants.
